---
title: "Jiaxuan Project — Carboplatin Cohort"
author: "Tianqi Ouyang"
date: "2026-04-09"
execute:
  eval: true
  warning: false
  message: false
---

# 1 Setup

```{r}
#| label: setup-jx-carbo
library(tidyverse)
library(scales)
library(ggplot2)
library(tidycmprsk)
library(ggsurvfit)
library(gtsummary)

# Load whole-cohort data, then keep only carboplatin patients
dat <- readRDS("jiaxuan_final_master.rds") %>%
  filter(platin_group == "Carboplatin")

# Create eGFR ratio: CKD-EPI Cr-Cys (unindexed) / Cockcroft-Gault
dat <- dat %>%
  mutate(egfr_ratio = ckd_epi_gfr_cre_cys_unindex / cockcroft)

cat("Carboplatin cohort N =", nrow(dat), "\n")
```

# 2 Table 1: Baseline Characteristics (Carboplatin Only)

```{r}
#| label: jx-table1-carbo
dat %>%
  dplyr::select(
    age, age_cat, sex, race, ethnicity, tumor_stage, cancer_type_cat_7,
    carbo_AUC, carbo_AUC_cat,
    ici, Bevacizumab, Paclitaxel, Pemetrexed, Doxorubicin, Etoposide,
    Gemcitabine, Pertuzumab, Trastuzumab, Docetaxel, Administered_alone,
    hiv_rpdr, thyroid, smoking, steroids,
    cci, ecog_score, bmi, bmi_cat,
    pre_HGB_45days, pre_PLT_45days, pre_ALB_45days,
    baseline_cys_c, baseline_cre, cr_cys,
    baseline_cre_egfr, baseline_cys_c_egfr,
    ckd_epi_gfr_cre_cys, ckd_epi_gfr_cre_cys_unindex,
    cockcroft, egfr_ratio
  ) %>%
  tbl_summary(
    statistic = list(age ~ "{mean} ({sd})")
  )
```

# 3 Fine-Gray Models — eGFR Ratio (CR-CYS / CG) (Carboplatin)

`egfr_ratio = ckd_epi_gfr_cre_cys_unindex / cockcroft`, entered as a linear continuous predictor in a Fine-Gray competing-risk model (death is the competing event).

Adjuster set (per project spec; `platin_group` omitted because this cohort is carboplatin-only): `age, sex, score` (Charlson), `ecog_score_cat2, cockcroft` (CG-CrCl), `cancer_type_cat_7, tumor_stage, high_dose` (platinum dose high vs low), `Paclitaxel, Pemetrexed, Gemcitabine` (platinum partners), `bmi, smoking, steroids, thyroid`. Anemia models additionally adjust for `pre_HGB_45days`; thrombocytopenia for `pre_PLT_45days`; AKI and composite models do not add baseline labs. When the predictor is `cockcroft`, CG-CrCl is dropped from the adjuster list to avoid duplication.

```{r}
#| label: jx-carbo-fg-helper
fg_model <- function(time_var, status_var, pred_var, pre_labs = NULL) {
  adj <- c("age","sex","score","ecog_score_cat2","cockcroft",
           "cancer_type_cat_7","tumor_stage","high_dose",
           "Paclitaxel","Pemetrexed","Gemcitabine",
           "bmi","smoking","steroids","thyroid")
  if (pred_var == "cockcroft") adj <- setdiff(adj, "cockcroft")
  if (!is.null(pre_labs)) adj <- c(adj, pre_labs)
  fmla <- as.formula(paste0(
    "Surv(", time_var, ", ", status_var, ") ~ ",
    paste(c(pred_var, adj), collapse = " + ")
  ))
  tidycmprsk::crr(fmla, failcode = 1, data = dat) %>%
    tbl_regression(exp = TRUE,
                   pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>%
    add_n()
}
```

## 3.1 Anemia Grade 2

```{r}
#| label: jx-carbo-fg-ratio-anemia2
fg_model("cmp_time_anemia_2", "cmp_status_anemia_2", "egfr_ratio", "pre_HGB_45days")
```

## 3.2 Anemia Grade 3

```{r}
#| label: jx-carbo-fg-ratio-anemia3
fg_model("cmp_time_anemia_3", "cmp_status_anemia_3", "egfr_ratio", "pre_HGB_45days")
```

## 3.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-carbo-fg-ratio-throm2
fg_model("cmp_time_throm_2", "cmp_status_throm_2", "egfr_ratio", "pre_PLT_45days")
```

## 3.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-carbo-fg-ratio-throm3
fg_model("cmp_time_throm_3", "cmp_status_throm_3", "egfr_ratio", "pre_PLT_45days")
```

## 3.5 AKI Grade 2

```{r}
#| label: jx-carbo-fg-ratio-aki2
fg_model("cmp_time_aki_2", "cmp_status_aki_2", "egfr_ratio")
```

## 3.6 AKI Grade 3

```{r}
#| label: jx-carbo-fg-ratio-aki3
fg_model("cmp_time_aki_3", "cmp_status_aki_3", "egfr_ratio")
```

## 3.7 Composite Grade 2 AEs

```{r}
#| label: jx-carbo-fg-ratio-grade2
fg_model("cmp_time_grade_2_aes", "cmp_status_grade_2_aes", "egfr_ratio")
```

## 3.8 Composite Grade 3 AEs

```{r}
#| label: jx-carbo-fg-ratio-grade3
fg_model("cmp_time_grade_3_aes", "cmp_status_grade_3_aes", "egfr_ratio")
```

# 4 Fine-Gray Models — Cockcroft-Gault eGFR (Carboplatin)

Same adjuster set as Section 3, except the continuous predictor is `cockcroft` alone instead of the ratio.

## 4.1 Anemia Grade 2

```{r}
#| label: jx-carbo-fg-cg-anemia2
fg_model("cmp_time_anemia_2", "cmp_status_anemia_2", "cockcroft", "pre_HGB_45days")
```

## 4.2 Anemia Grade 3

```{r}
#| label: jx-carbo-fg-cg-anemia3
fg_model("cmp_time_anemia_3", "cmp_status_anemia_3", "cockcroft", "pre_HGB_45days")
```

## 4.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-carbo-fg-cg-throm2
fg_model("cmp_time_throm_2", "cmp_status_throm_2", "cockcroft", "pre_PLT_45days")
```

## 4.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-carbo-fg-cg-throm3
fg_model("cmp_time_throm_3", "cmp_status_throm_3", "cockcroft", "pre_PLT_45days")
```

## 4.5 AKI Grade 2

```{r}
#| label: jx-carbo-fg-cg-aki2
fg_model("cmp_time_aki_2", "cmp_status_aki_2", "cockcroft")
```

## 4.6 AKI Grade 3

```{r}
#| label: jx-carbo-fg-cg-aki3
fg_model("cmp_time_aki_3", "cmp_status_aki_3", "cockcroft")
```

## 4.7 Composite Grade 2 AEs

```{r}
#| label: jx-carbo-fg-cg-grade2
fg_model("cmp_time_grade_2_aes", "cmp_status_grade_2_aes", "cockcroft")
```

## 4.8 Composite Grade 3 AEs

```{r}
#| label: jx-carbo-fg-cg-grade3
fg_model("cmp_time_grade_3_aes", "cmp_status_grade_3_aes", "cockcroft")
```

# 5 Fine-Gray Models — CKD-EPI Cr-Cys (unindexed) eGFR (Carboplatin)

Same adjuster set as Section 3, except the continuous predictor is `ckd_epi_gfr_cre_cys_unindex` alone.

## 5.1 Anemia Grade 2

```{r}
#| label: jx-carbo-fg-epi-anemia2
fg_model("cmp_time_anemia_2", "cmp_status_anemia_2", "ckd_epi_gfr_cre_cys_unindex", "pre_HGB_45days")
```

## 5.2 Anemia Grade 3

```{r}
#| label: jx-carbo-fg-epi-anemia3
fg_model("cmp_time_anemia_3", "cmp_status_anemia_3", "ckd_epi_gfr_cre_cys_unindex", "pre_HGB_45days")
```

## 5.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-carbo-fg-epi-throm2
fg_model("cmp_time_throm_2", "cmp_status_throm_2", "ckd_epi_gfr_cre_cys_unindex", "pre_PLT_45days")
```

## 5.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-carbo-fg-epi-throm3
fg_model("cmp_time_throm_3", "cmp_status_throm_3", "ckd_epi_gfr_cre_cys_unindex", "pre_PLT_45days")
```

## 5.5 AKI Grade 2

```{r}
#| label: jx-carbo-fg-epi-aki2
fg_model("cmp_time_aki_2", "cmp_status_aki_2", "ckd_epi_gfr_cre_cys_unindex")
```

## 5.6 AKI Grade 3

```{r}
#| label: jx-carbo-fg-epi-aki3
fg_model("cmp_time_aki_3", "cmp_status_aki_3", "ckd_epi_gfr_cre_cys_unindex")
```

## 5.7 Composite Grade 2 AEs

```{r}
#| label: jx-carbo-fg-epi-grade2
fg_model("cmp_time_grade_2_aes", "cmp_status_grade_2_aes", "ckd_epi_gfr_cre_cys_unindex")
```

## 5.8 Composite Grade 3 AEs

```{r}
#| label: jx-carbo-fg-epi-grade3
fg_model("cmp_time_grade_3_aes", "cmp_status_grade_3_aes", "ckd_epi_gfr_cre_cys_unindex")
```

# 6 subHR Curves — eGFR Ratio (Carboplatin)

Spline-based subHR curves for each competing outcome, estimated from Fine-Gray competing-risk models fit with a natural cubic spline (3 df) on `egfr_ratio`, adjusting for the same covariate set as Section 3 (no `platin_group` in the carboplatin-only cohort). Curves show the subdistribution hazard ratio (on the original scale) relative to the median observed ratio (dotted vertical line); reference value subHR = 1 (dashed horizontal line). Ribbons are 95% pointwise confidence intervals from the delta method using the spline vcov block. Only the 2nd–98th percentile range of ratio is plotted.

```{r}
#| label: jx-carbo-subhr-helper
suppressPackageStartupMessages(library(splines))

plot_subhr <- function(time_var, status_var, extra_adj = NULL, outcome_label) {
  base_adj <- c("age","sex","score","ecog_score_cat2","cockcroft",
                "cancer_type_cat_7","tumor_stage","high_dose",
                "Paclitaxel","Pemetrexed","Gemcitabine",
                "bmi","smoking","steroids","thyroid")
  keep <- c("egfr_ratio", time_var, status_var, base_adj, extra_adj)
  d <- dat %>% dplyr::select(all_of(keep)) %>% tidyr::drop_na()

  ns_b <- ns(d$egfr_ratio, df = 3)
  knots_in <- attr(ns_b, "knots")
  bdry     <- attr(ns_b, "Boundary.knots")
  colnames(ns_b) <- c("ns1","ns2","ns3")

  adj_df <- d[, c(base_adj, extra_adj), drop = FALSE]
  X_adj <- model.matrix(~ ., data = adj_df)[, -1, drop = FALSE]
  X <- cbind(as.matrix(ns_b), X_adj)

  stat_num <- suppressWarnings(as.integer(as.character(d[[status_var]])))
  time_num <- as.numeric(d[[time_var]])

  fit <- cmprsk::crr(ftime = time_num, fstatus = stat_num,
                     cov1 = X, failcode = 1)

  grid_x <- seq(quantile(d$egfr_ratio, 0.02, na.rm = TRUE),
                quantile(d$egfr_ratio, 0.98, na.rm = TRUE),
                length.out = 100)
  ref_x  <- median(d$egfr_ratio, na.rm = TRUE)

  ns_grid <- predict(ns(d$egfr_ratio, knots = knots_in, Boundary.knots = bdry),
                     grid_x)
  ns_ref  <- predict(ns(d$egfr_ratio, knots = knots_in, Boundary.knots = bdry),
                     ref_x)
  ns_diff <- sweep(as.matrix(ns_grid), 2, as.vector(ns_ref), "-")

  coef_ns <- fit$coef[1:3]
  V_ns    <- fit$var[1:3, 1:3]

  log_hr <- as.vector(ns_diff %*% coef_ns)
  se     <- sqrt(pmax(diag(ns_diff %*% V_ns %*% t(ns_diff)), 0))

  df_plot <- tibble(
    ratio = grid_x,
    subhr = exp(log_hr),
    lcl   = exp(log_hr - 1.96 * se),
    ucl   = exp(log_hr + 1.96 * se)
  )

  ggplot(df_plot, aes(x = ratio, y = subhr)) +
    geom_ribbon(aes(ymin = lcl, ymax = ucl), alpha = 0.2, fill = "steelblue") +
    geom_line(color = "steelblue", linewidth = 1) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "grey50") +
    geom_vline(xintercept = ref_x, linetype = "dotted", color = "grey40") +
    labs(x = "CKD-EPI Cr-Cys / CG ratio",
         y = "subHR (95% CI)",
         title = outcome_label) +
    theme_minimal(base_size = 11)
}
```

## 6.1 Anemia Grade 2

```{r}
#| label: jx-carbo-subhr-anemia2
#| fig-width: 6
#| fig-height: 4
plot_subhr("cmp_time_anemia_2", "cmp_status_anemia_2",
           "pre_HGB_45days", "Anemia Grade 2 (Carboplatin)")
```

## 6.2 Anemia Grade 3

```{r}
#| label: jx-carbo-subhr-anemia3
#| fig-width: 6
#| fig-height: 4
plot_subhr("cmp_time_anemia_3", "cmp_status_anemia_3",
           "pre_HGB_45days", "Anemia Grade 3 (Carboplatin)")
```

## 6.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-carbo-subhr-throm2
#| fig-width: 6
#| fig-height: 4
plot_subhr("cmp_time_throm_2", "cmp_status_throm_2",
           "pre_PLT_45days", "Thrombocytopenia Grade 2 (Carboplatin)")
```

## 6.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-carbo-subhr-throm3
#| fig-width: 6
#| fig-height: 4
plot_subhr("cmp_time_throm_3", "cmp_status_throm_3",
           "pre_PLT_45days", "Thrombocytopenia Grade 3 (Carboplatin)")
```

## 6.5 AKI Grade 2

```{r}
#| label: jx-carbo-subhr-aki2
#| fig-width: 6
#| fig-height: 4
plot_subhr("cmp_time_aki_2", "cmp_status_aki_2",
           NULL, "AKI Grade 2 (Carboplatin)")
```

## 6.6 AKI Grade 3

```{r}
#| label: jx-carbo-subhr-aki3
#| fig-width: 6
#| fig-height: 4
plot_subhr("cmp_time_aki_3", "cmp_status_aki_3",
           NULL, "AKI Grade 3 (Carboplatin)")
```

## 6.7 Composite Grade 2 AEs

```{r}
#| label: jx-carbo-subhr-grade2
#| fig-width: 6
#| fig-height: 4
plot_subhr("cmp_time_grade_2_aes", "cmp_status_grade_2_aes",
           NULL, "Composite Grade 2 AEs (Carboplatin)")
```

## 6.8 Composite Grade 3 AEs

```{r}
#| label: jx-carbo-subhr-grade3
#| fig-width: 6
#| fig-height: 4
plot_subhr("cmp_time_grade_3_aes", "cmp_status_grade_3_aes",
           NULL, "Composite Grade 3 AEs (Carboplatin)")
```

# 7 Model Diagnostics

## 7.1 Events per Variable (EPV)

Models with EPV < 10 are at risk of instability; EPV < 5 should not be reported without penalisation. Predictor counts: anemia/throm = 16 (15 adjusters + predictor, no `platin_group`), AKI/composite = 15.

```{r}
#| label: jx-epv-carbo
outcomes <- c("anemia_2", "anemia_3", "throm_2", "throm_3",
              "aki_2", "aki_3", "grade_2_aes", "grade_3_aes")

epv_table <- purrr::map_dfr(outcomes, function(out) {
  status_col <- paste0("cmp_status_", out)
  n_pred <- case_when(
    grepl("anemia", out) ~ 16L,
    grepl("throm", out)  ~ 16L,
    TRUE                 ~ 15L
  )
  tibble(
    outcome      = out,
    N            = sum(!is.na(dat[[status_col]])),
    events       = sum(dat[[status_col]] == 1, na.rm = TRUE),
    deaths       = sum(dat[[status_col]] == 2, na.rm = TRUE),
    n_predictors = n_pred,
    EPV          = round(events / n_pred, 1)
  )
})

epv_table %>%
  knitr::kable(caption = "Events per variable — Carboplatin Cohort")
```

## 7.2 Collinearity — VIF (eGFR Ratio Model)

VIF > 5 = concerning; VIF > 10 = problematic. Including `cockcroft` alongside `egfr_ratio` is expected to inflate VIFs since ratio has cockcroft in the denominator.

```{r}
#| label: jx-vif-ratio-carbo
library(car)

vif_dat <- dat %>%
  select(grade_2_aes, egfr_ratio, age, sex, score, ecog_score_cat2, cockcroft,
         cancer_type_cat_7, tumor_stage, high_dose,
         Paclitaxel, Pemetrexed, Gemcitabine,
         bmi, smoking, steroids, thyroid) %>%
  drop_na()

vif_mod <- glm(grade_2_aes ~ egfr_ratio + age + sex + score + ecog_score_cat2 +
                 cockcroft + cancer_type_cat_7 + tumor_stage + high_dose +
                 Paclitaxel + Pemetrexed + Gemcitabine +
                 bmi + smoking + steroids + thyroid,
               data = vif_dat, family = binomial)

vif_res <- vif(vif_mod)
if (is.matrix(vif_res)) {
  vif_res %>% as.data.frame() %>% rownames_to_column("term") %>%
    arrange(desc(`GVIF^(1/(2*Df))`)) %>% knitr::kable(digits = 2, caption = "VIF — eGFR CR-CYS / CG ratio model (carboplatin)")
} else {
  tibble(term = names(vif_res), VIF = vif_res) %>%
    arrange(desc(VIF)) %>% knitr::kable(digits = 2, caption = "VIF — eGFR CR-CYS / CG ratio model (carboplatin)")
}
```

## 7.3 Correlation Matrix — Continuous Predictors

```{r}
#| label: jx-cormat-carbo
cor_vars <- dat %>%
  select(egfr_ratio, cockcroft, ckd_epi_gfr_cre_cys_unindex, age, bmi, score,
         pre_HGB_45days, pre_PLT_45days) %>%
  drop_na()

cor(cor_vars) %>%
  round(3) %>%
  knitr::kable(caption = "Pearson correlation — continuous predictors (carboplatin)")
```
