---
title: "Jiaxuan Project — Whole Cohort"
author: "Tianqi Ouyang"
date: "2026-04-09"
execute:
  eval: true
  warning: false
  message: false
---

# 1 Setup

```{r}
#| label: setup-jx-whole
library(tidyverse)
library(scales)
library(ggplot2)
library(tidycmprsk)
library(ggsurvfit)
library(gtsummary)

# Load whole-cohort final_master from Jiaxuan data management
dat <- readRDS("jiaxuan_final_master.rds")

# Create eGFR-CG / eGFR CR-CYS ratio
dat <- dat %>%
  mutate(egfr_ratio = cockcroft / ckd_epi_gfr_cre_cys_unindex)
```

# 2 Table 1: Baseline Characteristics (Overall)

```{r}
#| label: jx-table1-whole
dat %>%
  dplyr::select(
    age, age_cat, sex, race, ethnicity, tumor_stage, cancer_type_cat_7,
    platin_group, carbo_AUC, carbo_AUC_cat,
    ici, Bevacizumab, Paclitaxel, Pemetrexed, Doxorubicin, Etoposide,
    Gemcitabine, Pertuzumab, Trastuzumab, Docetaxel, Administered_alone,
    hiv_rpdr, thyroid, smoking, steroids,
    cci, ecog_score, bmi, bmi_cat,
    pre_HGB_45days, pre_PLT_45days, pre_ALB_45days,
    baseline_cys_c, baseline_cre, cr_cys,
    baseline_cre_egfr, baseline_cys_c_egfr,
    ckd_epi_gfr_cre_cys, ckd_epi_gfr_cre_cys_unindex,
    cockcroft, egfr_ratio
  ) %>%
  tbl_summary(
    statistic = list(age ~ "{mean} ({sd})")
  )
```

## 2.1 Missing Data — Table 1 Variables

```{r}
#| label: jx-missing-whole
table1_vars <- c(
  "age", "age_cat", "sex", "race", "ethnicity", "tumor_stage", "cancer_type_cat_7",
  "platin_group", "carbo_AUC", "carbo_AUC_cat",
  "ici", "Bevacizumab", "Paclitaxel", "Pemetrexed", "Doxorubicin", "Etoposide",
  "Gemcitabine", "Pertuzumab", "Trastuzumab", "Docetaxel", "Administered_alone",
  "hiv_rpdr", "thyroid", "smoking", "steroids",
  "cci", "ecog_score", "bmi", "bmi_cat",
  "pre_HGB_45days", "pre_PLT_45days", "pre_ALB_45days",
  "baseline_cys_c", "baseline_cre", "cr_cys",
  "baseline_cre_egfr", "baseline_cys_c_egfr",
  "ckd_epi_gfr_cre_cys", "ckd_epi_gfr_cre_cys_unindex",
  "cockcroft", "egfr_ratio"
)

dat %>%
  select(any_of(table1_vars)) %>%
  summarise(across(everything(), ~ sum(is.na(.)))) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "n_missing") %>%
  mutate(pct_missing = round(100 * n_missing / nrow(dat), 1)) %>%
  filter(n_missing > 0) %>%
  arrange(desc(n_missing)) %>%
  knitr::kable(caption = "Missing data — Table 1 variables (non-zero only)")
```

# 3 LOESS Plots by eGFR-CG / eGFR CR-CYS Ratio

`egfr_ratio = cockcroft / ckd_epi_gfr_cre_cys_unindex`

```{r}
#| label: jx-loess-fn
loess_plot <- function(data, x, y, title, xlab, ylab) {
  ggplot(data, aes(x = {{x}}, y = {{y}})) +
    geom_smooth(method = "loess", se = TRUE, span = 0.75,
                color = "blue", linewidth = 1.5) +
    scale_y_continuous(labels = percent_format(accuracy = 1)) +
    labs(title = title, x = xlab, y = ylab) +
    theme_minimal(base_size = 12) +
    theme(
      axis.title.x  = element_text(size = 11),
      axis.title.y  = element_text(size = 11),
      axis.text.x   = element_text(size = 10),
      axis.text.y   = element_text(size = 10),
      plot.title     = element_text(size = 13, face = "bold")
    )
}
```

## 3.1 Anemia Grade 2

```{r}
#| label: jx-loess-ratio-anemia2
loess_plot(dat, egfr_ratio, Anemia_g2_90days,
           "Grade 2 Anemia by eGFR-CG/CR-CYS Ratio", "eGFR-CG / eGFR CR-CYS", "Anemia G2 Rate")
```

## 3.2 Anemia Grade 3

```{r}
#| label: jx-loess-ratio-anemia3
loess_plot(dat, egfr_ratio, Anemia_g3_90days,
           "Grade 3 Anemia by eGFR-CG/CR-CYS Ratio", "eGFR-CG / eGFR CR-CYS", "Anemia G3 Rate")
```

## 3.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-loess-ratio-throm2
loess_plot(dat, egfr_ratio, Throm_g2_90days,
           "Grade 2 Thrombocytopenia by eGFR-CG/CR-CYS Ratio", "eGFR-CG / eGFR CR-CYS", "Throm G2 Rate")
```

## 3.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-loess-ratio-throm3
loess_plot(dat, egfr_ratio, Throm_g3_90days,
           "Grade 3 Thrombocytopenia by eGFR-CG/CR-CYS Ratio", "eGFR-CG / eGFR CR-CYS", "Throm G3 Rate")
```

## 3.5 AKI Grade 2

```{r}
#| label: jx-loess-ratio-aki2
loess_plot(dat, egfr_ratio, AKI_g2_90days,
           "Grade 2 AKI by eGFR-CG/CR-CYS Ratio", "eGFR-CG / eGFR CR-CYS", "AKI G2 Rate")
```

## 3.6 AKI Grade 3

```{r}
#| label: jx-loess-ratio-aki3
loess_plot(dat, egfr_ratio, AKI_g3_90days,
           "Grade 3 AKI by eGFR-CG/CR-CYS Ratio", "eGFR-CG / eGFR CR-CYS", "AKI G3 Rate")
```

# 4 Fine-Gray Models — eGFR-CG/CR-CYS Ratio as Continuous Predictor

Adjusted for: `age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + platin_group`.
Anemia models add `pre_HGB_45days`; thrombocytopenia models add `pre_PLT_45days`; AKI models add `pre_CRE_45days`.

## 4.1 Anemia Grade 2

```{r}
#| label: jx-fg-ratio-anemia2
tidycmprsk::crr(
  Surv(cmp_time_anemia_2, cmp_status_anemia_2) ~ egfr_ratio + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + platin_group + pre_HGB_45days,
  failcode = 1, data = dat
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 4.2 Anemia Grade 3

```{r}
#| label: jx-fg-ratio-anemia3
tidycmprsk::crr(
  Surv(cmp_time_anemia_3, cmp_status_anemia_3) ~ egfr_ratio + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + platin_group + pre_HGB_45days,
  failcode = 1, data = dat
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 4.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-fg-ratio-throm2
tidycmprsk::crr(
  Surv(cmp_time_throm_2, cmp_status_throm_2) ~ egfr_ratio + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + platin_group + pre_PLT_45days,
  failcode = 1, data = dat
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 4.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-fg-ratio-throm3
tidycmprsk::crr(
  Surv(cmp_time_throm_3, cmp_status_throm_3) ~ egfr_ratio + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + platin_group + pre_PLT_45days,
  failcode = 1, data = dat
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 4.5 AKI Grade 2

```{r}
#| label: jx-fg-ratio-aki2
tidycmprsk::crr(
  Surv(cmp_time_aki_2, cmp_status_aki_2) ~ egfr_ratio + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + platin_group + pre_CRE_45days,
  failcode = 1, data = dat
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 4.6 AKI Grade 3

```{r}
#| label: jx-fg-ratio-aki3
tidycmprsk::crr(
  Surv(cmp_time_aki_3, cmp_status_aki_3) ~ egfr_ratio + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + platin_group + pre_CRE_45days,
  failcode = 1, data = dat
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 4.7 Composite Grade 2 AEs

```{r}
#| label: jx-fg-ratio-grade2
tidycmprsk::crr(
  Surv(cmp_time_grade_2_aes, cmp_status_grade_2_aes) ~ egfr_ratio + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + platin_group + pre_HGB_45days + pre_PLT_45days,
  failcode = 1, data = dat
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

## 4.8 Composite Grade 3 AEs

```{r}
#| label: jx-fg-ratio-grade3
tidycmprsk::crr(
  Surv(cmp_time_grade_3_aes, cmp_status_grade_3_aes) ~ egfr_ratio + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + platin_group + pre_HGB_45days + pre_PLT_45days,
  failcode = 1, data = dat
) %>% tbl_regression(exp = TRUE, pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()
```

# 7 Model Diagnostics

## 7.1 Events per Variable (EPV)

Models with EPV < 10 are at risk of instability; EPV < 5 should not be reported without penalisation.

```{r}
#| label: jx-epv-whole
outcomes <- c("anemia_2", "anemia_3", "throm_2", "throm_3",
              "aki_2", "aki_3", "grade_2_aes", "grade_3_aes")

epv_table <- purrr::map_dfr(outcomes, function(out) {

  status_col <- paste0("cmp_status_", out)
  n_pred <- case_when(
    grepl("anemia", out)  ~ 16L,
    grepl("throm", out)   ~ 16L,
    grepl("aki", out)     ~ 16L,
    TRUE                  ~ 17L
  )
  tibble(
    outcome      = out,
    N            = sum(!is.na(dat[[status_col]])),
    events       = sum(dat[[status_col]] == 1, na.rm = TRUE),
    deaths       = sum(dat[[status_col]] == 2, na.rm = TRUE),
    n_predictors = n_pred,
    EPV          = round(events / n_pred, 1)
  )
})

epv_table %>%
  knitr::kable(caption = "Events per variable — Whole Cohort")
```

## 5.2 Collinearity — VIF (eGFR Ratio Model)

VIF > 5 = concerning; VIF > 10 = problematic.

```{r}
#| label: jx-vif-ratio-whole
library(car)

vif_dat <- dat %>%
  select(grade_2_aes, egfr_ratio, age, sex, bmi, smoking, steroids, thyroid,
         tumor_stage, ecog_score_cat2, Paclitaxel, Pemetrexed, Gemcitabine,
         ici, score, platin_group, pre_HGB_45days, pre_PLT_45days) %>%
  drop_na()

vif_mod <- glm(grade_2_aes ~ egfr_ratio + age + sex + bmi + smoking + steroids +
                 thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel +
                 Pemetrexed + Gemcitabine + ici + score + platin_group +
                 pre_HGB_45days + pre_PLT_45days,
               data = vif_dat, family = binomial)

vif_res <- vif(vif_mod)
if (is.matrix(vif_res)) {
  vif_res %>% as.data.frame() %>% rownames_to_column("term") %>%
    arrange(desc(`GVIF^(1/(2*Df))`)) %>% knitr::kable(digits = 2, caption = "VIF — eGFR ratio model (whole cohort)")
} else {
  tibble(term = names(vif_res), VIF = vif_res) %>%
    arrange(desc(VIF)) %>% knitr::kable(digits = 2, caption = "VIF — eGFR ratio model (whole cohort)")
}
```

## 5.3 Correlation Matrix — Continuous Predictors

```{r}
#| label: jx-cormat-whole
cor_vars <- dat %>%
  select(egfr_ratio, cockcroft, ckd_epi_gfr_cre_cys_unindex, age, bmi, score,
         pre_HGB_45days, pre_PLT_45days) %>%
  drop_na()

cor(cor_vars) %>%
  round(3) %>%
  knitr::kable(caption = "Pearson correlation — continuous predictors")
```
