---
title: "Jiaxuan Project — Whole Cohort"
author: "Tianqi Ouyang"
date: "2026-04-09"
execute:
  eval: true
  warning: false
  message: false
---

# 1 Setup {.content-hidden}

```{r}
#| label: setup-jx-whole
# Force UTF-8 locale so kable captions and other strings render real Unicode
# (e.g. em-dash) instead of <U+2014> escape sequences.
invisible(Sys.setlocale("LC_ALL", "en_US.UTF-8"))
library(tidyverse)
library(scales)
library(ggplot2)
library(tidycmprsk)
library(ggsurvfit)
library(gtsummary)
library(flextable)
library(rvg)
library(officer)

# Output directory for downloadable Word tables (placed under docs/ so the
# rendered website can serve them from ../tables/whole/<name>.docx).
docx_dir <- "docs/tables/whole"
dir.create(docx_dir, recursive = TRUE, showWarnings = FALSE)

# Output directory for editable PowerPoint copies of every figure. A knitr
# plot hook (defined below) saves last_plot() to docs/pptx/whole/<label>.pptx
# and appends a download link after the figure in the rendered HTML.
dir.create("docs/pptx/whole", recursive = TRUE, showWarnings = FALSE)
pptx_dir <- normalizePath("docs/pptx/whole", mustWork = TRUE)
# Relative path for download links from rendered docs/qmd/*.html
pptx_rel_prefix <- "../pptx/whole/"

# Persist the chunk-label -> pptx-path mapping so the chunk hook can emit
# the download link only when the .pptx was actually written.
.pptx_written <- new.env()

# fig.process runs in the chunk eval context (so last_plot() is fresh) and
# writes an editable .pptx alongside the saved figure.
knitr::opts_chunk$set(fig.process = function(filename) {
  label <- knitr::opts_current$get("label")
  if (is.null(label)) return(filename)
  p <- tryCatch(ggplot2::last_plot(), error = function(e) NULL)
  if (is.null(p) || !inherits(p, "ggplot")) return(filename)
  pptx_path <- file.path(pptx_dir, paste0(label, ".pptx"))
  tryCatch({
    doc <- officer::read_pptx()
    doc <- officer::add_slide(doc, layout = "Title and Content",
                              master = "Office Theme")
    doc <- officer::ph_with(doc, rvg::dml(ggobj = p),
                            location = officer::ph_location_type(type = "body"))
    print(doc, target = pptx_path)
    .pptx_written[[label]] <- paste0(pptx_rel_prefix, label, ".pptx")
  }, error = function(e) NULL)
  filename
})

# A "chunk" hook fires after the whole chunk is rendered: append the link.
local({
  default_chunk_hook <- knitr::knit_hooks$get("chunk")
  knitr::knit_hooks$set(chunk = function(x, options) {
    out <- default_chunk_hook(x, options)
    label <- options$label
    if (!is.null(label) && !is.null(.pptx_written[[label]])) {
      rel <- .pptx_written[[label]]
      link <- sprintf(
        '\n\n<p style="margin-top:-0.5em;font-size:0.9em;"><a href="%s" download>📊 Download as PowerPoint (editable)</a></p>\n\n',
        rel)
      out <- paste0(out, link)
    }
    out
  })
})

# Save a gtsummary table to a Word document.
save_tbl_docx <- function(tbl, docx_name) {
  ft <- gtsummary::as_flex_table(tbl)
  flextable::save_as_docx(ft, path = file.path(docx_dir,
                                               paste0(docx_name, ".docx")))
  invisible(tbl)
}

# Load whole-cohort final_master from Jiaxuan data management
dat <- readRDS("jiaxuan_final_master.rds")

# Create eGFR ratio: CKD-EPI Cr-Cys (unindexed) / Cockcroft-Gault
# Also create per-10 mL/min rescaled versions of cockcroft and CKD-EPI for
# reporting (HRs per 1 mL/min are clinically uninterpretable; convention in
# nephro-onc is per 10 mL/min — bio_agent confirmed). Adjusters keep raw scale.
dat <- dat %>%
  mutate(
    # Ratio uses UNCAPPED eGFR
    egfr_ratio    = ckd_epi_gfr_cre_cys_unindex / cockcroft,
    egfr_ratio_per10 = -egfr_ratio * 10,  # per 0.1-unit *decrease* reporting scale
    egfr_discrepancy = ckd_epi_gfr_cre_cys_unindex - cockcroft,
    # per-10-mL/min DECLINE reporting scale for eGFR discrepancy: HR for this
    # variable reads as the multiplicative change in subHR per 10 mL/min lower
    # discrepancy (i.e., when CKD-EPI Cr-Cys is 10 mL/min farther below CG).
    egfr_disc_per10dec = -egfr_discrepancy / 10,
    cockcroft_per10 = cockcroft / 10,
    ckd_epi_per10   = ckd_epi_gfr_cre_cys_unindex / 10
  )
```

# 2 Table 1: Baseline Characteristics (Overall)

```{r}
#| label: jx-table1-whole
dat %>%
  dplyr::select(
    age, age_cat, sex, race, ethnicity, tumor_stage, cancer_type_cat_7,
    platin_group, carbo_AUC, carbo_AUC_cat, cis_dose, cis_dose_high,
    ici, Bevacizumab, Paclitaxel, Pemetrexed, Doxorubicin, Etoposide,
    Gemcitabine, Pertuzumab, Trastuzumab, Docetaxel, other_chemo, Administered_alone,
    hiv_rpdr, thyroid, smoking, steroids,
    cci, score, ecog_score, bmi, bmi_cat,
    pre_HGB_45days, pre_PLT_45days, pre_ALB_45days,
    baseline_cys_c, baseline_cre, cr_cys,
    baseline_cre_egfr, baseline_cys_c_egfr,
    ckd_epi_gfr_cre_cys, ckd_epi_gfr_cre_cys_unindex,
    cockcroft, egfr_ratio
  ) %>%
  tbl_summary(
    statistic = list(age ~ "{mean} ({sd})")
  )
```

# 3 eGFR Ratio Distribution (Overall)

```{r}
#| label: jx-egfr-ratio-hist
#| fig-width: 8
#| fig-height: 5
ratio_hist <- dat %>% filter(!is.na(egfr_ratio))

ggplot(ratio_hist, aes(x = egfr_ratio)) +
  geom_histogram(aes(y = after_stat(count) / sum(after_stat(count)) * 100),
                 binwidth = 0.1, boundary = 0,
                 fill = "steelblue", color = "black", alpha = 0.7) +
  labs(title = "Distribution of eGFR Ratio (CKD-EPI Cr-Cys unindexed / Cockcroft-Gault)",
       x = "eGFR Ratio",
       y = "Percent of Patients (%)") +
  scale_x_continuous(breaks = seq(0, 3, 0.2)) +
  theme_minimal(base_size = 14)
```

# 4 Fine-Gray Models — eGFR Ratio (adjusted for Cockcroft-Gault)

Each table below shows univariable (one variable at a time) and multivariable Fine-Gray subdistribution hazard ratios side-by-side. A Word version of every table is saved during render — click any link below to download:

- [Anemia Grade 2](../tables/whole/sec4_anemia_2.docx) · [Anemia Grade 3](../tables/whole/sec4_anemia_3.docx)
- [Thrombocytopenia Grade 2](../tables/whole/sec4_throm_2.docx) · [Thrombocytopenia Grade 3](../tables/whole/sec4_throm_3.docx)
- [AKI Grade 2](../tables/whole/sec4_aki_2.docx) · [AKI (KDIGO)](../tables/whole/sec4_aki_kdigo.docx)
- [Composite Grade 2 AEs](../tables/whole/sec4_grade_2_aes.docx) · [Composite Grade 3 AEs](../tables/whole/sec4_grade_3_aes.docx)
- [Overall Hospitalization](../tables/whole/sec4_any_hosp.docx) · [Platinum-Related Hospitalization](../tables/whole/sec4_side_effect.docx)
- [90-Day Death (Cox PH)](../tables/whole/sec4_death_90.docx)

```{r}
#| label: jx-fg-helper
.adj_set <- function(pred_var, pre_labs, egfr_adj) {
  adj <- c("age","sex","score","ecog_score_cat2",
           "cancer_type_cat_7","tumor_stage","platin_group","high_dose",
           "Paclitaxel","Pemetrexed","Gemcitabine","ici",
           "bmi","smoking","steroids","thyroid")
  # Drop platin_group when predictor requires dose data (carbo-only after drop_na)
  if (grepl("dose_discrep", pred_var)) adj <- setdiff(adj, "platin_group")
  if (egfr_adj == "cockcroft") adj <- c(adj, "cockcroft")
  if (egfr_adj == "ckd_epi")   adj <- c(adj, "ckd_epi_gfr_cre_cys_unindex")
  if (!is.null(pre_labs)) adj <- c(adj, pre_labs)
  adj
}

# fg_model: returns univariable + multivariable merged Fine-Gray table.
# If docx_name is supplied, also saves the table as a .docx in docx_dir.
fg_model <- function(time_var, status_var, pred_var, pre_labs = NULL,
                     egfr_adj = c("none", "cockcroft", "ckd_epi"),
                     docx_name = NULL) {
  egfr_adj <- match.arg(egfr_adj)
  adj <- .adj_set(pred_var, pre_labs, egfr_adj)
  all_vars <- c(pred_var, adj)

  # Multivariable
  fmla_mv <- as.formula(paste0(
    "Surv(", time_var, ", ", status_var, ") ~ ",
    paste(all_vars, collapse = " + ")
  ))
  tbl_mv <- tidycmprsk::crr(fmla_mv, failcode = 1, data = dat) %>%
    tbl_regression(exp = TRUE,
                   pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>%
    add_n()

  # Univariable: one Fine-Gray fit per variable
  y_call <- str2lang(sprintf("Surv(%s, %s)", time_var, status_var))
  tbl_uv <- rlang::inject(
    tbl_uvregression(
      data = dat,
      method = tidycmprsk::crr,
      y = !!y_call,
      include = dplyr::all_of(all_vars),
      exponentiate = TRUE,
      pvalue_fun = function(x) style_pvalue(x, digits = 3),
      method.args = list(failcode = 1)
    )
  )

  out <- tbl_merge(
    tbls = list(tbl_uv, tbl_mv),
    tab_spanner = c("**Univariable**", "**Multivariable**")
  )

  if (!is.null(docx_name)) save_tbl_docx(out, docx_name)
  out
}

# cox_model: same signature/output for the 90-day death analysis (Cox PH).
cox_model <- function(time_var, status_var, pred_var, pre_labs = NULL,
                      egfr_adj = c("none", "cockcroft", "ckd_epi"),
                      docx_name = NULL) {
  egfr_adj <- match.arg(egfr_adj)
  adj <- .adj_set(pred_var, pre_labs, egfr_adj)
  all_vars <- c(pred_var, adj)

  fmla_mv <- as.formula(paste0(
    "Surv(", time_var, ", ", status_var, ") ~ ",
    paste(all_vars, collapse = " + ")
  ))
  tbl_mv <- survival::coxph(fmla_mv, data = dat) %>%
    tbl_regression(exp = TRUE,
                   pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>%
    add_n()

  y_call <- str2lang(sprintf("Surv(%s, %s)", time_var, status_var))
  tbl_uv <- rlang::inject(
    tbl_uvregression(
      data = dat,
      method = survival::coxph,
      y = !!y_call,
      include = dplyr::all_of(all_vars),
      exponentiate = TRUE,
      pvalue_fun = function(x) style_pvalue(x, digits = 3)
    )
  )

  out <- tbl_merge(
    tbls = list(tbl_uv, tbl_mv),
    tab_spanner = c("**Univariable**", "**Multivariable**")
  )

  if (!is.null(docx_name)) save_tbl_docx(out, docx_name)
  out
}
```

## 4.1 Anemia Grade 2

```{r}
#| label: jx-fg-cg-anemia2
fg_model("cmp_time_anemia_2", "cmp_status_anemia_2", "egfr_ratio_per10", "pre_HGB_45days", "cockcroft", docx_name = "sec4_anemia_2")
```

## 4.2 Anemia Grade 3

```{r}
#| label: jx-fg-cg-anemia3
fg_model("cmp_time_anemia_3", "cmp_status_anemia_3", "egfr_ratio_per10", "pre_HGB_45days", "cockcroft", docx_name = "sec4_anemia_3")
```

## 4.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-fg-cg-throm2
fg_model("cmp_time_throm_2", "cmp_status_throm_2", "egfr_ratio_per10", "pre_PLT_45days", "cockcroft", docx_name = "sec4_throm_2")
```

## 4.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-fg-cg-throm3
fg_model("cmp_time_throm_3", "cmp_status_throm_3", "egfr_ratio_per10", "pre_PLT_45days", "cockcroft", docx_name = "sec4_throm_3")
```

## 4.5 AKI Grade 2

```{r}
#| label: jx-fg-cg-aki2
fg_model("cmp_time_aki_2", "cmp_status_aki_2", "egfr_ratio_per10", egfr_adj = "cockcroft", docx_name = "sec4_aki_2")
```

## 4.6 AKI (KDIGO)

```{r}
#| label: jx-fg-cg-akikdigo
fg_model("cmp_time_aki_kdigo", "cmp_status_aki_kdigo", "egfr_ratio_per10", egfr_adj = "cockcroft", docx_name = "sec4_aki_kdigo")
```

## 4.7 Composite Grade 2 AEs

```{r}
#| label: jx-fg-cg-grade2
fg_model("cmp_time_grade_2_aes", "cmp_status_grade_2_aes", "egfr_ratio_per10", egfr_adj = "cockcroft", docx_name = "sec4_grade_2_aes")
```

## 4.8 Composite Grade 3 AEs

```{r}
#| label: jx-fg-cg-grade3
fg_model("cmp_time_grade_3_aes", "cmp_status_grade_3_aes", "egfr_ratio_per10", egfr_adj = "cockcroft", docx_name = "sec4_grade_3_aes")
```

## 4.9 Overall Hospitalization

```{r}
#| label: jx-fg-cg-anyhosp
fg_model("cmp_time_any_hosp", "cmp_status_any_hosp", "egfr_ratio_per10", egfr_adj = "cockcroft", docx_name = "sec4_any_hosp")
```

## 4.10 Platinum-Related Hospitalization

```{r}
#| label: jx-fg-cg-sideeffect
fg_model("cmp_time_side_effect", "cmp_status_side_effect", "egfr_ratio_per10", egfr_adj = "cockcroft", docx_name = "sec4_side_effect")
```

## 4.11 90-Day Death (Cox PH)

```{r}
#| label: jx-cox-cg-death
cox_model("time_to_death_90", "death_90", "egfr_ratio_per10", egfr_adj = "cockcroft", docx_name = "sec4_death_90")
```

# 5 Cause-Specific Hazard Models — eGFR Ratio (adjusted for Cockcroft-Gault)

```{r}
#| label: jx-csh-helper
csh_model <- function(time_var, status_var, pred_var, pre_labs = NULL) {
  adj <- c("age","sex","score","ecog_score_cat2",
           "cancer_type_cat_7","tumor_stage","platin_group","high_dose",
           "Paclitaxel","Pemetrexed","Gemcitabine","ici",
           "bmi","smoking","steroids","thyroid","cockcroft")
  if (grepl("dose_discrep", pred_var)) adj <- setdiff(adj, "platin_group")
  if (!is.null(pre_labs)) adj <- c(adj, pre_labs)
  # Cause-specific: treat death (status == 2) as censored
  d <- dat
  d$csh_status <- ifelse(d[[status_var]] == 1, 1L, 0L)
  fmla <- as.formula(paste0(
    "Surv(", time_var, ", csh_status) ~ ",
    paste(c(pred_var, adj), collapse = " + ")
  ))
  survival::coxph(fmla, data = d) %>%
    tbl_regression(exp = TRUE,
                   pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>%
    add_n()
}
```

## 5.1 Anemia Grade 2

```{r}
#| label: jx-csh-anemia2
csh_model("cmp_time_anemia_2", "cmp_status_anemia_2", "egfr_ratio_per10", "pre_HGB_45days")
```

## 5.2 Anemia Grade 3

```{r}
#| label: jx-csh-anemia3
csh_model("cmp_time_anemia_3", "cmp_status_anemia_3", "egfr_ratio_per10", "pre_HGB_45days")
```

## 5.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-csh-throm2
csh_model("cmp_time_throm_2", "cmp_status_throm_2", "egfr_ratio_per10", "pre_PLT_45days")
```

## 5.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-csh-throm3
csh_model("cmp_time_throm_3", "cmp_status_throm_3", "egfr_ratio_per10", "pre_PLT_45days")
```

## 5.5 AKI Grade 2

```{r}
#| label: jx-csh-aki2
csh_model("cmp_time_aki_2", "cmp_status_aki_2", "egfr_ratio_per10")
```

## 5.6 AKI (KDIGO)

```{r}
#| label: jx-csh-akikdigo
csh_model("cmp_time_aki_kdigo", "cmp_status_aki_kdigo", "egfr_ratio_per10")
```

## 5.7 Composite Grade 2 AEs

```{r}
#| label: jx-csh-grade2
csh_model("cmp_time_grade_2_aes", "cmp_status_grade_2_aes", "egfr_ratio_per10")
```

## 5.8 Composite Grade 3 AEs

```{r}
#| label: jx-csh-grade3
csh_model("cmp_time_grade_3_aes", "cmp_status_grade_3_aes", "egfr_ratio_per10")
```

## 5.9 Overall Hospitalization

```{r}
#| label: jx-csh-anyhosp
csh_model("cmp_time_any_hosp", "cmp_status_any_hosp", "egfr_ratio_per10")
```

## 5.10 Platinum-Related Hospitalization

```{r}
#| label: jx-csh-sideeffect
csh_model("cmp_time_side_effect", "cmp_status_side_effect", "egfr_ratio_per10")
```

## 5.11 90-Day Death (Cox PH)

```{r}
#| label: jx-csh-death
cox_model("time_to_death_90", "death_90", "egfr_ratio_per10", egfr_adj = "cockcroft")
```

::: {.callout-note}
## Why anchor at the median (subHR = 1 at the reference)

Three reasons to anchor at the **median**:

1. **Interpretability**: "A patient with eGFR ratio of 0.8 has ~1.5× the subHR compared to a typical patient (at the median)."
2. **Stability**: The median sits in the densest part of the data, so estimates near it have the tightest confidence intervals. The CIs fan out as you move away — you can see this in the plots.
3. **No arbitrary choice**: If we picked 1.0 arbitrarily, the plot would look almost identical here (because median ≈ 1), but in cohorts where the median is 0.9 or 1.1, picking 1.0 would either shift or distort the curve without changing the actual model.
:::

# 6 Linear subHR Curves — eGFR Ratio (raw scale)

```{r}
#| label: jx-linsubhr-helper
plot_subhr_linear_ratio <- function(time_var, status_var, extra_adj = NULL,
                                    outcome_label, x_axis = c("ratio","percentile")) {
  x_axis <- match.arg(x_axis)
  base_adj <- c("age","sex","score","ecog_score_cat2","cockcroft",
                "cancer_type_cat_7","tumor_stage","platin_group","high_dose",
                "Paclitaxel","Pemetrexed","Gemcitabine","ici",
                "bmi","smoking","steroids","thyroid")
  keep <- c("egfr_ratio", time_var, status_var, base_adj, extra_adj)
  d <- dat %>% dplyr::select(all_of(keep)) %>% tidyr::drop_na()

  adj_df <- d[, c(base_adj, extra_adj), drop = FALSE]
  X_adj <- model.matrix(~ ., data = adj_df)[, -1, drop = FALSE]
  X <- cbind(egfr_ratio = d$egfr_ratio, X_adj)

  stat_num <- suppressWarnings(as.integer(as.character(d[[status_var]])))
  time_num <- as.numeric(d[[time_var]])

  fit <- cmprsk::crr(ftime = time_num, fstatus = stat_num,
                     cov1 = X, failcode = 1)

  beta   <- fit$coef[1]
  V_beta <- fit$var[1, 1]

  ref_x  <- median(d$egfr_ratio, na.rm = TRUE)
  grid_x <- seq(quantile(d$egfr_ratio, 0.025, na.rm = TRUE),
                quantile(d$egfr_ratio, 0.975, na.rm = TRUE),
                length.out = 100)

  log_hr <- beta * (grid_x - ref_x)
  se     <- sqrt((grid_x - ref_x)^2 * V_beta)

  if (x_axis == "percentile") {
    ecdf_fn      <- ecdf(d$egfr_ratio)
    grid_display <- ecdf_fn(grid_x) * 100
    ref_display  <- ecdf_fn(ref_x)  * 100
    xlab <- "Percentile of eGFR Ratio"
  } else {
    grid_display <- grid_x
    ref_display  <- ref_x
    xlab <- "CKD-EPI Cr-Cys / CG ratio"
  }

  df_plot <- tibble(
    x     = grid_display,
    subhr = exp(log_hr),
    lcl   = exp(log_hr - 1.96 * se),
    ucl   = exp(log_hr + 1.96 * se)
  )

  p <- ggplot(df_plot, aes(x = x, y = subhr)) +
    geom_ribbon(aes(ymin = lcl, ymax = ucl), alpha = 0.2, fill = "darkorange") +
    geom_line(color = "darkorange", linewidth = 1) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "grey50") +
    geom_vline(xintercept = ref_display, linetype = "dotted", color = "grey40") +
    labs(x = xlab, y = "subHR (95% CI)", title = outcome_label) +
    theme_minimal(base_size = 11)

  if (x_axis == "ratio") {
    p <- p + coord_cartesian(xlim = c(0.65, 1.45), ylim = c(0, 4))
  } else {
    p <- p + coord_cartesian(xlim = c(0.65, 1.45), ylim = c(0, 4))
  }
  p
}

plot_cox_linear_ratio <- function(time_var, status_var, extra_adj = NULL,
                                  outcome_label, x_axis = c("ratio","percentile")) {
  x_axis <- match.arg(x_axis)
  base_adj <- c("age","sex","score","ecog_score_cat2","cockcroft",
                "cancer_type_cat_7","tumor_stage","platin_group","high_dose",
                "Paclitaxel","Pemetrexed","Gemcitabine","ici",
                "bmi","smoking","steroids","thyroid")
  keep <- c("egfr_ratio", time_var, status_var, base_adj, extra_adj)
  d <- dat %>% dplyr::select(all_of(keep)) %>% tidyr::drop_na()

  fmla <- as.formula(paste0(
    "Surv(", time_var, ", ", status_var, ") ~ egfr_ratio + ",
    paste(c(base_adj, extra_adj), collapse = " + ")
  ))
  fit <- survival::coxph(fmla, data = d)

  beta   <- coef(fit)["egfr_ratio"]
  V_beta <- vcov(fit)["egfr_ratio", "egfr_ratio"]

  ref_x  <- median(d$egfr_ratio, na.rm = TRUE)
  grid_x <- seq(quantile(d$egfr_ratio, 0.025, na.rm = TRUE),
                quantile(d$egfr_ratio, 0.975, na.rm = TRUE),
                length.out = 100)

  log_hr <- beta * (grid_x - ref_x)
  se     <- sqrt((grid_x - ref_x)^2 * V_beta)

  if (x_axis == "percentile") {
    ecdf_fn      <- ecdf(d$egfr_ratio)
    grid_display <- ecdf_fn(grid_x) * 100
    ref_display  <- ecdf_fn(ref_x)  * 100
    xlab <- "Percentile of eGFR Ratio"
  } else {
    grid_display <- grid_x
    ref_display  <- ref_x
    xlab <- "CKD-EPI Cr-Cys / CG ratio"
  }

  df_plot <- tibble(
    x   = grid_display,
    hr  = exp(log_hr),
    lcl = exp(log_hr - 1.96 * se),
    ucl = exp(log_hr + 1.96 * se)
  )

  p <- ggplot(df_plot, aes(x = x, y = hr)) +
    geom_ribbon(aes(ymin = lcl, ymax = ucl), alpha = 0.2, fill = "darkorange") +
    geom_line(color = "darkorange", linewidth = 1) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "grey50") +
    geom_vline(xintercept = ref_display, linetype = "dotted", color = "grey40") +
    labs(x = xlab, y = "HR (95% CI)", title = outcome_label) +
    theme_minimal(base_size = 11)

  if (x_axis == "ratio") {
    p <- p + coord_cartesian(xlim = c(0.65, 1.45), ylim = c(0, 4))
  } else {
    p <- p + coord_cartesian(xlim = c(0.65, 1.45), ylim = c(0, 4))
  }
  p
}
```

## 6.1 Anemia Grade 2

```{r}
#| label: jx-linsubhr-ratio-anemia2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_anemia_2", "cmp_status_anemia_2",
                        "pre_HGB_45days", "Anemia Grade 2", "ratio")
```

## 6.2 Anemia Grade 3

```{r}
#| label: jx-linsubhr-ratio-anemia3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_anemia_3", "cmp_status_anemia_3",
                        "pre_HGB_45days", "Anemia Grade 3", "ratio")
```

## 6.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-linsubhr-ratio-throm2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_throm_2", "cmp_status_throm_2",
                        "pre_PLT_45days", "Thrombocytopenia Grade 2", "ratio")
```

## 6.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-linsubhr-ratio-throm3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_throm_3", "cmp_status_throm_3",
                        "pre_PLT_45days", "Thrombocytopenia Grade 3", "ratio")
```

## 6.5 AKI Grade 2

```{r}
#| label: jx-linsubhr-ratio-aki2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_aki_2", "cmp_status_aki_2",
                        NULL, "AKI Grade 2", "ratio")
```

## 6.6 AKI (KDIGO)

```{r}
#| label: jx-linsubhr-ratio-akikdigo
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_aki_kdigo", "cmp_status_aki_kdigo",
                        NULL, "AKI (KDIGO)", "ratio")
```

## 6.7 Composite Grade 2 AEs

```{r}
#| label: jx-linsubhr-ratio-grade2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_grade_2_aes", "cmp_status_grade_2_aes",
                        NULL, "Composite Grade 2 AEs", "ratio")
```

## 6.8 Composite Grade 3 AEs

```{r}
#| label: jx-linsubhr-ratio-grade3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_grade_3_aes", "cmp_status_grade_3_aes",
                        NULL, "Composite Grade 3 AEs", "ratio")
```

## 6.9 Overall Hospitalization

```{r}
#| label: jx-linsubhr-ratio-anyhosp
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_any_hosp", "cmp_status_any_hosp",
                        NULL, "Overall Hospitalization", "ratio")
```

## 6.10 Platinum-Related Hospitalization

```{r}
#| label: jx-linsubhr-ratio-sideeffect
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_side_effect", "cmp_status_side_effect",
                        NULL, "Platinum-Related Hospitalization", "ratio")
```

## 6.11 90-Day Death (Cox PH)

```{r}
#| label: jx-cox-linear-ratio-death
#| fig-width: 6
#| fig-height: 4
plot_cox_linear_ratio("time_to_death_90", "death_90",
                      NULL, "90-Day Death (Cox PH)", "ratio")
```

# 7 Linear subHR Curves — eGFR Discrepancy (raw scale)

## 7.0 Summary table: Fine-Gray subHR per 10 mL/min decline in eGFR discrepancy

One row per outcome. Multivariable Fine-Gray model fit with `egfr_disc_per10dec = -egfr_discrepancy / 10` (positive when CKD-EPI Cr-Cys is below CG) plus the same adjusters used by the curves below. The HR for `egfr_disc_per10dec` is the multiplicative change in subHR per **10 mL/min lower** eGFR discrepancy. 90-day death uses Cox PH (no competing event); all other outcomes use Fine-Gray with death as the competing event. p-values are Wald.

[📄 Download Word table](../tables/whole/sec7_disc_summary.docx)

```{r}
#| label: jx-fg-disc-summary-whole
.disc_adj_set <- function(pre_labs = NULL) {
  base_adj <- c("age","sex","score","ecog_score_cat2",
                "cancer_type_cat_7","tumor_stage","platin_group","high_dose",
                "Paclitaxel","Pemetrexed","Gemcitabine","ici",
                "bmi","smoking","steroids","thyroid")
  if (!is.null(pre_labs)) base_adj <- c(base_adj, pre_labs)
  base_adj
}

fg_disc_row <- function(time_var, status_var, label, pre_labs = NULL) {
  adj <- .disc_adj_set(pre_labs)
  d <- dat %>%
    dplyr::select(all_of(c("egfr_disc_per10dec", time_var, status_var, adj))) %>%
    tidyr::drop_na()
  adj_df <- d[, adj, drop = FALSE]
  X_adj  <- model.matrix(~ ., data = adj_df)[, -1, drop = FALSE]
  X      <- cbind(egfr_disc_per10dec = d$egfr_disc_per10dec, X_adj)
  stat_num <- suppressWarnings(as.integer(as.character(d[[status_var]])))
  time_num <- as.numeric(d[[time_var]])
  fit <- cmprsk::crr(time_num, stat_num, cov1 = X, failcode = 1)
  b <- unname(fit$coef[1]); se <- sqrt(fit$var[1, 1])
  hr <- exp(b); lcl <- exp(b - 1.96 * se); ucl <- exp(b + 1.96 * se)
  pv <- 2 * (1 - pnorm(abs(b / se)))
  tibble(
    Outcome = label,
    Model   = "Fine-Gray",
    N       = nrow(d),
    Events  = sum(stat_num == 1, na.rm = TRUE),
    `(sub)HR (95% CI)` = sprintf("%.2f (%.2f, %.2f)", hr, lcl, ucl),
    `p-value` = ifelse(pv < 0.001, "<0.001", sprintf("%.3f", pv))
  )
}

cox_disc_row <- function(time_var, status_var, label, pre_labs = NULL) {
  adj <- .disc_adj_set(pre_labs)
  d <- dat %>%
    dplyr::select(all_of(c("egfr_disc_per10dec", time_var, status_var, adj))) %>%
    tidyr::drop_na()
  fmla <- as.formula(paste0("Surv(", time_var, ", ", status_var,
                            ") ~ egfr_disc_per10dec + ",
                            paste(adj, collapse = " + ")))
  fit <- survival::coxph(fmla, data = d)
  b   <- unname(coef(fit)["egfr_disc_per10dec"])
  se  <- sqrt(vcov(fit)["egfr_disc_per10dec", "egfr_disc_per10dec"])
  hr  <- exp(b); lcl <- exp(b - 1.96 * se); ucl <- exp(b + 1.96 * se)
  pv  <- 2 * (1 - pnorm(abs(b / se)))
  tibble(
    Outcome = label,
    Model   = "Cox PH",
    N       = nrow(d),
    Events  = sum(d[[status_var]] == 1, na.rm = TRUE),
    `(sub)HR (95% CI)` = sprintf("%.2f (%.2f, %.2f)", hr, lcl, ucl),
    `p-value` = ifelse(pv < 0.001, "<0.001", sprintf("%.3f", pv))
  )
}

disc_summary <- bind_rows(
  fg_disc_row ("cmp_time_anemia_2",     "cmp_status_anemia_2",     "Anemia Grade 2",                   "pre_HGB_45days"),
  fg_disc_row ("cmp_time_anemia_3",     "cmp_status_anemia_3",     "Anemia Grade 3",                   "pre_HGB_45days"),
  fg_disc_row ("cmp_time_throm_2",      "cmp_status_throm_2",      "Thrombocytopenia Grade 2",         "pre_PLT_45days"),
  fg_disc_row ("cmp_time_throm_3",      "cmp_status_throm_3",      "Thrombocytopenia Grade 3",         "pre_PLT_45days"),
  fg_disc_row ("cmp_time_aki_2",        "cmp_status_aki_2",        "AKI Grade 2"),
  fg_disc_row ("cmp_time_aki_kdigo",    "cmp_status_aki_kdigo",    "AKI (KDIGO)"),
  fg_disc_row ("cmp_time_grade_2_aes",  "cmp_status_grade_2_aes",  "Composite Grade 2 AEs"),
  fg_disc_row ("cmp_time_grade_3_aes",  "cmp_status_grade_3_aes",  "Composite Grade 3 AEs"),
  fg_disc_row ("cmp_time_any_hosp",     "cmp_status_any_hosp",     "Overall Hospitalization"),
  fg_disc_row ("cmp_time_side_effect",  "cmp_status_side_effect",  "Platinum-Related Hospitalization"),
  cox_disc_row("time_to_death_90",      "death_90",                "90-Day Death")
)

ft_disc <- flextable::flextable(disc_summary) |>
  flextable::set_caption("Multivariable (sub)HR per 10 mL/min decline in eGFR discrepancy (CKD-EPI Cr-Cys − Cockcroft-Gault). Fine-Gray for competing-risk outcomes; Cox PH for 90-day death.") |>
  flextable::autofit()
flextable::save_as_docx(ft_disc,
  path = file.path(docx_dir, "sec7_disc_summary.docx"))
ft_disc
```
```{r}
#| label: jx-linsubhr-disc-helper
plot_subhr_linear_disc <- function(time_var, status_var, extra_adj = NULL,
                                   outcome_label) {
  base_adj <- c("age","sex","score","ecog_score_cat2",
                "cancer_type_cat_7","tumor_stage","platin_group","high_dose",
                "Paclitaxel","Pemetrexed","Gemcitabine","ici",
                "bmi","smoking","steroids","thyroid")
  keep <- c("egfr_discrepancy", time_var, status_var, base_adj, extra_adj)
  d <- dat %>% dplyr::select(all_of(keep)) %>% tidyr::drop_na()

  adj_df <- d[, c(base_adj, extra_adj), drop = FALSE]
  X_adj <- model.matrix(~ ., data = adj_df)[, -1, drop = FALSE]
  X <- cbind(egfr_discrepancy = d$egfr_discrepancy, X_adj)

  stat_num <- suppressWarnings(as.integer(as.character(d[[status_var]])))
  time_num <- as.numeric(d[[time_var]])

  fit <- cmprsk::crr(ftime = time_num, fstatus = stat_num,
                     cov1 = X, failcode = 1)

  beta   <- fit$coef[1]
  V_beta <- fit$var[1, 1]
  se_b   <- sqrt(V_beta)

  # subHR summaries: per 1 mL/min, and per IQR (Q3 - Q1) of egfr_discrepancy
  q1    <- as.numeric(quantile(d$egfr_discrepancy, 0.25, na.rm = TRUE))
  q3    <- as.numeric(quantile(d$egfr_discrepancy, 0.75, na.rm = TRUE))
  iqr_w <- q3 - q1
  # per 10 mL/min DECLINE: HR = exp(-10 * beta); SE on log scale = 10 * se_b
  hr10  <- exp(-10 * beta);       hr10_l <- exp(-10 * beta - 1.96 * 10 * se_b);     hr10_u <- exp(-10 * beta + 1.96 * 10 * se_b)
  # per IQR DECLINE: HR = exp(-iqr_w * beta); SE on log scale = |iqr_w| * se_b
  hri   <- exp(-iqr_w * beta);    hri_l <- exp(-iqr_w * beta - 1.96 * abs(iqr_w) * se_b); hri_u <- exp(-iqr_w * beta + 1.96 * abs(iqr_w) * se_b)
  subtitle_str <- sprintf(
    "subHR per 10 mL/min decline: %.2f (%.2f-%.2f)  |  per IQR decline (Δ = %.1f): %.2f (%.2f-%.2f)  |  IQR: [%.1f, %.1f]",
    hr10, hr10_l, hr10_u, iqr_w, hri, hri_l, hri_u, q1, q3)

  ref_x  <- median(d$egfr_discrepancy, na.rm = TRUE)
  grid_x <- seq(quantile(d$egfr_discrepancy, 0.025, na.rm = TRUE),
                quantile(d$egfr_discrepancy, 0.975, na.rm = TRUE),
                length.out = 100)

  log_hr <- beta * (grid_x - ref_x)
  se     <- sqrt((grid_x - ref_x)^2 * V_beta)

  df_plot <- tibble(
    x     = grid_x,
    subhr = exp(log_hr),
    lcl   = exp(log_hr - 1.96 * se),
    ucl   = exp(log_hr + 1.96 * se)
  )

  ggplot(df_plot, aes(x = x, y = subhr)) +
    geom_ribbon(aes(ymin = lcl, ymax = ucl), alpha = 0.2, fill = "darkorange") +
    geom_line(color = "darkorange", linewidth = 1) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "grey50") +
    geom_vline(xintercept = ref_x, linetype = "dotted", color = "grey40") +
    geom_vline(xintercept = c(q1, q3), linetype = "dashed",
               color = "steelblue", alpha = 0.7) +
    labs(x = "eGFR Discrepancy (mL/min)",
         y = "subHR (95% CI)",
         title = outcome_label,
         subtitle = subtitle_str) +
    coord_cartesian(ylim = c(0, 4)) +
    theme_minimal(base_size = 11) +
    theme(plot.subtitle = element_text(size = 9, color = "grey25"))
}

plot_cox_linear_disc <- function(time_var, status_var, extra_adj = NULL,
                                 outcome_label) {
  base_adj <- c("age","sex","score","ecog_score_cat2",
                "cancer_type_cat_7","tumor_stage","platin_group","high_dose",
                "Paclitaxel","Pemetrexed","Gemcitabine","ici",
                "bmi","smoking","steroids","thyroid")
  keep <- c("egfr_discrepancy", time_var, status_var, base_adj, extra_adj)
  d <- dat %>% dplyr::select(all_of(keep)) %>% tidyr::drop_na()

  fmla <- as.formula(paste0(
    "Surv(", time_var, ", ", status_var, ") ~ egfr_discrepancy + ",
    paste(c(base_adj, extra_adj), collapse = " + ")
  ))
  fit <- survival::coxph(fmla, data = d)

  beta   <- coef(fit)["egfr_discrepancy"]
  V_beta <- vcov(fit)["egfr_discrepancy", "egfr_discrepancy"]
  se_b   <- sqrt(V_beta)

  q1    <- as.numeric(quantile(d$egfr_discrepancy, 0.25, na.rm = TRUE))
  q3    <- as.numeric(quantile(d$egfr_discrepancy, 0.75, na.rm = TRUE))
  iqr_w <- q3 - q1
  hr10  <- exp(-10 * beta);       hr10_l <- exp(-10 * beta - 1.96 * 10 * se_b);     hr10_u <- exp(-10 * beta + 1.96 * 10 * se_b)
  hri   <- exp(-iqr_w * beta);    hri_l <- exp(-iqr_w * beta - 1.96 * abs(iqr_w) * se_b); hri_u <- exp(-iqr_w * beta + 1.96 * abs(iqr_w) * se_b)
  subtitle_str <- sprintf(
    "HR per 10 mL/min decline: %.2f (%.2f-%.2f)  |  per IQR decline (Δ = %.1f): %.2f (%.2f-%.2f)  |  IQR: [%.1f, %.1f]",
    hr10, hr10_l, hr10_u, iqr_w, hri, hri_l, hri_u, q1, q3)

  ref_x  <- median(d$egfr_discrepancy, na.rm = TRUE)
  grid_x <- seq(quantile(d$egfr_discrepancy, 0.025, na.rm = TRUE),
                quantile(d$egfr_discrepancy, 0.975, na.rm = TRUE),
                length.out = 100)

  log_hr <- beta * (grid_x - ref_x)
  se     <- sqrt((grid_x - ref_x)^2 * V_beta)

  df_plot <- tibble(
    x   = grid_x,
    hr  = exp(log_hr),
    lcl = exp(log_hr - 1.96 * se),
    ucl = exp(log_hr + 1.96 * se)
  )

  ggplot(df_plot, aes(x = x, y = hr)) +
    geom_ribbon(aes(ymin = lcl, ymax = ucl), alpha = 0.2, fill = "darkorange") +
    geom_line(color = "darkorange", linewidth = 1) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "grey50") +
    geom_vline(xintercept = ref_x, linetype = "dotted", color = "grey40") +
    geom_vline(xintercept = c(q1, q3), linetype = "dashed",
               color = "steelblue", alpha = 0.7) +
    labs(x = "eGFR Discrepancy (mL/min)",
         y = "HR (95% CI)",
         title = outcome_label,
         subtitle = subtitle_str) +
    coord_cartesian(ylim = c(0, 4)) +
    theme_minimal(base_size = 11) +
    theme(plot.subtitle = element_text(size = 9, color = "grey25"))
}
```

## 7.1 Anemia Grade 2

```{r}
#| label: jx-linsubhr-disc-anemia2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_disc("cmp_time_anemia_2", "cmp_status_anemia_2",
                       "pre_HGB_45days", "Anemia Grade 2")
```

## 7.2 Anemia Grade 3

```{r}
#| label: jx-linsubhr-disc-anemia3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_disc("cmp_time_anemia_3", "cmp_status_anemia_3",
                       "pre_HGB_45days", "Anemia Grade 3")
```

## 7.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-linsubhr-disc-throm2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_disc("cmp_time_throm_2", "cmp_status_throm_2",
                       "pre_PLT_45days", "Thrombocytopenia Grade 2")
```

## 7.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-linsubhr-disc-throm3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_disc("cmp_time_throm_3", "cmp_status_throm_3",
                       "pre_PLT_45days", "Thrombocytopenia Grade 3")
```

## 7.5 AKI Grade 2

```{r}
#| label: jx-linsubhr-disc-aki2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_disc("cmp_time_aki_2", "cmp_status_aki_2",
                       NULL, "AKI Grade 2")
```

## 7.6 AKI (KDIGO)

```{r}
#| label: jx-linsubhr-disc-akikdigo
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_disc("cmp_time_aki_kdigo", "cmp_status_aki_kdigo",
                       NULL, "AKI (KDIGO)")
```

## 7.7 Composite Grade 2 AEs

```{r}
#| label: jx-linsubhr-disc-grade2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_disc("cmp_time_grade_2_aes", "cmp_status_grade_2_aes",
                       NULL, "Composite Grade 2 AEs")
```

## 7.8 Composite Grade 3 AEs

```{r}
#| label: jx-linsubhr-disc-grade3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_disc("cmp_time_grade_3_aes", "cmp_status_grade_3_aes",
                       NULL, "Composite Grade 3 AEs")
```

## 7.9 Overall Hospitalization

```{r}
#| label: jx-linsubhr-disc-anyhosp
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_disc("cmp_time_any_hosp", "cmp_status_any_hosp",
                       NULL, "Overall Hospitalization")
```

## 7.10 Platinum-Related Hospitalization

```{r}
#| label: jx-linsubhr-disc-sideeffect
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_disc("cmp_time_side_effect", "cmp_status_side_effect",
                       NULL, "Platinum-Related Hospitalization")
```

## 7.11 90-Day Death (Cox PH)

```{r}
#| label: jx-linsubhr-disc-death
#| fig-width: 6
#| fig-height: 4
plot_cox_linear_disc("time_to_death_90", "death_90",
                     NULL, "90-Day Death (Cox PH)")
```

# 8 Linear subHR Curves — Hospitalization by Reason

## 8.1 Nausea/Vomiting/GI

```{r}
#| label: jx-linsubhr-ratio-hosp1
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_hosp_1", "cmp_status_hosp_1",
                        NULL, "Nausea/Vomiting/GI")
```

## 8.2 Failure to Thrive/Fatigue/Dehydration

```{r}
#| label: jx-linsubhr-ratio-hosp2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_hosp_2", "cmp_status_hosp_2",
                        NULL, "Failure to Thrive/Fatigue/Dehydration")
```

## 8.3 AKI

```{r}
#| label: jx-linsubhr-ratio-hosp3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_hosp_3", "cmp_status_hosp_3",
                        NULL, "AKI")
```

## 8.4 Electrolyte Abnormalities

```{r}
#| label: jx-linsubhr-ratio-hosp4
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_hosp_4", "cmp_status_hosp_4",
                        NULL, "Electrolyte Abnormalities")
```

## 8.5 Cytopenia

```{r}
#| label: jx-linsubhr-ratio-hosp5
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_hosp_5", "cmp_status_hosp_5",
                        NULL, "Cytopenia")
```

## 8.6 Febrile Neutropenia

```{r}
#| label: jx-linsubhr-ratio-hosp6
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_hosp_6", "cmp_status_hosp_6",
                        NULL, "Febrile Neutropenia")
```

## 8.7 Infection/Sepsis

```{r}
#| label: jx-linsubhr-ratio-hosp7
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_hosp_7", "cmp_status_hosp_7",
                        NULL, "Infection/Sepsis")
```

## 8.8 Cancer Progression

```{r}
#| label: jx-linsubhr-ratio-hosp8
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_hosp_8", "cmp_status_hosp_8",
                        NULL, "Cancer Progression")
```

## 8.9 Immune-related AE & Other

Composite competing-risk outcome combining hospitalisations coded as Immune-related AE (reason 9) and Other (reason 11). Event = 1 if either occurred within 90 days; time = earliest of the two.

```{r}
#| label: jx-linsubhr-ratio-hosp-immune-other
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_hosp_immune_other",
                        "cmp_status_hosp_immune_other",
                        NULL, "Immune-related AE & Other")
```

## 8.10 Planned Surgery/Port

```{r}
#| label: jx-linsubhr-ratio-hosp10
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear_ratio("cmp_time_hosp_10", "cmp_status_hosp_10",
                        NULL, "Planned Surgery/Port")
```

# 9 Scatter Plots — eGFR Discrepancy

## 9.1 eGFR Discrepancy vs CKD-EPI Cr-Cys (unindexed)

```{r}
#| label: jx-scatter-egfr-epi
#| fig-width: 6
#| fig-height: 4
ggplot(dat %>% filter(!is.na(egfr_discrepancy)),
       aes(x = ckd_epi_gfr_cre_cys_unindex, y = egfr_discrepancy)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method = "lm", se = TRUE, color = "steelblue") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
  labs(x = "CKD-EPI Cr-Cys eGFR (unindexed, mL/min)",
       y = "eGFR Discrepancy (mL/min)",
       title = "eGFR Discrepancy vs CKD-EPI Cr-Cys eGFR") +
  theme_minimal(base_size = 11)
```

## 9.2 eGFR Discrepancy vs Cockcroft-Gault

```{r}
#| label: jx-scatter-egfr-cg
#| fig-width: 6
#| fig-height: 4
ggplot(dat %>% filter(!is.na(egfr_discrepancy)),
       aes(x = cockcroft, y = egfr_discrepancy)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method = "lm", se = TRUE, color = "steelblue") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
  labs(x = "Cockcroft-Gault eGFR (mL/min)",
       y = "eGFR Discrepancy (mL/min)",
       title = "eGFR Discrepancy vs Cockcroft-Gault eGFR") +
  theme_minimal(base_size = 11)
```


# 10 CG vs CKD-EPI Cr-Cys (highlighted by Age / BMI)

For each plot below, the x-axis is Cockcroft-Gault eGFR (mL/min) and the y-axis is CKD-EPI Cr-Cys *unindexed* eGFR (mL/min). The dashed line is `y = x` (perfect agreement). Patients meeting the highlighted threshold are coloured red; all others are grey. `N` shown in each title is the count of patients with both eGFR values non-missing; `n_red` is the count meeting the red criterion.

```{r}
#| label: jx-scatter-cg-epi-helper
plot_cg_vs_epi <- function(highlight_var, threshold, label) {
  d <- dat %>%
    filter(!is.na(cockcroft), !is.na(ckd_epi_gfr_cre_cys_unindex),
           !is.na(.data[[highlight_var]])) %>%
    mutate(highlight = .data[[highlight_var]] >= threshold)

  n_total <- nrow(d)
  n_red   <- sum(d$highlight)

  ggplot(d, aes(x = cockcroft, y = ckd_epi_gfr_cre_cys_unindex,
                color = highlight)) +
    geom_abline(slope = 1, intercept = 0, linetype = "dashed",
                color = "grey50") +
    geom_point(alpha = 0.6, size = 1.6) +
    scale_color_manual(values = c("FALSE" = "grey60", "TRUE" = "#E31A1C"),
                       guide = "none") +
    coord_cartesian(xlim = c(0, 200), ylim = c(0, 200)) +
    labs(x = "Cockcroft-Gault eGFR (mL/min)",
         y = "CKD-EPI Cr-Cys eGFR, unindexed (mL/min)",
         title = sprintf("%s   |   N = %d, n_red = %d",
                         label, n_total, n_red)) +
    theme_minimal(base_size = 11)
}
```

## 10.1 Age >= 70

```{r}
#| label: jx-scatter-cg-epi-age70
#| fig-width: 6
#| fig-height: 5
plot_cg_vs_epi("age", 70, "Age >= 70")
```

## 10.2 Age >= 75

```{r}
#| label: jx-scatter-cg-epi-age75
#| fig-width: 6
#| fig-height: 5
plot_cg_vs_epi("age", 75, "Age >= 75")
```

## 10.3 Age >= 80

```{r}
#| label: jx-scatter-cg-epi-age80
#| fig-width: 6
#| fig-height: 5
plot_cg_vs_epi("age", 80, "Age >= 80")
```

## 10.4 BMI >= 25

```{r}
#| label: jx-scatter-cg-epi-bmi25
#| fig-width: 6
#| fig-height: 5
plot_cg_vs_epi("bmi", 25, "BMI >= 25")
```

## 10.5 BMI >= 30

```{r}
#| label: jx-scatter-cg-epi-bmi30
#| fig-width: 6
#| fig-height: 5
plot_cg_vs_epi("bmi", 30, "BMI >= 30")
```

## 10.6 Sex

```{r}
#| label: jx-scatter-cg-epi-sex
#| fig-width: 6
#| fig-height: 5
d_sex <- dat %>%
  filter(!is.na(cockcroft), !is.na(ckd_epi_gfr_cre_cys_unindex), !is.na(sex))

ggplot(d_sex, aes(x = cockcroft, y = ckd_epi_gfr_cre_cys_unindex,
                  color = sex)) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed",
              color = "grey50") +
  geom_point(alpha = 0.6, size = 1.6) +
  scale_color_manual(values = c("Female" = "#E31A1C", "Male" = "grey60")) +
  coord_cartesian(xlim = c(0, 200), ylim = c(0, 200)) +
  labs(x = "Cockcroft-Gault eGFR (mL/min)",
       y = "CKD-EPI Cr-Cys eGFR, unindexed (mL/min)",
       color = NULL,
       title = sprintf("Sex   |   N = %d (Female %d, Male %d)",
                       nrow(d_sex),
                       sum(d_sex$sex == "Female"),
                       sum(d_sex$sex == "Male"))) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "top")
```
