---
title: "Jiaxuan Project — Carboplatin Cohort"
author: "Tianqi Ouyang"
date: "2026-04-09"
execute:
  eval: true
  warning: false
  message: false
---

# 1 Setup

```{r}
#| label: setup-jx-carbo
# Force UTF-8 locale so kable captions and other strings render real Unicode
# (e.g. em-dash) instead of <U+2014> escape sequences.
invisible(Sys.setlocale("LC_ALL", "en_US.UTF-8"))
library(tidyverse)
library(scales)
library(ggplot2)
library(tidycmprsk)
library(ggsurvfit)
library(gtsummary)

# Load whole-cohort data, then keep only carboplatin patients
dat <- readRDS("jiaxuan_final_master.rds") %>%
  filter(platin_group == "Carboplatin")

# Create eGFR ratio: CKD-EPI Cr-Cys (unindexed) / Cockcroft-Gault
# Also create per-10 mL/min rescaled versions of cockcroft and CKD-EPI for
# reporting (HRs per 1 mL/min are clinically uninterpretable; convention in
# nephro-onc is per 10 mL/min — bio_agent confirmed). Adjusters keep raw scale.
dat <- dat %>%
  mutate(
    egfr_ratio    = ckd_epi_gfr_cre_cys_unindex / cockcroft,
    egfr_ratio_per10 = -egfr_ratio * 10,  # per 0.1-unit *decrease* reporting scale
    cockcroft_per10 = cockcroft / 10,
    ckd_epi_per10   = ckd_epi_gfr_cre_cys_unindex / 10
  )

cat("Carboplatin cohort N =", nrow(dat), "\n")
```

# 2 Table 1: Baseline Characteristics (Carboplatin Only)

```{r}
#| label: jx-table1-carbo
dat %>%
  dplyr::select(
    age, age_cat, sex, race, ethnicity, tumor_stage, cancer_type_cat_7,
    carbo_AUC, carbo_AUC_cat,
    ici, Bevacizumab, Paclitaxel, Pemetrexed, Doxorubicin, Etoposide,
    Gemcitabine, Pertuzumab, Trastuzumab, Docetaxel, Administered_alone,
    hiv_rpdr, thyroid, smoking, steroids,
    cci, ecog_score, bmi, bmi_cat,
    pre_HGB_45days, pre_PLT_45days, pre_ALB_45days,
    baseline_cys_c, baseline_cre, cr_cys,
    baseline_cre_egfr, baseline_cys_c_egfr,
    ckd_epi_gfr_cre_cys, ckd_epi_gfr_cre_cys_unindex,
    cockcroft, egfr_ratio
  ) %>%
  tbl_summary(
    statistic = list(age ~ "{mean} ({sd})")
  )
```

# 3 Fine-Gray Models — eGFR Ratio (CR-CYS / CG) (Carboplatin)

```{r}
#| label: jx-carbo-fg-helper
fg_model <- function(time_var, status_var, pred_var, pre_labs = NULL) {
  adj <- c("age","sex","score","ecog_score_cat2","cockcroft",
           "cancer_type_cat_7","tumor_stage","high_dose",
           "Paclitaxel","Pemetrexed","Gemcitabine",
           "bmi","smoking","steroids","thyroid")
  # Drop cockcroft from adjusters when it (or its rescaled version) is the predictor
  if (pred_var %in% c("cockcroft","cockcroft_per10")) {
    adj <- setdiff(adj, "cockcroft")
  }
  if (!is.null(pre_labs)) adj <- c(adj, pre_labs)
  fmla <- as.formula(paste0(
    "Surv(", time_var, ", ", status_var, ") ~ ",
    paste(c(pred_var, adj), collapse = " + ")
  ))
  tidycmprsk::crr(fmla, failcode = 1, data = dat) %>%
    tbl_regression(exp = TRUE,
                   pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>%
    add_n()
}

cox_model <- function(time_var, status_var, pred_var, pre_labs = NULL) {
  adj <- c("age","sex","score","ecog_score_cat2","cockcroft",
           "cancer_type_cat_7","tumor_stage","high_dose",
           "Paclitaxel","Pemetrexed","Gemcitabine",
           "bmi","smoking","steroids","thyroid")
  if (pred_var %in% c("cockcroft","cockcroft_per10")) {
    adj <- setdiff(adj, "cockcroft")
  }
  if (!is.null(pre_labs)) adj <- c(adj, pre_labs)
  fmla <- as.formula(paste0(
    "Surv(", time_var, ", ", status_var, ") ~ ",
    paste(c(pred_var, adj), collapse = " + ")
  ))
  survival::coxph(fmla, data = dat) %>%
    tbl_regression(exp = TRUE,
                   pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>%
    add_n()
}
```

## 3.1 Anemia Grade 2

```{r}
#| label: jx-carbo-fg-ratio-anemia2
fg_model("cmp_time_anemia_2", "cmp_status_anemia_2", "egfr_ratio_per10", "pre_HGB_45days")
```

## 3.2 Anemia Grade 3

```{r}
#| label: jx-carbo-fg-ratio-anemia3
fg_model("cmp_time_anemia_3", "cmp_status_anemia_3", "egfr_ratio_per10", "pre_HGB_45days")
```

## 3.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-carbo-fg-ratio-throm2
fg_model("cmp_time_throm_2", "cmp_status_throm_2", "egfr_ratio_per10", "pre_PLT_45days")
```

## 3.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-carbo-fg-ratio-throm3
fg_model("cmp_time_throm_3", "cmp_status_throm_3", "egfr_ratio_per10", "pre_PLT_45days")
```

## 3.5 AKI Grade 2

```{r}
#| label: jx-carbo-fg-ratio-aki2
fg_model("cmp_time_aki_2", "cmp_status_aki_2", "egfr_ratio_per10")
```

## 3.6 AKI (KDIGO)

```{r}
#| label: jx-carbo-fg-ratio-akikdigo
fg_model("cmp_time_aki_kdigo", "cmp_status_aki_kdigo", "egfr_ratio_per10")
```

## 3.7 Composite Grade 2 AEs

```{r}
#| label: jx-carbo-fg-ratio-grade2
fg_model("cmp_time_grade_2_aes", "cmp_status_grade_2_aes", "egfr_ratio_per10")
```

## 3.8 Composite Grade 3 AEs

```{r}
#| label: jx-carbo-fg-ratio-grade3
fg_model("cmp_time_grade_3_aes", "cmp_status_grade_3_aes", "egfr_ratio_per10")
```

## 3.9 Overall Hospitalization

```{r}
#| label: jx-carbo-fg-ratio-anyhosp
fg_model("cmp_time_any_hosp", "cmp_status_any_hosp", "egfr_ratio_per10")
```

## 3.10 Platinum-Related Hospitalization

```{r}
#| label: jx-carbo-fg-ratio-sideeffect
fg_model("cmp_time_side_effect", "cmp_status_side_effect", "egfr_ratio_per10")
```

## 3.11 90-Day Death

```{r}
#| label: jx-carbo-cox-ratio-death
cox_model("time_to_death_90", "death_90", "egfr_ratio_per10")
```

# 4 Fine-Gray Models — Cockcroft-Gault eGFR (per 10 mL/min, Carboplatin)

## 4.1 Anemia Grade 2

```{r}
#| label: jx-carbo-fg-cg-anemia2
fg_model("cmp_time_anemia_2", "cmp_status_anemia_2", "cockcroft_per10", "pre_HGB_45days")
```

## 4.2 Anemia Grade 3

```{r}
#| label: jx-carbo-fg-cg-anemia3
fg_model("cmp_time_anemia_3", "cmp_status_anemia_3", "cockcroft_per10", "pre_HGB_45days")
```

## 4.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-carbo-fg-cg-throm2
fg_model("cmp_time_throm_2", "cmp_status_throm_2", "cockcroft_per10", "pre_PLT_45days")
```

## 4.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-carbo-fg-cg-throm3
fg_model("cmp_time_throm_3", "cmp_status_throm_3", "cockcroft_per10", "pre_PLT_45days")
```

## 4.5 AKI Grade 2

```{r}
#| label: jx-carbo-fg-cg-aki2
fg_model("cmp_time_aki_2", "cmp_status_aki_2", "cockcroft_per10")
```

## 4.6 AKI (KDIGO)

```{r}
#| label: jx-carbo-fg-cg-akikdigo
fg_model("cmp_time_aki_kdigo", "cmp_status_aki_kdigo", "cockcroft_per10")
```

## 4.7 Composite Grade 2 AEs

```{r}
#| label: jx-carbo-fg-cg-grade2
fg_model("cmp_time_grade_2_aes", "cmp_status_grade_2_aes", "cockcroft_per10")
```

## 4.8 Composite Grade 3 AEs

```{r}
#| label: jx-carbo-fg-cg-grade3
fg_model("cmp_time_grade_3_aes", "cmp_status_grade_3_aes", "cockcroft_per10")
```

## 4.9 Overall Hospitalization

```{r}
#| label: jx-carbo-fg-cg-anyhosp
fg_model("cmp_time_any_hosp", "cmp_status_any_hosp", "cockcroft_per10")
```

## 4.10 Platinum-Related Hospitalization

```{r}
#| label: jx-carbo-fg-cg-sideeffect
fg_model("cmp_time_side_effect", "cmp_status_side_effect", "cockcroft_per10")
```

## 4.11 90-Day Death

```{r}
#| label: jx-carbo-cox-cg-death
cox_model("time_to_death_90", "death_90", "cockcroft_per10")
```

# 5 Fine-Gray Models — CKD-EPI Cr-Cys (unindexed) eGFR (per 10 mL/min, Carboplatin)

## 5.1 Anemia Grade 2

```{r}
#| label: jx-carbo-fg-epi-anemia2
fg_model("cmp_time_anemia_2", "cmp_status_anemia_2", "ckd_epi_per10", "pre_HGB_45days")
```

## 5.2 Anemia Grade 3

```{r}
#| label: jx-carbo-fg-epi-anemia3
fg_model("cmp_time_anemia_3", "cmp_status_anemia_3", "ckd_epi_per10", "pre_HGB_45days")
```

## 5.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-carbo-fg-epi-throm2
fg_model("cmp_time_throm_2", "cmp_status_throm_2", "ckd_epi_per10", "pre_PLT_45days")
```

## 5.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-carbo-fg-epi-throm3
fg_model("cmp_time_throm_3", "cmp_status_throm_3", "ckd_epi_per10", "pre_PLT_45days")
```

## 5.5 AKI Grade 2

```{r}
#| label: jx-carbo-fg-epi-aki2
fg_model("cmp_time_aki_2", "cmp_status_aki_2", "ckd_epi_per10")
```

## 5.6 AKI (KDIGO)

```{r}
#| label: jx-carbo-fg-epi-akikdigo
fg_model("cmp_time_aki_kdigo", "cmp_status_aki_kdigo", "ckd_epi_per10")
```

## 5.7 Composite Grade 2 AEs

```{r}
#| label: jx-carbo-fg-epi-grade2
fg_model("cmp_time_grade_2_aes", "cmp_status_grade_2_aes", "ckd_epi_per10")
```

## 5.8 Composite Grade 3 AEs

```{r}
#| label: jx-carbo-fg-epi-grade3
fg_model("cmp_time_grade_3_aes", "cmp_status_grade_3_aes", "ckd_epi_per10")
```

## 5.9 Overall Hospitalization

```{r}
#| label: jx-carbo-fg-epi-anyhosp
fg_model("cmp_time_any_hosp", "cmp_status_any_hosp", "ckd_epi_per10")
```

## 5.10 Platinum-Related Hospitalization

```{r}
#| label: jx-carbo-fg-epi-sideeffect
fg_model("cmp_time_side_effect", "cmp_status_side_effect", "ckd_epi_per10")
```

## 5.11 90-Day Death

```{r}
#| label: jx-carbo-cox-epi-death
cox_model("time_to_death_90", "death_90", "ckd_epi_per10")
```

# 6 subHR Curves — Dose Discrepancy (Carboplatin)

```{r}
#| label: jx-carbo-subhr-helper
suppressPackageStartupMessages(library(splines))

plot_subhr <- function(time_var, status_var, extra_adj = NULL, outcome_label) {
  base_adj <- c("age","sex","score","ecog_score_cat2","cockcroft",
                "cancer_type_cat_7","tumor_stage","high_dose",
                "Paclitaxel","Pemetrexed","Gemcitabine",
                "bmi","smoking","steroids","thyroid")
  keep <- c("dose_discrepancy", time_var, status_var, base_adj, extra_adj)
  d <- dat %>% dplyr::select(all_of(keep)) %>% tidyr::drop_na()

  ns_b <- ns(d$dose_discrepancy, df = 3)
  knots_in <- attr(ns_b, "knots")
  bdry     <- attr(ns_b, "Boundary.knots")
  colnames(ns_b) <- c("ns1","ns2","ns3")

  adj_df <- d[, c(base_adj, extra_adj), drop = FALSE]
  X_adj <- model.matrix(~ ., data = adj_df)[, -1, drop = FALSE]
  X <- cbind(as.matrix(ns_b), X_adj)

  stat_num <- suppressWarnings(as.integer(as.character(d[[status_var]])))
  time_num <- as.numeric(d[[time_var]])

  fit <- cmprsk::crr(ftime = time_num, fstatus = stat_num,
                     cov1 = X, failcode = 1)

  grid_x <- seq(quantile(d$dose_discrepancy, 0.02, na.rm = TRUE),
                quantile(d$dose_discrepancy, 0.98, na.rm = TRUE),
                length.out = 100)
  ref_x  <- median(d$dose_discrepancy, na.rm = TRUE)

  ns_grid <- predict(ns(d$dose_discrepancy, knots = knots_in, Boundary.knots = bdry),
                     grid_x)
  ns_ref  <- predict(ns(d$dose_discrepancy, knots = knots_in, Boundary.knots = bdry),
                     ref_x)
  ns_diff <- sweep(as.matrix(ns_grid), 2, as.vector(ns_ref), "-")

  coef_ns <- fit$coef[1:3]
  V_ns    <- fit$var[1:3, 1:3]

  log_hr <- as.vector(ns_diff %*% coef_ns)
  se     <- sqrt(pmax(diag(ns_diff %*% V_ns %*% t(ns_diff)), 0))

  df_plot <- tibble(
    discrepancy = grid_x,
    subhr = exp(log_hr),
    lcl   = exp(log_hr - 1.96 * se),
    ucl   = exp(log_hr + 1.96 * se)
  )

  ggplot(df_plot, aes(x = discrepancy, y = subhr)) +
    geom_ribbon(aes(ymin = lcl, ymax = ucl), alpha = 0.2, fill = "steelblue") +
    geom_line(color = "steelblue", linewidth = 1) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "grey50") +
    geom_vline(xintercept = ref_x, linetype = "dotted", color = "grey40") +
    labs(x = "Dose Discrepancy (mg)",
         y = "subHR (95% CI)",
         title = outcome_label) +
    coord_cartesian(ylim = c(0, 4)) +
    theme_minimal(base_size = 11)
}

plot_cox_spline <- function(time_var, status_var, extra_adj = NULL, outcome_label) {
  base_adj <- c("age","sex","score","ecog_score_cat2","cockcroft",
                "cancer_type_cat_7","tumor_stage","high_dose",
                "Paclitaxel","Pemetrexed","Gemcitabine",
                "bmi","smoking","steroids","thyroid")
  keep <- c("dose_discrepancy", time_var, status_var, base_adj, extra_adj)
  d <- dat %>% dplyr::select(all_of(keep)) %>% tidyr::drop_na()

  fmla <- as.formula(paste0(
    "Surv(", time_var, ", ", status_var, ") ~ ns(dose_discrepancy, df = 3) + ",
    paste(c(base_adj, extra_adj), collapse = " + ")
  ))
  fit <- survival::coxph(fmla, data = d)

  grid_x <- seq(quantile(d$dose_discrepancy, 0.02, na.rm = TRUE),
                quantile(d$dose_discrepancy, 0.98, na.rm = TRUE),
                length.out = 100)
  ref_x  <- median(d$dose_discrepancy, na.rm = TRUE)

  ns_b     <- ns(d$dose_discrepancy, df = 3)
  knots_in <- attr(ns_b, "knots")
  bdry     <- attr(ns_b, "Boundary.knots")

  ns_grid <- predict(ns(d$dose_discrepancy, knots = knots_in, Boundary.knots = bdry), grid_x)
  ns_ref  <- predict(ns(d$dose_discrepancy, knots = knots_in, Boundary.knots = bdry), ref_x)
  ns_diff <- sweep(as.matrix(ns_grid), 2, as.vector(ns_ref), "-")

  coef_ns <- coef(fit)[1:3]
  V_ns    <- vcov(fit)[1:3, 1:3]

  log_hr <- as.vector(ns_diff %*% coef_ns)
  se     <- sqrt(pmax(diag(ns_diff %*% V_ns %*% t(ns_diff)), 0))

  df_plot <- tibble(
    discrepancy = grid_x,
    hr    = exp(log_hr),
    lcl   = exp(log_hr - 1.96 * se),
    ucl   = exp(log_hr + 1.96 * se)
  )

  ggplot(df_plot, aes(x = discrepancy, y = hr)) +
    geom_ribbon(aes(ymin = lcl, ymax = ucl), alpha = 0.2, fill = "steelblue") +
    geom_line(color = "steelblue", linewidth = 1) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "grey50") +
    geom_vline(xintercept = ref_x, linetype = "dotted", color = "grey40") +
    labs(x = "Dose Discrepancy (mg)",
         y = "HR (95% CI)",
         title = outcome_label) +
    coord_cartesian(ylim = c(0, 4)) +
    theme_minimal(base_size = 11)
}
```

## 6.1 Anemia Grade 2

```{r}
#| label: jx-carbo-subhr-anemia2
#| fig-width: 6
#| fig-height: 4
plot_subhr("cmp_time_anemia_2", "cmp_status_anemia_2",
           "pre_HGB_45days", "Anemia Grade 2 (Carboplatin)")
```

## 6.2 Anemia Grade 3

```{r}
#| label: jx-carbo-subhr-anemia3
#| fig-width: 6
#| fig-height: 4
plot_subhr("cmp_time_anemia_3", "cmp_status_anemia_3",
           "pre_HGB_45days", "Anemia Grade 3 (Carboplatin)")
```

## 6.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-carbo-subhr-throm2
#| fig-width: 6
#| fig-height: 4
plot_subhr("cmp_time_throm_2", "cmp_status_throm_2",
           "pre_PLT_45days", "Thrombocytopenia Grade 2 (Carboplatin)")
```

## 6.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-carbo-subhr-throm3
#| fig-width: 6
#| fig-height: 4
plot_subhr("cmp_time_throm_3", "cmp_status_throm_3",
           "pre_PLT_45days", "Thrombocytopenia Grade 3 (Carboplatin)")
```

## 6.5 AKI Grade 2

```{r}
#| label: jx-carbo-subhr-aki2
#| fig-width: 6
#| fig-height: 4
plot_subhr("cmp_time_aki_2", "cmp_status_aki_2",
           NULL, "AKI Grade 2 (Carboplatin)")
```

## 6.6 AKI (KDIGO)

```{r}
#| label: jx-carbo-subhr-akikdigo
#| fig-width: 6
#| fig-height: 4
plot_subhr("cmp_time_aki_kdigo", "cmp_status_aki_kdigo",
           NULL, "AKI KDIGO (Carboplatin)")
```

## 6.7 Composite Grade 2 AEs

```{r}
#| label: jx-carbo-subhr-grade2
#| fig-width: 6
#| fig-height: 4
plot_subhr("cmp_time_grade_2_aes", "cmp_status_grade_2_aes",
           NULL, "Composite Grade 2 AEs (Carboplatin)")
```

## 6.8 Composite Grade 3 AEs

```{r}
#| label: jx-carbo-subhr-grade3
#| fig-width: 6
#| fig-height: 4
plot_subhr("cmp_time_grade_3_aes", "cmp_status_grade_3_aes",
           NULL, "Composite Grade 3 AEs (Carboplatin)")
```

## 6.9 Overall Hospitalization

```{r}
#| label: jx-carbo-subhr-anyhosp
#| fig-width: 6
#| fig-height: 4
plot_subhr("cmp_time_any_hosp", "cmp_status_any_hosp",
           NULL, "Overall Hospitalization (Carboplatin)")
```

## 6.10 Platinum-Related Hospitalization

```{r}
#| label: jx-carbo-subhr-sideeffect
#| fig-width: 6
#| fig-height: 4
plot_subhr("cmp_time_side_effect", "cmp_status_side_effect",
           NULL, "Platinum-Related Hospitalization (Carboplatin)")
```

## 6.11 90-Day Death

```{r}
#| label: jx-carbo-cox-spline-death
#| fig-width: 6
#| fig-height: 4
plot_cox_spline("time_to_death_90", "death_90",
                NULL, "90-Day Death (Carboplatin)")
```

# 7 Linear subHR Curves — Dose Discrepancy (raw scale, Carboplatin)

```{r}
#| label: jx-carbo-linsubhr-helper
plot_subhr_linear <- function(time_var, status_var, extra_adj = NULL,
                              outcome_label, x_axis = c("discrepancy","percentile")) {
  x_axis <- match.arg(x_axis)
  base_adj <- c("age","sex","score","ecog_score_cat2","cockcroft",
                "cancer_type_cat_7","tumor_stage","high_dose",
                "Paclitaxel","Pemetrexed","Gemcitabine",
                "bmi","smoking","steroids","thyroid")
  keep <- c("dose_discrepancy", time_var, status_var, base_adj, extra_adj)
  d <- dat %>% dplyr::select(all_of(keep)) %>% tidyr::drop_na()

  adj_df <- d[, c(base_adj, extra_adj), drop = FALSE]
  X_adj <- model.matrix(~ ., data = adj_df)[, -1, drop = FALSE]
  X <- cbind(dose_discrepancy = d$dose_discrepancy, X_adj)

  stat_num <- suppressWarnings(as.integer(as.character(d[[status_var]])))
  time_num <- as.numeric(d[[time_var]])

  fit <- cmprsk::crr(ftime = time_num, fstatus = stat_num,
                     cov1 = X, failcode = 1)

  beta   <- fit$coef[1]
  V_beta <- fit$var[1, 1]

  ref_x  <- median(d$dose_discrepancy, na.rm = TRUE)
  grid_x <- seq(quantile(d$dose_discrepancy, 0.02, na.rm = TRUE),
                quantile(d$dose_discrepancy, 0.98, na.rm = TRUE),
                length.out = 100)

  log_hr <- beta * (grid_x - ref_x)
  se     <- sqrt((grid_x - ref_x)^2 * V_beta)

  if (x_axis == "percentile") {
    ecdf_fn      <- ecdf(d$dose_discrepancy)
    grid_display <- ecdf_fn(grid_x) * 100
    ref_display  <- ecdf_fn(ref_x)  * 100
    xlab <- "Percentile of Dose Discrepancy"
  } else {
    grid_display <- grid_x
    ref_display  <- ref_x
    xlab <- "Dose Discrepancy (mg)"
  }

  df_plot <- tibble(
    x     = grid_display,
    subhr = exp(log_hr),
    lcl   = exp(log_hr - 1.96 * se),
    ucl   = exp(log_hr + 1.96 * se)
  )

  ggplot(df_plot, aes(x = x, y = subhr)) +
    geom_ribbon(aes(ymin = lcl, ymax = ucl), alpha = 0.2, fill = "darkorange") +
    geom_line(color = "darkorange", linewidth = 1) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "grey50") +
    geom_vline(xintercept = ref_display, linetype = "dotted", color = "grey40") +
    labs(x = xlab, y = "subHR (95% CI)", title = outcome_label) +
    coord_cartesian(ylim = c(0, 4)) +
    theme_minimal(base_size = 11)
}

plot_cox_linear <- function(time_var, status_var, extra_adj = NULL,
                            outcome_label, x_axis = c("discrepancy","percentile")) {
  x_axis <- match.arg(x_axis)
  base_adj <- c("age","sex","score","ecog_score_cat2","cockcroft",
                "cancer_type_cat_7","tumor_stage","high_dose",
                "Paclitaxel","Pemetrexed","Gemcitabine",
                "bmi","smoking","steroids","thyroid")
  keep <- c("dose_discrepancy", time_var, status_var, base_adj, extra_adj)
  d <- dat %>% dplyr::select(all_of(keep)) %>% tidyr::drop_na()

  fmla <- as.formula(paste0(
    "Surv(", time_var, ", ", status_var, ") ~ dose_discrepancy + ",
    paste(c(base_adj, extra_adj), collapse = " + ")
  ))
  fit <- survival::coxph(fmla, data = d)

  beta   <- coef(fit)["dose_discrepancy"]
  V_beta <- vcov(fit)["dose_discrepancy", "dose_discrepancy"]

  ref_x  <- median(d$dose_discrepancy, na.rm = TRUE)
  grid_x <- seq(quantile(d$dose_discrepancy, 0.02, na.rm = TRUE),
                quantile(d$dose_discrepancy, 0.98, na.rm = TRUE),
                length.out = 100)

  log_hr <- beta * (grid_x - ref_x)
  se     <- sqrt((grid_x - ref_x)^2 * V_beta)

  if (x_axis == "percentile") {
    ecdf_fn      <- ecdf(d$dose_discrepancy)
    grid_display <- ecdf_fn(grid_x) * 100
    ref_display  <- ecdf_fn(ref_x)  * 100
    xlab <- "Percentile of Dose Discrepancy"
  } else {
    grid_display <- grid_x
    ref_display  <- ref_x
    xlab <- "Dose Discrepancy (mg)"
  }

  df_plot <- tibble(
    x   = grid_display,
    hr  = exp(log_hr),
    lcl = exp(log_hr - 1.96 * se),
    ucl = exp(log_hr + 1.96 * se)
  )

  ggplot(df_plot, aes(x = x, y = hr)) +
    geom_ribbon(aes(ymin = lcl, ymax = ucl), alpha = 0.2, fill = "darkorange") +
    geom_line(color = "darkorange", linewidth = 1) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "grey50") +
    geom_vline(xintercept = ref_display, linetype = "dotted", color = "grey40") +
    labs(x = xlab, y = "HR (95% CI)", title = outcome_label) +
    coord_cartesian(
      ylim = c(0, 4)
    ) +
    theme_minimal(base_size = 11)
}
```

## 7.1 Anemia Grade 2

```{r}
#| label: jx-carbo-linsubhr-anemia2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_anemia_2", "cmp_status_anemia_2",
                  "pre_HGB_45days", "Anemia Grade 2 (Carboplatin)", "discrepancy")
```

## 7.2 Anemia Grade 3

```{r}
#| label: jx-carbo-linsubhr-anemia3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_anemia_3", "cmp_status_anemia_3",
                  "pre_HGB_45days", "Anemia Grade 3 (Carboplatin)", "discrepancy")
```

## 7.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-carbo-linsubhr-throm2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_throm_2", "cmp_status_throm_2",
                  "pre_PLT_45days", "Thrombocytopenia Grade 2 (Carboplatin)", "discrepancy")
```

## 7.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-carbo-linsubhr-throm3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_throm_3", "cmp_status_throm_3",
                  "pre_PLT_45days", "Thrombocytopenia Grade 3 (Carboplatin)", "discrepancy")
```

## 7.5 AKI Grade 2

```{r}
#| label: jx-carbo-linsubhr-aki2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_aki_2", "cmp_status_aki_2",
                  NULL, "AKI Grade 2 (Carboplatin)", "discrepancy")
```

## 7.6 AKI (KDIGO)

```{r}
#| label: jx-carbo-linsubhr-akikdigo
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_aki_kdigo", "cmp_status_aki_kdigo",
                  NULL, "AKI KDIGO (Carboplatin)", "discrepancy")
```

## 7.7 Composite Grade 2 AEs

```{r}
#| label: jx-carbo-linsubhr-grade2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_grade_2_aes", "cmp_status_grade_2_aes",
                  NULL, "Composite Grade 2 AEs (Carboplatin)", "discrepancy")
```

## 7.8 Composite Grade 3 AEs

```{r}
#| label: jx-carbo-linsubhr-grade3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_grade_3_aes", "cmp_status_grade_3_aes",
                  NULL, "Composite Grade 3 AEs (Carboplatin)", "discrepancy")
```

## 7.9 Overall Hospitalization

```{r}
#| label: jx-carbo-linsubhr-anyhosp
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_any_hosp", "cmp_status_any_hosp",
                  NULL, "Overall Hospitalization (Carboplatin)", "discrepancy")
```

## 7.10 Platinum-Related Hospitalization

```{r}
#| label: jx-carbo-linsubhr-sideeffect
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_side_effect", "cmp_status_side_effect",
                  NULL, "Platinum-Related Hospitalization (Carboplatin)", "discrepancy")
```

## 7.11 90-Day Death

```{r}
#| label: jx-carbo-cox-linear-death
#| fig-width: 6
#| fig-height: 4
plot_cox_linear("time_to_death_90", "death_90",
                NULL, "90-Day Death (Carboplatin)", "discrepancy")
```

# 8 Linear subHR Curves — Dose Discrepancy (percentile x-axis, Carboplatin)

## 8.1 Anemia Grade 2

```{r}
#| label: jx-carbo-linsubhr-pct-anemia2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_anemia_2", "cmp_status_anemia_2",
                  "pre_HGB_45days", "Anemia Grade 2 (Carboplatin)", "percentile")
```

## 8.2 Anemia Grade 3

```{r}
#| label: jx-carbo-linsubhr-pct-anemia3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_anemia_3", "cmp_status_anemia_3",
                  "pre_HGB_45days", "Anemia Grade 3 (Carboplatin)", "percentile")
```

## 8.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-carbo-linsubhr-pct-throm2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_throm_2", "cmp_status_throm_2",
                  "pre_PLT_45days", "Thrombocytopenia Grade 2 (Carboplatin)", "percentile")
```

## 8.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-carbo-linsubhr-pct-throm3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_throm_3", "cmp_status_throm_3",
                  "pre_PLT_45days", "Thrombocytopenia Grade 3 (Carboplatin)", "percentile")
```

## 8.5 AKI Grade 2

```{r}
#| label: jx-carbo-linsubhr-pct-aki2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_aki_2", "cmp_status_aki_2",
                  NULL, "AKI Grade 2 (Carboplatin)", "percentile")
```

## 8.6 AKI (KDIGO)

```{r}
#| label: jx-carbo-linsubhr-pct-akikdigo
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_aki_kdigo", "cmp_status_aki_kdigo",
                  NULL, "AKI KDIGO (Carboplatin)", "percentile")
```

## 8.7 Composite Grade 2 AEs

```{r}
#| label: jx-carbo-linsubhr-pct-grade2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_grade_2_aes", "cmp_status_grade_2_aes",
                  NULL, "Composite Grade 2 AEs (Carboplatin)", "percentile")
```

## 8.8 Composite Grade 3 AEs

```{r}
#| label: jx-carbo-linsubhr-pct-grade3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_grade_3_aes", "cmp_status_grade_3_aes",
                  NULL, "Composite Grade 3 AEs (Carboplatin)", "percentile")
```

## 8.9 Overall Hospitalization

```{r}
#| label: jx-carbo-linsubhr-pct-anyhosp
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_any_hosp", "cmp_status_any_hosp",
                  NULL, "Overall Hospitalization (Carboplatin)", "percentile")
```

## 8.10 Platinum-Related Hospitalization

```{r}
#| label: jx-carbo-linsubhr-pct-sideeffect
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_side_effect", "cmp_status_side_effect",
                  NULL, "Platinum-Related Hospitalization (Carboplatin)", "percentile")
```

## 8.11 90-Day Death

```{r}
#| label: jx-carbo-cox-linear-pct-death
#| fig-width: 6
#| fig-height: 4
plot_cox_linear("time_to_death_90", "death_90",
                NULL, "90-Day Death (Carboplatin)", "percentile")
```

# 9 Model Diagnostics

## 9.1 Events per Variable (EPV)

```{r}
#| label: jx-epv-carbo
outcomes <- c("anemia_2", "anemia_3", "throm_2", "throm_3",
              "aki_2", "aki_kdigo", "grade_2_aes", "grade_3_aes",
              "any_hosp", "side_effect", "death_90")

epv_table <- purrr::map_dfr(outcomes, function(out) {
  status_col <- paste0("cmp_status_", out)
  n_pred <- case_when(
    grepl("anemia", out) ~ 16L,
    grepl("throm", out)  ~ 16L,
    TRUE                 ~ 15L
  )
  tibble(
    outcome      = out,
    N            = sum(!is.na(dat[[status_col]])),
    events       = sum(dat[[status_col]] == 1, na.rm = TRUE),
    deaths       = sum(dat[[status_col]] == 2, na.rm = TRUE),
    n_predictors = n_pred,
    EPV          = round(events / n_pred, 1)
  )
})

epv_table %>%
  knitr::kable(caption = "Events per variable — Carboplatin Cohort")
```

## 9.2 Collinearity — VIF (eGFR Ratio Model)

```{r}
#| label: jx-vif-ratio-carbo
library(car)

vif_dat <- dat %>%
  select(grade_2_aes, egfr_ratio_per10, age, sex, score, ecog_score_cat2, cockcroft,
         cancer_type_cat_7, tumor_stage, high_dose,
         Paclitaxel, Pemetrexed, Gemcitabine,
         bmi, smoking, steroids, thyroid) %>%
  drop_na()

vif_mod <- glm(grade_2_aes ~ egfr_ratio_per10 + age + sex + score + ecog_score_cat2 +
                 cockcroft + cancer_type_cat_7 + tumor_stage + high_dose +
                 Paclitaxel + Pemetrexed + Gemcitabine +
                 bmi + smoking + steroids + thyroid,
               data = vif_dat, family = binomial)

vif_res <- vif(vif_mod)
if (is.matrix(vif_res)) {
  vif_res %>% as.data.frame() %>% rownames_to_column("term") %>%
    arrange(desc(`GVIF^(1/(2*Df))`)) %>% knitr::kable(digits = 2, caption = "VIF — eGFR CR-CYS / CG ratio model (carboplatin)")
} else {
  tibble(term = names(vif_res), VIF = vif_res) %>%
    arrange(desc(VIF)) %>% knitr::kable(digits = 2, caption = "VIF — eGFR CR-CYS / CG ratio model (carboplatin)")
}
```

## 9.3 Correlation Matrix — Continuous Predictors

```{r}
#| label: jx-cormat-carbo
cor_vars <- dat %>%
  select(egfr_ratio, cockcroft, ckd_epi_gfr_cre_cys_unindex, age, bmi, score,
         pre_HGB_45days, pre_PLT_45days) %>%
  drop_na()

cor(cor_vars) %>%
  round(3) %>%
  knitr::kable(caption = "Pearson correlation — continuous predictors (carboplatin)")
```
