---
title: "Jiaxuan Project — Whole Cohort"
author: "Tianqi Ouyang"
date: "2026-04-09"
execute:
  eval: true
  warning: false
  message: false
---

# 1 Setup

```{r}
#| label: setup-jx-whole
library(tidyverse)
library(scales)
library(ggplot2)
library(tidycmprsk)
library(ggsurvfit)
library(gtsummary)

# Load whole-cohort final_master from Jiaxuan data management
dat <- readRDS("jiaxuan_final_master.rds")

# Create eGFR ratio: CKD-EPI Cr-Cys (unindexed) / Cockcroft-Gault
dat <- dat %>%
  mutate(egfr_ratio = ckd_epi_gfr_cre_cys_unindex / cockcroft)
```

# 2 Table 1: Baseline Characteristics (Overall)

```{r}
#| label: jx-table1-whole
dat %>%
  dplyr::select(
    age, age_cat, sex, race, ethnicity, tumor_stage, cancer_type_cat_7,
    platin_group, carbo_AUC, carbo_AUC_cat, cis_dose,
    ici, Bevacizumab, Paclitaxel, Pemetrexed, Doxorubicin, Etoposide,
    Gemcitabine, Pertuzumab, Trastuzumab, Docetaxel, Administered_alone,
    hiv_rpdr, thyroid, smoking, steroids,
    cci, ecog_score, bmi, bmi_cat,
    pre_HGB_45days, pre_PLT_45days, pre_ALB_45days,
    baseline_cys_c, baseline_cre, cr_cys,
    baseline_cre_egfr, baseline_cys_c_egfr,
    ckd_epi_gfr_cre_cys, ckd_epi_gfr_cre_cys_unindex,
    cockcroft, egfr_ratio
  ) %>%
  tbl_summary(
    statistic = list(age ~ "{mean} ({sd})")
  )
```

# 3 Spline subHR Curves by eGFR CR-CYS / CG Ratio

`egfr_ratio = ckd_epi_gfr_cre_cys_unindex / cockcroft`

Each plot shows the subdistribution hazard ratio (subHR, 95% CI) from a Fine-Gray model with a restricted cubic spline (natural spline basis) on the ratio, relative to the median ratio (dotted vertical line). The x-axis is the raw ratio trimmed to the 2.5–97.5 percentiles; the rug at the bottom shows the observed distribution. All models are adjusted for the same covariate set as Section 4.

```{r}
#| label: jx-subhr-fn
library(splines)

# Fit Fine-Gray with an RCS basis on `xvar` and return subHR curve vs reference.
subhr_curve <- function(data, time_var, status_var, xvar,
                        pre_lab = NULL, df_spline = NULL,
                        trim = c(0.025, 0.975), ref_fun = median,
                        title = NULL, xlab = "eGFR CR-CYS / CG ratio") {

  adj <- c("age","sex","bmi","smoking","steroids","thyroid","tumor_stage",
           "ecog_score_cat2","Paclitaxel","Pemetrexed","Gemcitabine",
           "ici","score")
  if (!is.null(pre_lab)) adj <- c(adj, pre_lab)

  d <- data %>%
    dplyr::select(dplyr::all_of(c(time_var, status_var, xvar, adj))) %>%
    tidyr::drop_na()

  # status as numeric 0/1/2 (stored as factor upstream)
  stat_num <- as.numeric(as.character(d[[status_var]]))

  x <- d[[xvar]]
  n_events <- sum(stat_num == 1, na.rm = TRUE)

  # Spline df guided by events-per-variable heuristic
  if (is.null(df_spline)) {
    df_spline <- if (n_events < 100) 3 else if (n_events < 200) 4 else 5
  }

  # Natural-spline basis on the raw ratio
  basis <- splines::ns(x, df = df_spline)

  # Design matrix for adjusters (drop intercept)
  adj_mf <- model.matrix(~ ., data = d[, adj, drop = FALSE])[, -1, drop = FALSE]

  X <- cbind(basis, adj_mf)
  colnames(X) <- make.names(colnames(X), unique = TRUE)

  # Fit Fine-Gray directly with cmprsk::crr
  fit <- cmprsk::crr(
    ftime   = d[[time_var]],
    fstatus = stat_num,
    cov1    = X,
    failcode = 1, cencode = 0
  )

  k <- ncol(basis)
  beta_s <- fit$coef[seq_len(k)]
  V_s    <- fit$var[seq_len(k), seq_len(k), drop = FALSE]

  # Reference value and trimmed grid
  ref  <- ref_fun(x)
  q_lo <- as.numeric(quantile(x, trim[1], na.rm = TRUE))
  q_hi <- as.numeric(quantile(x, trim[2], na.rm = TRUE))
  x_grid <- seq(q_lo, q_hi, length.out = 200)

  basis_ref  <- predict(basis, newx = ref)
  basis_grid <- predict(basis, newx = x_grid)
  L <- sweep(basis_grid, 2, as.numeric(basis_ref), "-")

  log_shr <- as.numeric(L %*% beta_s)
  se      <- sqrt(diag(L %*% V_s %*% t(L)))

  dfp <- tibble::tibble(
    x   = x_grid,
    shr = exp(log_shr),
    lo  = exp(log_shr - 1.96 * se),
    hi  = exp(log_shr + 1.96 * se)
  )

  rug_df <- tibble::tibble(x = x[x >= q_lo & x <= q_hi])

  ggplot(dfp, aes(x, shr)) +
    geom_ribbon(aes(ymin = lo, ymax = hi), fill = "steelblue", alpha = 0.25) +
    geom_line(color = "steelblue", linewidth = 1.3) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "grey40") +
    geom_vline(xintercept = ref, linetype = "dotted", color = "grey40") +
    geom_rug(data = rug_df, aes(x = x), inherit.aes = FALSE,
             sides = "b", alpha = 0.15) +
    labs(title = title, x = xlab, y = "subHR (95% CI)") +
    theme_minimal(base_size = 12) +
    theme(
      axis.title.x = element_text(size = 11),
      axis.title.y = element_text(size = 11),
      plot.title   = element_text(size = 13, face = "bold")
    )
}
```

## 3.1 Anemia Grade 2

```{r}
#| label: jx-subhr-ratio-anemia2
subhr_curve(dat, "cmp_time_anemia_2", "cmp_status_anemia_2", "egfr_ratio",
            pre_lab = "pre_HGB_45days",
            title = "Grade 2 Anemia — subHR vs eGFR CR-CYS / CG ratio")
```

## 3.2 Anemia Grade 3

```{r}
#| label: jx-subhr-ratio-anemia3
subhr_curve(dat, "cmp_time_anemia_3", "cmp_status_anemia_3", "egfr_ratio",
            pre_lab = "pre_HGB_45days",
            title = "Grade 3 Anemia — subHR vs eGFR CR-CYS / CG ratio")
```

## 3.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-subhr-ratio-throm2
subhr_curve(dat, "cmp_time_throm_2", "cmp_status_throm_2", "egfr_ratio",
            pre_lab = "pre_PLT_45days",
            title = "Grade 2 Thrombocytopenia — subHR vs eGFR CR-CYS / CG ratio")
```

## 3.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-subhr-ratio-throm3
subhr_curve(dat, "cmp_time_throm_3", "cmp_status_throm_3", "egfr_ratio",
            pre_lab = "pre_PLT_45days",
            title = "Grade 3 Thrombocytopenia — subHR vs eGFR CR-CYS / CG ratio")
```

## 3.5 AKI Grade 2

```{r}
#| label: jx-subhr-ratio-aki2
subhr_curve(dat, "cmp_time_aki_2", "cmp_status_aki_2", "egfr_ratio",
            pre_lab = "pre_CRE_45days",
            title = "Grade 2 AKI — subHR vs eGFR CR-CYS / CG ratio")
```

## 3.6 AKI Grade 3

```{r}
#| label: jx-subhr-ratio-aki3
subhr_curve(dat, "cmp_time_aki_3", "cmp_status_aki_3", "egfr_ratio",
            pre_lab = "pre_CRE_45days",
            title = "Grade 3 AKI — subHR vs eGFR CR-CYS / CG ratio")
```

# 4 Fine-Gray Models — Three Parallel Predictor Sets

Three parallel Fine-Gray models are fit per outcome, each using a different continuous kidney-function predictor (the ratio, Cockcroft-Gault alone, and CKD-EPI Cr-Cys unindexed alone). The predictors are **not** co-entered in a single model because the ratio is their quotient. All three share the same adjuster set: `age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score`, plus `pre_HGB_45days` (anemia), `pre_PLT_45days` (thrombocytopenia), `pre_CRE_45days` (AKI), or both baseline labs (composite).

```{r}
#| label: jx-fg-helper
fg_tbl <- function(time_var, status_var, pred_var, pre_lab = NULL) {
  adj <- c("age","sex","bmi","smoking","steroids","thyroid","tumor_stage",
           "ecog_score_cat2","Paclitaxel","Pemetrexed","Gemcitabine",
           "ici","score")
  if (!is.null(pre_lab)) adj <- c(adj, pre_lab)
  fmla <- as.formula(paste0(
    "Surv(", time_var, ", ", status_var, ") ~ ",
    paste(c(pred_var, adj), collapse = " + ")
  ))
  tidycmprsk::crr(fmla, failcode = 1, data = dat) %>%
    tbl_regression(exp = TRUE,
                   pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>%
    add_n()
}

fg_three <- function(time_var, status_var, pre_lab = NULL) {
  t1 <- fg_tbl(time_var, status_var, "egfr_ratio",                 pre_lab)
  t2 <- fg_tbl(time_var, status_var, "cockcroft",                  pre_lab)
  t3 <- fg_tbl(time_var, status_var, "ckd_epi_gfr_cre_cys_unindex",pre_lab)
  tbl_merge(
    list(t1, t2, t3),
    tab_spanner = c("**eGFR Ratio (CR-CYS / CG)**",
                    "**Cockcroft-Gault**",
                    "**CKD-EPI Cr-Cys (unindexed)**")
  )
}
```

## 4.1 Anemia Grade 2

```{r}
#| label: jx-fg-anemia2
fg_three("cmp_time_anemia_2", "cmp_status_anemia_2", "pre_HGB_45days")
```

## 4.2 Anemia Grade 3

```{r}
#| label: jx-fg-anemia3
fg_three("cmp_time_anemia_3", "cmp_status_anemia_3", "pre_HGB_45days")
```

## 4.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-fg-throm2
fg_three("cmp_time_throm_2", "cmp_status_throm_2", "pre_PLT_45days")
```

## 4.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-fg-throm3
fg_three("cmp_time_throm_3", "cmp_status_throm_3", "pre_PLT_45days")
```

## 4.5 AKI Grade 2

```{r}
#| label: jx-fg-aki2
fg_three("cmp_time_aki_2", "cmp_status_aki_2", "pre_CRE_45days")
```

## 4.6 AKI Grade 3

```{r}
#| label: jx-fg-aki3
fg_three("cmp_time_aki_3", "cmp_status_aki_3", "pre_CRE_45days")
```

## 4.7 Composite Grade 2 AEs

```{r}
#| label: jx-fg-grade2
fg_tbl_2 <- function(pred_var) {
  tidycmprsk::crr(
    as.formula(paste0("Surv(cmp_time_grade_2_aes, cmp_status_grade_2_aes) ~ ",
                      pred_var,
                      " + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days + pre_PLT_45days")),
    failcode = 1, data = dat
  ) %>% tbl_regression(exp = TRUE,
                       pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>%
    add_n()
}
tbl_merge(
  list(fg_tbl_2("egfr_ratio"),
       fg_tbl_2("cockcroft"),
       fg_tbl_2("ckd_epi_gfr_cre_cys_unindex")),
  tab_spanner = c("**eGFR Ratio (CR-CYS / CG)**",
                  "**Cockcroft-Gault**",
                  "**CKD-EPI Cr-Cys (unindexed)**")
)
```

## 4.8 Composite Grade 3 AEs

```{r}
#| label: jx-fg-grade3
fg_tbl_3 <- function(pred_var) {
  tidycmprsk::crr(
    as.formula(paste0("Surv(cmp_time_grade_3_aes, cmp_status_grade_3_aes) ~ ",
                      pred_var,
                      " + age + sex + bmi + smoking + steroids + thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel + Pemetrexed + Gemcitabine + ici + score + pre_HGB_45days + pre_PLT_45days")),
    failcode = 1, data = dat
  ) %>% tbl_regression(exp = TRUE,
                       pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>%
    add_n()
}
tbl_merge(
  list(fg_tbl_3("egfr_ratio"),
       fg_tbl_3("cockcroft"),
       fg_tbl_3("ckd_epi_gfr_cre_cys_unindex")),
  tab_spanner = c("**eGFR Ratio (CR-CYS / CG)**",
                  "**Cockcroft-Gault**",
                  "**CKD-EPI Cr-Cys (unindexed)**")
)
```

# 5 Model Diagnostics

## 5.1 Events per Variable (EPV)

Models with EPV < 10 are at risk of instability; EPV < 5 should not be reported without penalisation.

```{r}
#| label: jx-epv-whole
outcomes <- c("anemia_2", "anemia_3", "throm_2", "throm_3",
              "aki_2", "aki_3", "grade_2_aes", "grade_3_aes")

epv_table <- purrr::map_dfr(outcomes, function(out) {

  status_col <- paste0("cmp_status_", out)
  n_pred <- case_when(
    grepl("anemia", out)  ~ 15L,
    grepl("throm", out)   ~ 15L,
    grepl("aki", out)     ~ 15L,
    TRUE                  ~ 16L
  )
  tibble(
    outcome      = out,
    N            = sum(!is.na(dat[[status_col]])),
    events       = sum(dat[[status_col]] == 1, na.rm = TRUE),
    deaths       = sum(dat[[status_col]] == 2, na.rm = TRUE),
    n_predictors = n_pred,
    EPV          = round(events / n_pred, 1)
  )
})

epv_table %>%
  knitr::kable(caption = "Events per variable — Whole Cohort")
```

## 5.2 Collinearity — VIF (eGFR Ratio Model)

VIF > 5 = concerning; VIF > 10 = problematic.

```{r}
#| label: jx-vif-ratio-whole
library(car)

vif_dat <- dat %>%
  select(grade_2_aes, egfr_ratio, age, sex, bmi, smoking, steroids, thyroid,
         tumor_stage, ecog_score_cat2, Paclitaxel, Pemetrexed, Gemcitabine,
         ici, score, pre_HGB_45days, pre_PLT_45days) %>%
  drop_na()

vif_mod <- glm(grade_2_aes ~ egfr_ratio + age + sex + bmi + smoking + steroids +
                 thyroid + tumor_stage + ecog_score_cat2 + Paclitaxel +
                 Pemetrexed + Gemcitabine + ici + score +
                 pre_HGB_45days + pre_PLT_45days,
               data = vif_dat, family = binomial)

vif_res <- vif(vif_mod)
if (is.matrix(vif_res)) {
  vif_res %>% as.data.frame() %>% rownames_to_column("term") %>%
    arrange(desc(`GVIF^(1/(2*Df))`)) %>% knitr::kable(digits = 2, caption = "VIF — eGFR CR-CYS / CG ratio model (whole cohort)")
} else {
  tibble(term = names(vif_res), VIF = vif_res) %>%
    arrange(desc(VIF)) %>% knitr::kable(digits = 2, caption = "VIF — eGFR CR-CYS / CG ratio model (whole cohort)")
}
```

## 5.3 Correlation Matrix — Continuous Predictors

```{r}
#| label: jx-cormat-whole
cor_vars <- dat %>%
  select(egfr_ratio, cockcroft, ckd_epi_gfr_cre_cys_unindex, age, bmi, score,
         pre_HGB_45days, pre_PLT_45days) %>%
  drop_na()

cor(cor_vars) %>%
  round(3) %>%
  knitr::kable(caption = "Pearson correlation — continuous predictors")
```
