---
title: "Jiaxuan Project — Whole Cohort"
author: "Tianqi Ouyang"
date: "2026-04-09"
execute:
  eval: true
  warning: false
  message: false
---

# 1 Setup

```{r}
#| label: setup-jx-whole
# Force UTF-8 locale so kable captions and other strings render real Unicode
# (e.g. em-dash) instead of <U+2014> escape sequences.
Sys.setlocale("LC_ALL", "en_US.UTF-8")
library(tidyverse)
library(scales)
library(ggplot2)
library(tidycmprsk)
library(ggsurvfit)
library(gtsummary)

# Load whole-cohort final_master from Jiaxuan data management
dat <- readRDS("jiaxuan_final_master.rds")

# Create eGFR ratio: CKD-EPI Cr-Cys (unindexed) / Cockcroft-Gault
# Also create per-10 mL/min rescaled versions of cockcroft and CKD-EPI for
# reporting (HRs per 1 mL/min are clinically uninterpretable; convention in
# nephro-onc is per 10 mL/min — bio_agent confirmed). Adjusters keep raw scale.
dat <- dat %>%
  mutate(
    egfr_ratio    = ckd_epi_gfr_cre_cys_unindex / cockcroft,
    cockcroft_per10 = cockcroft / 10,
    ckd_epi_per10   = ckd_epi_gfr_cre_cys_unindex / 10
  )
```

# 2 Table 1: Baseline Characteristics (Overall)

```{r}
#| label: jx-table1-whole
dat %>%
  dplyr::select(
    age, age_cat, sex, race, ethnicity, tumor_stage, cancer_type_cat_7,
    platin_group, carbo_AUC, carbo_AUC_cat, cis_dose,
    ici, Bevacizumab, Paclitaxel, Pemetrexed, Doxorubicin, Etoposide,
    Gemcitabine, Pertuzumab, Trastuzumab, Docetaxel, Administered_alone,
    hiv_rpdr, thyroid, smoking, steroids,
    cci, ecog_score, bmi, bmi_cat,
    pre_HGB_45days, pre_PLT_45days, pre_ALB_45days,
    baseline_cys_c, baseline_cre, cr_cys,
    baseline_cre_egfr, baseline_cys_c_egfr,
    ckd_epi_gfr_cre_cys, ckd_epi_gfr_cre_cys_unindex,
    cockcroft, egfr_ratio
  ) %>%
  tbl_summary(
    statistic = list(age ~ "{mean} ({sd})")
  )
```

# 3 Fine-Gray Models — eGFR Ratio (CR-CYS / CG)

`egfr_ratio = ckd_epi_gfr_cre_cys_unindex / cockcroft`, entered as a linear continuous predictor in a Fine-Gray competing-risk model (death is the competing event).

Adjuster set (per project spec): `age, sex, score` (Charlson), `ecog_score_cat2, cockcroft` (CG-CrCl), `cancer_type_cat_7, tumor_stage, platin_group` (cis vs carbo), `high_dose` (platinum dose high vs low), `Paclitaxel, Pemetrexed, Gemcitabine` (platinum partners), `bmi, smoking, steroids, thyroid`. Anemia models additionally adjust for `pre_HGB_45days`; thrombocytopenia for `pre_PLT_45days`; AKI and composite models do not add baseline labs. When the predictor is `cockcroft`, CG-CrCl is dropped from the adjuster list to avoid duplication.

```{r}
#| label: jx-fg-helper
fg_model <- function(time_var, status_var, pred_var, pre_labs = NULL) {
  adj <- c("age","sex","score","ecog_score_cat2","cockcroft",
           "cancer_type_cat_7","tumor_stage","platin_group","high_dose",
           "Paclitaxel","Pemetrexed","Gemcitabine",
           "bmi","smoking","steroids","thyroid")
  # Drop cockcroft from adjusters when it (or its rescaled version) is the predictor
  if (pred_var %in% c("cockcroft","cockcroft_per10")) {
    adj <- setdiff(adj, "cockcroft")
  }
  if (!is.null(pre_labs)) adj <- c(adj, pre_labs)
  fmla <- as.formula(paste0(
    "Surv(", time_var, ", ", status_var, ") ~ ",
    paste(c(pred_var, adj), collapse = " + ")
  ))
  tidycmprsk::crr(fmla, failcode = 1, data = dat) %>%
    tbl_regression(exp = TRUE,
                   pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>%
    add_n()
}
```

## 3.1 Anemia Grade 2

```{r}
#| label: jx-fg-ratio-anemia2
fg_model("cmp_time_anemia_2", "cmp_status_anemia_2", "egfr_ratio", "pre_HGB_45days")
```

## 3.2 Anemia Grade 3

```{r}
#| label: jx-fg-ratio-anemia3
fg_model("cmp_time_anemia_3", "cmp_status_anemia_3", "egfr_ratio", "pre_HGB_45days")
```

## 3.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-fg-ratio-throm2
fg_model("cmp_time_throm_2", "cmp_status_throm_2", "egfr_ratio", "pre_PLT_45days")
```

## 3.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-fg-ratio-throm3
fg_model("cmp_time_throm_3", "cmp_status_throm_3", "egfr_ratio", "pre_PLT_45days")
```

## 3.5 AKI Grade 2

```{r}
#| label: jx-fg-ratio-aki2
fg_model("cmp_time_aki_2", "cmp_status_aki_2", "egfr_ratio")
```

## 3.6 Composite Grade 2 AEs

```{r}
#| label: jx-fg-ratio-grade2
fg_model("cmp_time_grade_2_aes", "cmp_status_grade_2_aes", "egfr_ratio")
```

## 3.7 Composite Grade 3 AEs

```{r}
#| label: jx-fg-ratio-grade3
fg_model("cmp_time_grade_3_aes", "cmp_status_grade_3_aes", "egfr_ratio")
```

# 4 Fine-Gray Models — Cockcroft-Gault eGFR (per 10 mL/min)

Same adjuster set as Section 3, except the continuous predictor is `cockcroft_per10` (= `cockcroft / 10`). The reported HR is **per 10 mL/min higher** Cockcroft-Gault eGFR — i.e., HR < 1 means higher kidney function is associated with fewer events. Per-1-mL/min HRs are clinically uninterpretable; per-10 is the convention in nephro-oncology (bio_agent confirmed). p-values and model fit are identical to a per-1-unit fit.

## 4.1 Anemia Grade 2

```{r}
#| label: jx-fg-cg-anemia2
fg_model("cmp_time_anemia_2", "cmp_status_anemia_2", "cockcroft_per10", "pre_HGB_45days")
```

## 4.2 Anemia Grade 3

```{r}
#| label: jx-fg-cg-anemia3
fg_model("cmp_time_anemia_3", "cmp_status_anemia_3", "cockcroft_per10", "pre_HGB_45days")
```

## 4.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-fg-cg-throm2
fg_model("cmp_time_throm_2", "cmp_status_throm_2", "cockcroft_per10", "pre_PLT_45days")
```

## 4.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-fg-cg-throm3
fg_model("cmp_time_throm_3", "cmp_status_throm_3", "cockcroft_per10", "pre_PLT_45days")
```

## 4.5 AKI Grade 2

```{r}
#| label: jx-fg-cg-aki2
fg_model("cmp_time_aki_2", "cmp_status_aki_2", "cockcroft_per10")
```

## 4.6 Composite Grade 2 AEs

```{r}
#| label: jx-fg-cg-grade2
fg_model("cmp_time_grade_2_aes", "cmp_status_grade_2_aes", "cockcroft_per10")
```

## 4.7 Composite Grade 3 AEs

```{r}
#| label: jx-fg-cg-grade3
fg_model("cmp_time_grade_3_aes", "cmp_status_grade_3_aes", "cockcroft_per10")
```

# 5 Fine-Gray Models — CKD-EPI Cr-Cys (unindexed) eGFR (per 10 mL/min)

Same adjuster set as Section 3, except the continuous predictor is `ckd_epi_per10` (= `ckd_epi_gfr_cre_cys_unindex / 10`). The reported HR is **per 10 mL/min/1.73 m² higher** CKD-EPI Cr-Cys eGFR. p-values and model fit are identical to a per-1-unit fit.

## 5.1 Anemia Grade 2

```{r}
#| label: jx-fg-epi-anemia2
fg_model("cmp_time_anemia_2", "cmp_status_anemia_2", "ckd_epi_per10", "pre_HGB_45days")
```

## 5.2 Anemia Grade 3

```{r}
#| label: jx-fg-epi-anemia3
fg_model("cmp_time_anemia_3", "cmp_status_anemia_3", "ckd_epi_per10", "pre_HGB_45days")
```

## 5.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-fg-epi-throm2
fg_model("cmp_time_throm_2", "cmp_status_throm_2", "ckd_epi_per10", "pre_PLT_45days")
```

## 5.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-fg-epi-throm3
fg_model("cmp_time_throm_3", "cmp_status_throm_3", "ckd_epi_per10", "pre_PLT_45days")
```

## 5.5 AKI Grade 2

```{r}
#| label: jx-fg-epi-aki2
fg_model("cmp_time_aki_2", "cmp_status_aki_2", "ckd_epi_per10")
```

## 5.6 Composite Grade 2 AEs

```{r}
#| label: jx-fg-epi-grade2
fg_model("cmp_time_grade_2_aes", "cmp_status_grade_2_aes", "ckd_epi_per10")
```

## 5.7 Composite Grade 3 AEs

```{r}
#| label: jx-fg-epi-grade3
fg_model("cmp_time_grade_3_aes", "cmp_status_grade_3_aes", "ckd_epi_per10")
```

# 6 subHR Curves — eGFR Ratio

Spline-based subHR curves for each competing outcome, estimated from Fine-Gray competing-risk models fit with a natural cubic spline (3 df) on `egfr_ratio`, adjusting for the same covariate set as Section 3. Curves show the subdistribution hazard ratio (on the original scale) relative to the median observed ratio (dotted vertical line); reference value subHR = 1 (dashed horizontal line). Ribbons are 95% pointwise confidence intervals from the delta method using the spline vcov block. Only the 2nd–98th percentile range of ratio is plotted to limit influence of tails.

```{r}
#| label: jx-subhr-helper
suppressPackageStartupMessages(library(splines))

plot_subhr <- function(time_var, status_var, extra_adj = NULL, outcome_label) {
  base_adj <- c("age","sex","score","ecog_score_cat2","cockcroft",
                "cancer_type_cat_7","tumor_stage","platin_group","high_dose",
                "Paclitaxel","Pemetrexed","Gemcitabine",
                "bmi","smoking","steroids","thyroid")
  keep <- c("egfr_ratio", time_var, status_var, base_adj, extra_adj)
  d <- dat %>% dplyr::select(all_of(keep)) %>% tidyr::drop_na()

  ns_b <- ns(d$egfr_ratio, df = 3)
  knots_in <- attr(ns_b, "knots")
  bdry     <- attr(ns_b, "Boundary.knots")
  colnames(ns_b) <- c("ns1","ns2","ns3")

  adj_df <- d[, c(base_adj, extra_adj), drop = FALSE]
  X_adj <- model.matrix(~ ., data = adj_df)[, -1, drop = FALSE]
  X <- cbind(as.matrix(ns_b), X_adj)

  stat_num <- suppressWarnings(as.integer(as.character(d[[status_var]])))
  time_num <- as.numeric(d[[time_var]])

  fit <- cmprsk::crr(ftime = time_num, fstatus = stat_num,
                     cov1 = X, failcode = 1)

  grid_x <- seq(quantile(d$egfr_ratio, 0.02, na.rm = TRUE),
                quantile(d$egfr_ratio, 0.98, na.rm = TRUE),
                length.out = 100)
  ref_x  <- median(d$egfr_ratio, na.rm = TRUE)

  ns_grid <- predict(ns(d$egfr_ratio, knots = knots_in, Boundary.knots = bdry),
                     grid_x)
  ns_ref  <- predict(ns(d$egfr_ratio, knots = knots_in, Boundary.knots = bdry),
                     ref_x)
  ns_diff <- sweep(as.matrix(ns_grid), 2, as.vector(ns_ref), "-")

  coef_ns <- fit$coef[1:3]
  V_ns    <- fit$var[1:3, 1:3]

  log_hr <- as.vector(ns_diff %*% coef_ns)
  se     <- sqrt(pmax(diag(ns_diff %*% V_ns %*% t(ns_diff)), 0))

  df_plot <- tibble(
    ratio = grid_x,
    subhr = exp(log_hr),
    lcl   = exp(log_hr - 1.96 * se),
    ucl   = exp(log_hr + 1.96 * se)
  )

  ggplot(df_plot, aes(x = ratio, y = subhr)) +
    geom_ribbon(aes(ymin = lcl, ymax = ucl), alpha = 0.2, fill = "steelblue") +
    geom_line(color = "steelblue", linewidth = 1) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "grey50") +
    geom_vline(xintercept = ref_x, linetype = "dotted", color = "grey40") +
    labs(x = "CKD-EPI Cr-Cys / CG ratio",
         y = "subHR (95% CI)",
         title = outcome_label) +
    coord_cartesian(xlim = c(0.5, 1.5), ylim = c(0, 4)) +
    theme_minimal(base_size = 11)
}
```

## 6.1 Anemia Grade 2

```{r}
#| label: jx-subhr-anemia2
#| fig-width: 6
#| fig-height: 4
plot_subhr("cmp_time_anemia_2", "cmp_status_anemia_2",
           "pre_HGB_45days", "Anemia Grade 2")
```

## 6.2 Anemia Grade 3

```{r}
#| label: jx-subhr-anemia3
#| fig-width: 6
#| fig-height: 4
plot_subhr("cmp_time_anemia_3", "cmp_status_anemia_3",
           "pre_HGB_45days", "Anemia Grade 3")
```

## 6.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-subhr-throm2
#| fig-width: 6
#| fig-height: 4
plot_subhr("cmp_time_throm_2", "cmp_status_throm_2",
           "pre_PLT_45days", "Thrombocytopenia Grade 2")
```

## 6.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-subhr-throm3
#| fig-width: 6
#| fig-height: 4
plot_subhr("cmp_time_throm_3", "cmp_status_throm_3",
           "pre_PLT_45days", "Thrombocytopenia Grade 3")
```

## 6.5 AKI Grade 2

```{r}
#| label: jx-subhr-aki2
#| fig-width: 6
#| fig-height: 4
plot_subhr("cmp_time_aki_2", "cmp_status_aki_2",
           NULL, "AKI Grade 2")
```

## 6.6 Composite Grade 2 AEs

```{r}
#| label: jx-subhr-grade2
#| fig-width: 6
#| fig-height: 4
plot_subhr("cmp_time_grade_2_aes", "cmp_status_grade_2_aes",
           NULL, "Composite Grade 2 AEs")
```

## 6.7 Composite Grade 3 AEs

```{r}
#| label: jx-subhr-grade3
#| fig-width: 6
#| fig-height: 4
plot_subhr("cmp_time_grade_3_aes", "cmp_status_grade_3_aes",
           NULL, "Composite Grade 3 AEs")
```

# 7 Linear subHR Curves — eGFR Ratio (raw scale)

Same Fine-Gray models as Section 3 (linear continuous `egfr_ratio`, no spline) and the same adjuster set, but visualised as a curve. The reference is the median observed ratio (dotted vertical line); subHR(x) = exp(beta · (x − reference)). Because the predictor is linear, the curve is exponential on the original scale and a straight line on the log scale. The 95% CI band widens linearly with distance from the reference. Plotted over the 2nd–98th percentile range of ratio.

```{r}
#| label: jx-linsubhr-helper
plot_subhr_linear <- function(time_var, status_var, extra_adj = NULL,
                              outcome_label, x_axis = c("ratio","percentile")) {
  x_axis <- match.arg(x_axis)
  base_adj <- c("age","sex","score","ecog_score_cat2","cockcroft",
                "cancer_type_cat_7","tumor_stage","platin_group","high_dose",
                "Paclitaxel","Pemetrexed","Gemcitabine",
                "bmi","smoking","steroids","thyroid")
  keep <- c("egfr_ratio", time_var, status_var, base_adj, extra_adj)
  d <- dat %>% dplyr::select(all_of(keep)) %>% tidyr::drop_na()

  adj_df <- d[, c(base_adj, extra_adj), drop = FALSE]
  X_adj <- model.matrix(~ ., data = adj_df)[, -1, drop = FALSE]
  X <- cbind(egfr_ratio = d$egfr_ratio, X_adj)

  stat_num <- suppressWarnings(as.integer(as.character(d[[status_var]])))
  time_num <- as.numeric(d[[time_var]])

  fit <- cmprsk::crr(ftime = time_num, fstatus = stat_num,
                     cov1 = X, failcode = 1)

  beta   <- fit$coef[1]
  V_beta <- fit$var[1, 1]

  ref_x  <- median(d$egfr_ratio, na.rm = TRUE)
  grid_x <- seq(quantile(d$egfr_ratio, 0.02, na.rm = TRUE),
                quantile(d$egfr_ratio, 0.98, na.rm = TRUE),
                length.out = 100)

  log_hr <- beta * (grid_x - ref_x)
  se     <- sqrt((grid_x - ref_x)^2 * V_beta)

  if (x_axis == "percentile") {
    ecdf_fn      <- ecdf(d$egfr_ratio)
    grid_display <- ecdf_fn(grid_x) * 100
    ref_display  <- ecdf_fn(ref_x)  * 100
    xlab <- "Percentile of CKD-EPI Cr-Cys / CG ratio"
  } else {
    grid_display <- grid_x
    ref_display  <- ref_x
    xlab <- "CKD-EPI Cr-Cys / CG ratio"
  }

  df_plot <- tibble(
    x     = grid_display,
    subhr = exp(log_hr),
    lcl   = exp(log_hr - 1.96 * se),
    ucl   = exp(log_hr + 1.96 * se)
  )

  ggplot(df_plot, aes(x = x, y = subhr)) +
    geom_ribbon(aes(ymin = lcl, ymax = ucl), alpha = 0.2, fill = "darkorange") +
    geom_line(color = "darkorange", linewidth = 1) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "grey50") +
    geom_vline(xintercept = ref_display, linetype = "dotted", color = "grey40") +
    labs(x = xlab, y = "subHR (95% CI)", title = outcome_label) +
    coord_cartesian(
      xlim = if (x_axis == "ratio") c(0.5, 1.5) else NULL,
      ylim = c(0, 4)
    ) +
    theme_minimal(base_size = 11)
}
```

## 7.1 Anemia Grade 2

```{r}
#| label: jx-linsubhr-anemia2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_anemia_2", "cmp_status_anemia_2",
                  "pre_HGB_45days", "Anemia Grade 2", "ratio")
```

## 7.2 Anemia Grade 3

```{r}
#| label: jx-linsubhr-anemia3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_anemia_3", "cmp_status_anemia_3",
                  "pre_HGB_45days", "Anemia Grade 3", "ratio")
```

## 7.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-linsubhr-throm2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_throm_2", "cmp_status_throm_2",
                  "pre_PLT_45days", "Thrombocytopenia Grade 2", "ratio")
```

## 7.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-linsubhr-throm3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_throm_3", "cmp_status_throm_3",
                  "pre_PLT_45days", "Thrombocytopenia Grade 3", "ratio")
```

## 7.5 AKI Grade 2

```{r}
#| label: jx-linsubhr-aki2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_aki_2", "cmp_status_aki_2",
                  NULL, "AKI Grade 2", "ratio")
```

## 7.6 Composite Grade 2 AEs

```{r}
#| label: jx-linsubhr-grade2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_grade_2_aes", "cmp_status_grade_2_aes",
                  NULL, "Composite Grade 2 AEs", "ratio")
```

## 7.7 Composite Grade 3 AEs

```{r}
#| label: jx-linsubhr-grade3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_grade_3_aes", "cmp_status_grade_3_aes",
                  NULL, "Composite Grade 3 AEs", "ratio")
```

# 8 Linear subHR Curves — eGFR Ratio (percentile x-axis)

Same linear Fine-Gray models as Section 7, but the x-axis is the empirical percentile of `egfr_ratio` (0–100) instead of the raw ratio. This matches the display convention used in the main project's LOESS plots and makes the figures comparable across different ratio distributions. The model itself is unchanged; only the x-axis transformation differs.

## 8.1 Anemia Grade 2

```{r}
#| label: jx-linsubhr-pct-anemia2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_anemia_2", "cmp_status_anemia_2",
                  "pre_HGB_45days", "Anemia Grade 2", "percentile")
```

## 8.2 Anemia Grade 3

```{r}
#| label: jx-linsubhr-pct-anemia3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_anemia_3", "cmp_status_anemia_3",
                  "pre_HGB_45days", "Anemia Grade 3", "percentile")
```

## 8.3 Thrombocytopenia Grade 2

```{r}
#| label: jx-linsubhr-pct-throm2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_throm_2", "cmp_status_throm_2",
                  "pre_PLT_45days", "Thrombocytopenia Grade 2", "percentile")
```

## 8.4 Thrombocytopenia Grade 3

```{r}
#| label: jx-linsubhr-pct-throm3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_throm_3", "cmp_status_throm_3",
                  "pre_PLT_45days", "Thrombocytopenia Grade 3", "percentile")
```

## 8.5 AKI Grade 2

```{r}
#| label: jx-linsubhr-pct-aki2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_aki_2", "cmp_status_aki_2",
                  NULL, "AKI Grade 2", "percentile")
```

## 8.6 Composite Grade 2 AEs

```{r}
#| label: jx-linsubhr-pct-grade2
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_grade_2_aes", "cmp_status_grade_2_aes",
                  NULL, "Composite Grade 2 AEs", "percentile")
```

## 8.7 Composite Grade 3 AEs

```{r}
#| label: jx-linsubhr-pct-grade3
#| fig-width: 6
#| fig-height: 4
plot_subhr_linear("cmp_time_grade_3_aes", "cmp_status_grade_3_aes",
                  NULL, "Composite Grade 3 AEs", "percentile")
```

# 9 Model Diagnostics

## 9.1 Events per Variable (EPV)

Models with EPV < 10 are at risk of instability; EPV < 5 should not be reported without penalisation. Predictor counts: anemia/throm = 17 (16 adjusters + predictor), AKI/composite = 16.

```{r}
#| label: jx-epv-whole
outcomes <- c("anemia_2", "anemia_3", "throm_2", "throm_3",
              "aki_2", "grade_2_aes", "grade_3_aes")

epv_table <- purrr::map_dfr(outcomes, function(out) {
  status_col <- paste0("cmp_status_", out)
  n_pred <- case_when(
    grepl("anemia", out) ~ 17L,
    grepl("throm", out)  ~ 17L,
    TRUE                 ~ 16L
  )
  tibble(
    outcome      = out,
    N            = sum(!is.na(dat[[status_col]])),
    events       = sum(dat[[status_col]] == 1, na.rm = TRUE),
    deaths       = sum(dat[[status_col]] == 2, na.rm = TRUE),
    n_predictors = n_pred,
    EPV          = round(events / n_pred, 1)
  )
})

epv_table %>%
  knitr::kable(caption = "Events per variable — Whole Cohort")
```

## 9.2 Collinearity — VIF (eGFR Ratio Model)

VIF > 5 = concerning; VIF > 10 = problematic. Note that including `cockcroft` alongside `egfr_ratio` (which has cockcroft in the denominator) is expected to inflate VIFs.

```{r}
#| label: jx-vif-ratio-whole
library(car)

vif_dat <- dat %>%
  select(grade_2_aes, egfr_ratio, age, sex, score, ecog_score_cat2, cockcroft,
         cancer_type_cat_7, tumor_stage, platin_group, high_dose,
         Paclitaxel, Pemetrexed, Gemcitabine,
         bmi, smoking, steroids, thyroid) %>%
  drop_na()

vif_mod <- glm(grade_2_aes ~ egfr_ratio + age + sex + score + ecog_score_cat2 +
                 cockcroft + cancer_type_cat_7 + tumor_stage + platin_group +
                 high_dose + Paclitaxel + Pemetrexed + Gemcitabine +
                 bmi + smoking + steroids + thyroid,
               data = vif_dat, family = binomial)

vif_res <- vif(vif_mod)
if (is.matrix(vif_res)) {
  vif_res %>% as.data.frame() %>% rownames_to_column("term") %>%
    arrange(desc(`GVIF^(1/(2*Df))`)) %>% knitr::kable(digits = 2, caption = "VIF — eGFR CR-CYS / CG ratio model (whole cohort)")
} else {
  tibble(term = names(vif_res), VIF = vif_res) %>%
    arrange(desc(VIF)) %>% knitr::kable(digits = 2, caption = "VIF — eGFR CR-CYS / CG ratio model (whole cohort)")
}
```

## 9.3 Correlation Matrix — Continuous Predictors

```{r}
#| label: jx-cormat-whole
cor_vars <- dat %>%
  select(egfr_ratio, cockcroft, ckd_epi_gfr_cre_cys_unindex, age, bmi, score,
         pre_HGB_45days, pre_PLT_45days) %>%
  drop_na()

cor(cor_vars) %>%
  round(3) %>%
  knitr::kable(caption = "Pearson correlation — continuous predictors")
```
