---
title: "Analysis"
author: "Meg"
date: "2026-03-26"
execute:
  eval: true
  warning: false
  message: false
---

# 1 Setup

```{r}
#| label: setup-analysis
library(tidyverse)
library(scales)
library(ggplot2)
library(tidycmprsk)
library(ggsurvfit)
library(gtsummary)

# Load final_master from data management output
final_master <- readRDS("final_master.rds")
```

# 2 Table 1: Baseline Characteristics

## 2.1 By Creatinine/Cystatin C Ratio

```{r}
#| label: table1-baseline
##dose_1: carbo-AUC ≥ 5 mg/mL/min, or cisplatin ≥ 75 mg/m2
table_one_cc_ratio <- final_master %>%
  dplyr::select(age, age_cat, sex, race, ethnicity, tumor_stage, cancer_type_cat_7,
                platin_group, cis_dose, cis_dose_cat, carbo_dose, carbo_AUC_cat, dose_1,
                ici, Bevacizumab, Paclitaxel, Pemetrexed, Doxorubicin, Etoposide, Gemcitabine, Pertuzumab, Trastuzumab, Docetaxel, Fluorouracil, Methotrexate, Vinblastine, Administered_alone,
                hiv_rpdr, thyroid,
                score, ecog_score, bmi, bmi_cat, pre_HGB_45days, pre_PLT_45days, pre_ALB_45days, baseline_cys_c, baseline_cre, cockcroft, baseline_cre_egfr, baseline_cys_c_egfr, ckd_epi_gfr_cre_cys, baseline_cre_egfr_unindexed, baseline_cys_c_egfr_unindexed, ckd_epi_gfr_cre_cys_unindex, ckd_stage_cg, cr_cys, cr_cys_7) %>%
  tbl_summary(statistic = list(age ~ "{mean} ({sd})"),
              by = cr_cys_7) %>%
  add_overall() %>%
  add_p(
    test.args = list(
      all_categorical() ~ list(simulate.p.value = TRUE)
    )
  )
table_one_cc_ratio
```

# 3 Derived Variables for Plots

```{r}
#| label: derived-vars
# Hospitalization binary (from REDCap hosp_status_90d)
# Dose discrepancy percentile: based on carbo_dose_cys / carbo_dose_cg ratio
final_master <- final_master %>%
  mutate(
    hosp_90 = case_when(
      hosp_status_90d == 1 ~ 1,
      hosp_status_90d == 2 ~ 0,
      TRUE ~ NA_real_
    ),
    platinum_related_hosp = ifelse(side_effect == 1, 1, 0),
    dd_percentile = ntile(dose_discrepancy, 100),
    dd_decile     = ntile(dose_discrepancy, 10)
  )
```

## 3.1 Incidence Outcomes by Creatinine/Cystatin C Ratio

```{r}
#| label: table1-incidence
table_one_incidence <- final_master %>%
  select(platinum_related_hosp, hosp_90, grade_3_aes, death_90, cr_cys_7) %>%
  tbl_summary(
    by = cr_cys_7,
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = list(
      all_continuous() ~ 1,
      all_categorical() ~ 1
    )
  ) %>%
  add_overall()
table_one_incidence
```

```{r}
#| label: decile-rates
# Compute event rates by dose discrepancy decile
final_master <- final_master %>%
  group_by(dd_decile) %>%
  mutate(
    anemia_2_rate_decile              = mean(Anemia_g2_90days, na.rm = TRUE),
    anemia_3_rate_decile              = mean(Anemia_g3_90days, na.rm = TRUE),
    throm_2_rate_decile               = mean(Throm_g2_90days, na.rm = TRUE),
    throm_3_rate_decile               = mean(Throm_g3_90days, na.rm = TRUE),
    aki_2_rate_decile                 = mean(AKI_g2_90days, na.rm = TRUE),
    aki_3_rate_decile                 = mean(AKI_g3_90days, na.rm = TRUE),
    hos_rate_decile                   = mean(hosp_90, na.rm = TRUE),
    platinum_related_hos_rate_decile  = mean(platinum_related_hosp, na.rm = TRUE),
    death_rate_decile                 = mean(death_90, na.rm = TRUE)
  ) %>%
  ungroup() %>%
  mutate(dd_decile = as.numeric(dd_decile))
```

```{r}
#| label: decile-summary
# Summarize dose discrepancy by decile
summary_by_decile <- final_master %>%
  group_by(dd_decile) %>%
  summarise(
    n      = n(),
    min    = min(dose_discrepancy, na.rm = TRUE),
    q1     = quantile(dose_discrepancy, 0.25, na.rm = TRUE),
    median = median(dose_discrepancy, na.rm = TRUE),
    mean   = mean(dose_discrepancy, na.rm = TRUE),
    q3     = quantile(dose_discrepancy, 0.75, na.rm = TRUE),
    max    = max(dose_discrepancy, na.rm = TRUE),
    sd     = sd(dose_discrepancy, na.rm = TRUE)
  )
```

# 4 LOESS Plot Function

```{r}
#| label: fn-loess-plot
loess_plot <- function(data, x, y, x_point, y_point, title, xlab, ylab) {
  ggplot(data, aes(x = {{x}}, y = {{y}})) +
    geom_point(aes(x = {{x_point}}, y = {{y_point}}),
               size = 6, color = "black", shape = 19) +
    geom_smooth(method = "loess", se = TRUE, span = 0.75, color = "blue", linewidth = 2) +
    scale_x_continuous(breaks = seq(0, 100, by = 10)) +
    scale_y_continuous(labels = percent_format(accuracy = 1)) +
    labs(title = title, x = xlab, y = ylab) +
    theme_minimal() +
    theme(
      axis.title.x  = element_text(size = 20),
      axis.title.y  = element_text(size = 20),
      axis.text.x   = element_text(size = 16),
      axis.text.y   = element_text(size = 16),
      plot.title     = element_text(size = 24, face = "bold")
    ) +
    annotate("rect", xmin = 1, xmax = 25, ymin = -Inf, ymax = Inf,
             alpha = 0.2, fill = "yellow")
}
```

# 5 LOESS Plots by Dose Discrepancy Percentile

## 5.1 Grade 2 Anemia

```{r}
#| label: plot-anemia-2
loess_plot(
  data = final_master, x = dd_percentile, y = Anemia_g2_90days,
  x_point = dd_decile * 10, y_point = anemia_2_rate_decile,
  title = "Grade >= 2 Anemia",
  xlab = "Percentile of Dose Discrepancy (CKD-EPI/CG)", ylab = "Grade >= 2 Anemia"
)
```

## 5.2 Grade 3 Thrombocytopenia

```{r}
#| label: plot-throm-3
loess_plot(
  data = final_master, x = dd_percentile, y = Throm_g3_90days,
  x_point = dd_decile * 10, y_point = throm_3_rate_decile,
  title = "Grade >= 3 Thrombocytopenia",
  xlab = "Percentile of Dose Discrepancy (CKD-EPI/CG)", ylab = "Grade >= 3 Thrombocytopenia"
)
```

## 5.3 Grade 3 AKI (Creatinine Increased)

```{r}
#| label: plot-aki-3
loess_plot(
  data = final_master, x = dd_percentile, y = AKI_g3_90days,
  x_point = dd_decile * 10, y_point = aki_3_rate_decile,
  title = "Grade >= 3 Creatinine Increased",
  xlab = "Percentile of Dose Discrepancy (CKD-EPI/CG)", ylab = "Grade >= 3 Creatinine Increased"
)
```

## 5.4 Overall Hospitalization

```{r}
#| label: plot-hosp
loess_plot(
  data = final_master, x = dd_percentile, y = hosp_90,
  x_point = dd_decile * 10, y_point = hos_rate_decile,
  title = "Overall Hospitalization",
  xlab = "Percentile of Dose Discrepancy (CKD-EPI/CG)", ylab = "Overall Hospitalization"
)
```

## 5.5 Platinum-Related Hospitalization

```{r}
#| label: plot-platinum-hosp
loess_plot(
  data = final_master, x = dd_percentile, y = platinum_related_hosp,
  x_point = dd_decile * 10, y_point = platinum_related_hos_rate_decile,
  title = "Hospitalization for Platinum-Associated AEs",
  xlab = "Percentile of Dose Discrepancy (CKD-EPI/CG)", ylab = "Hospitalization for Platinum-Associated AEs"
)
```

# 6 Dose Discrepancy Plots

## 6.1 CKD-EPI vs Cockcroft-Gault Scatter

```{r}
#| label: plot-scatter-gfr
ggplot(final_master, aes(x = cockcroft, y = ckd_epi_gfr_cre_cys_unindex)) +
  geom_point(alpha = 0.6, color = "black") +
  geom_abline(intercept = 0, slope = 1, linetype = "solid", color = "grey50") +
  scale_x_continuous(limits = c(0, 225), expand = c(0, 0)) +
  scale_y_continuous(limits = c(0, 225), expand = c(0, 0)) +
  labs(x = "Cockcroft-Gault (mL/min)",
       y = "CKD-EPI Cr-Cys Unindexed (mL/min)",
       title = "Cockcroft-Gault vs CKD-EPI Cr-Cys") +
  theme_bw() +
  theme(panel.grid.minor = element_blank())
```

## 6.2 GFR Distribution: CG vs CKD-EPI

```{r}
#| label: plot-gfr-hist
plot_data_long <- final_master %>%
  select(record_id, cockcroft, ckd_epi_gfr_cre_cys_unindex) %>%
  pivot_longer(
    cols = c(cockcroft, ckd_epi_gfr_cre_cys_unindex),
    names_to = "measure_type", values_to = "gfr_value"
  ) %>%
  filter(!is.na(gfr_value)) %>%
  mutate(measure_type = case_match(measure_type,
    "cockcroft"                    ~ "Cockcroft-Gault",
    "ckd_epi_gfr_cre_cys_unindex" ~ "CKD-EPI (Cr-Cys) Unindexed"
  ))

ggplot(plot_data_long, aes(x = gfr_value, fill = measure_type)) +
  geom_histogram(color = "black", alpha = 0.7, bins = 30, position = "identity") +
  facet_wrap(~ measure_type) +
  geom_vline(
    data = plot_data_long %>% group_by(measure_type) %>%
      summarise(grp_mean = mean(gfr_value, na.rm = TRUE)),
    aes(xintercept = grp_mean), color = "red", linetype = "dashed", linewidth = 0.8
  ) +
  scale_fill_manual(values = c("#1F78B4", "#33A02C")) +
  labs(title = "Renal Function Distribution",
       subtitle = "Comparing Absolute GFR (mL/min)",
       x = "GFR (mL/min)", y = "Number of Patients") +
  theme_minimal(base_size = 14) +
  theme(legend.position = "none")
```

## 6.3 Carboplatin Dose Discrepancy Distribution

```{r}
#| label: plot-dose-diff
ggplot(final_master, aes(x = dose_diff_pct)) +
  geom_histogram(color = "black", fill = "#1F78B4", alpha = 0.7, bins = 40) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "red", linewidth = 0.8) +
  labs(title = "Carboplatin Dose Difference: CKD-EPI Cr-Cys vs Cockcroft-Gault",
       x = "Dose Difference (%)", y = "Number of Patients",
       subtitle = "Positive = CKD-EPI recommends higher dose") +
  theme_minimal(base_size = 14)
```

## 6.4 Scatter by Sex

```{r}
#| label: plot-scatter-sex
ggplot(final_master, aes(x = cockcroft, y = ckd_epi_gfr_cre_cys_unindex, color = sex)) +
  geom_point(alpha = 0.6) +
  geom_abline(intercept = 0, slope = 1, linetype = "solid", color = "grey50") +
  scale_x_continuous(limits = c(0, 225), expand = c(0, 0)) +
  scale_y_continuous(limits = c(0, 225), expand = c(0, 0)) +
  scale_color_manual(values = c("Male" = "black", "Female" = "red"),
                     name = "Sex") +
  labs(x = "Cockcroft-Gault (mL/min)",
       y = "CKD-EPI Cr-Cys Unindexed (mL/min)",
       title = "CG vs CKD-EPI by Sex") +
  theme_bw() + theme(panel.grid.minor = element_blank())
```

## 6.5 Scatter by BMI

```{r}
#| label: plot-scatter-bmi
ggplot(final_master, aes(x = cockcroft, y = ckd_epi_gfr_cre_cys_unindex, color = bmi_30)) +
  geom_point(alpha = 0.6) +
  geom_abline(intercept = 0, slope = 1, linetype = "solid", color = "grey50") +
  scale_x_continuous(limits = c(0, 225), expand = c(0, 0)) +
  scale_y_continuous(limits = c(0, 225), expand = c(0, 0)) +
  scale_color_manual(values = c("<30" = "black", ">=30" = "red"), name = "BMI") +
  labs(x = "Cockcroft-Gault (mL/min)",
       y = "CKD-EPI Cr-Cys Unindexed (mL/min)",
       title = "CG vs CKD-EPI by BMI") +
  theme_bw() + theme(panel.grid.minor = element_blank())
```

## 6.6 Scatter by Age

```{r}
#| label: plot-scatter-age
ggplot(final_master, aes(x = cockcroft, y = ckd_epi_gfr_cre_cys_unindex, color = age_70)) +
  geom_point(alpha = 0.6) +
  geom_abline(intercept = 0, slope = 1, linetype = "solid", color = "grey50") +
  scale_x_continuous(limits = c(0, 225), expand = c(0, 0)) +
  scale_y_continuous(limits = c(0, 225), expand = c(0, 0)) +
  scale_color_manual(values = c("<70" = "black", ">=70" = "red"), name = "Age") +
  labs(x = "Cockcroft-Gault (mL/min)",
       y = "CKD-EPI Cr-Cys Unindexed (mL/min)",
       title = "CG vs CKD-EPI by Age") +
  theme_bw() + theme(panel.grid.minor = element_blank())
```

# 7 Cumulative Incidence Plots

## 7.1 Platinum-Related Hospitalization (Side Effect)

```{r}
#| label: cuminc-side-effect
fit_side_effect <- cuminc(
  Surv(cmp_time_side_effect, cmp_status_side_effect) ~ cr_cys_7,
  data = final_master
)

ggcuminc(fit_side_effect) +
  labs(
    title = "Platinum-Related Hospitalization",
    x = "Follow-up Time (Days)",
    y = "Cumulative Incidence"
  ) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  theme_classic(base_size = 14) +
  theme(
    plot.title    = element_text(face = "bold", size = 16),
    axis.title    = element_text(size = 14),
    axis.text     = element_text(size = 12),
    legend.title  = element_blank(),
    legend.text   = element_text(size = 12)
  ) +
  scale_color_manual(values = c("red", "blue"))
```
