---
title: "Analysis"
author: "Meg"
date: "2026-03-26"
execute:
  eval: true
  warning: false
  message: false
---

# 1 Setup

```{r}
#| label: setup-analysis
library(tidyverse)
library(scales)
library(ggplot2)
library(tidycmprsk)
library(ggsurvfit)
library(gtsummary)

# Load final_master from data management output
final_master <- readRDS("final_master.rds")
```

# 2 Derived Variables

```{r}
#| label: derived-vars
final_master <- final_master %>%
  mutate(
    hosp_90 = case_when(
      hosp_status_90d == 1 ~ 1,
      hosp_status_90d == 2 ~ 0,
      TRUE ~ NA_real_
    ),
    platinum_related_hosp = ifelse(side_effect == 1, 1, 0),
    dd_percentile = ntile(dose_discrepancy, 100),
    dd_decile     = ntile(dose_discrepancy, 10)
  )
```

# 3 Table 1: Baseline Characteristics

```{r}
#| label: table1-baseline
table_one <- final_master %>%
  dplyr::select(
    age, age_cat, sex, race, ethnicity, tumor_stage, cancer_type_cat_7,
    carbo_dose, carbo_AUC_cat, dose_1,
    ici, Bevacizumab, Paclitaxel, Pemetrexed, Doxorubicin, Etoposide,
    Gemcitabine, Pertuzumab, Trastuzumab, Docetaxel, Administered_alone,
    hiv_rpdr, thyroid,
    cci, ecog_score, bmi, bmi_cat,
    pre_HGB_45days, pre_PLT_45days, pre_ALB_45days,
    baseline_cys_c, baseline_cre,
    baseline_cre_egfr, baseline_cys_c_egfr,
    ckd_epi_gfr_cre_cys, ckd_epi_gfr_cre_cys_unindex,
    carbo_dose_redcap, carbo_dose_cre_cys, dose_discrepancy, dose_diff_pct
  ) %>%
  tbl_summary(
    statistic = list(age ~ "{mean} ({sd})")
  )
table_one
```

## 3.1 Incidence Outcomes

```{r}
#| label: table1-incidence
table_one_incidence <- final_master %>%
  select(platinum_related_hosp, hosp_90, grade_3_aes, death_90) %>%
  tbl_summary(
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = list(
      all_continuous() ~ 1,
      all_categorical() ~ 1
    )
  )
table_one_incidence
```

# 4 Dose Distribution

## 4.1 Actual vs Predicted Dose (Overlaid)

```{r}
#| label: plot-dose-overlay
dose_long <- final_master %>%
  select(record_id, carbo_dose_redcap, carbo_dose_cre_cys) %>%
  pivot_longer(
    cols = c(carbo_dose_redcap, carbo_dose_cre_cys),
    names_to = "dose_type", values_to = "dose_mg"
  ) %>%
  filter(!is.na(dose_mg)) %>%
  mutate(dose_type = case_match(dose_type,
    "carbo_dose_redcap"  ~ "Actual (REDCap)",
    "carbo_dose_cre_cys" ~ "Predicted (CKD-EPI Cr-Cys)"
  ))

ggplot(dose_long, aes(x = dose_mg, fill = dose_type)) +
  geom_histogram(alpha = 0.5, bins = 40, position = "identity", color = "black") +
  scale_fill_manual(values = c("Actual (REDCap)" = "#E31A1C",
                                "Predicted (CKD-EPI Cr-Cys)" = "#1F78B4")) +
  labs(title = "Carboplatin Dose Distribution",
       x = "Dose (mg)", y = "Number of Patients", fill = "Dose Type") +
  theme_minimal(base_size = 14)
```

## 4.2 Actual vs Predicted Dose (Side by Side)

```{r}
#| label: plot-dose-facet
ggplot(dose_long, aes(x = dose_mg, fill = dose_type)) +
  geom_histogram(color = "black", alpha = 0.7, bins = 40) +
  facet_wrap(~ dose_type) +
  geom_vline(
    data = dose_long %>% group_by(dose_type) %>%
      summarise(grp_mean = mean(dose_mg, na.rm = TRUE)),
    aes(xintercept = grp_mean), color = "red", linetype = "dashed", linewidth = 0.8
  ) +
  scale_fill_manual(values = c("Actual (REDCap)" = "#E31A1C",
                                "Predicted (CKD-EPI Cr-Cys)" = "#1F78B4")) +
  labs(title = "Carboplatin Dose Distribution",
       x = "Dose (mg)", y = "Number of Patients") +
  theme_minimal(base_size = 14) +
  theme(legend.position = "none")
```

```{r}
#| label: decile-rates
final_master <- final_master %>%
  group_by(dd_decile) %>%
  mutate(
    anemia_2_rate_decile              = mean(Anemia_g2_90days, na.rm = TRUE),
    anemia_3_rate_decile              = mean(Anemia_g3_90days, na.rm = TRUE),
    throm_2_rate_decile               = mean(Throm_g2_90days, na.rm = TRUE),
    throm_3_rate_decile               = mean(Throm_g3_90days, na.rm = TRUE),
    aki_2_rate_decile                 = mean(AKI_g2_90days, na.rm = TRUE),
    aki_3_rate_decile                 = mean(AKI_g3_90days, na.rm = TRUE),
    hos_rate_decile                   = mean(hosp_90, na.rm = TRUE),
    platinum_related_hos_rate_decile  = mean(platinum_related_hosp, na.rm = TRUE),
    death_rate_decile                 = mean(death_90, na.rm = TRUE)
  ) %>%
  ungroup() %>%
  mutate(dd_decile = as.numeric(dd_decile))
```

# 5 LOESS Plots: AE Rates by Dose Discrepancy Percentile

```{r}
#| label: fn-loess-plot
loess_plot <- function(data, x, y, x_point, y_point, title, xlab, ylab) {
  ggplot(data, aes(x = {{x}}, y = {{y}})) +
    geom_point(aes(x = {{x_point}}, y = {{y_point}}),
               size = 4, color = "black", shape = 19) +
    geom_smooth(method = "loess", se = TRUE, span = 0.75, color = "blue", linewidth = 1.5) +
    scale_y_continuous(labels = percent_format(accuracy = 1)) +
    labs(title = title, x = xlab, y = ylab) +
    theme_minimal(base_size = 12) +
    theme(
      axis.title.x  = element_text(size = 11),
      axis.title.y  = element_text(size = 11),
      axis.text.x   = element_text(size = 10),
      axis.text.y   = element_text(size = 10),
      plot.title     = element_text(size = 13, face = "bold")
    )
}

loess_plot_raw <- function(data, x, y, title, xlab, ylab) {
  ggplot(data, aes(x = {{x}}, y = {{y}})) +
    geom_smooth(method = "loess", se = TRUE, span = 0.75, color = "blue", linewidth = 1.5) +
    scale_y_continuous(labels = percent_format(accuracy = 1)) +
    labs(title = title, x = xlab, y = ylab) +
    theme_minimal(base_size = 12) +
    theme(
      axis.title.x  = element_text(size = 11),
      axis.title.y  = element_text(size = 11),
      axis.text.x   = element_text(size = 10),
      axis.text.y   = element_text(size = 10),
      plot.title     = element_text(size = 13, face = "bold")
    )
}
```

## 5.1 Grade 2 Anemia

```{r}
#| label: plot-anemia-2
loess_plot(
  data = final_master, x = dd_percentile, y = Anemia_g2_90days,
  x_point = dd_decile * 10, y_point = anemia_2_rate_decile,
  title = "Grade >= 2 Anemia",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "Grade >= 2 Anemia"
)
```

## 5.2 Grade 3 Thrombocytopenia

```{r}
#| label: plot-throm-3
loess_plot(
  data = final_master, x = dd_percentile, y = Throm_g3_90days,
  x_point = dd_decile * 10, y_point = throm_3_rate_decile,
  title = "Grade >= 3 Thrombocytopenia",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "Grade >= 3 Thrombocytopenia"
)
```

## 5.3 Grade 3 AKI

```{r}
#| label: plot-aki-3
loess_plot(
  data = final_master, x = dd_percentile, y = AKI_g3_90days,
  x_point = dd_decile * 10, y_point = aki_3_rate_decile,
  title = "Grade >= 3 Creatinine Increased",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "Grade >= 3 Creatinine Increased"
)
```

## 5.4 Overall Hospitalization

```{r}
#| label: plot-hosp
loess_plot(
  data = final_master, x = dd_percentile, y = hosp_90,
  x_point = dd_decile * 10, y_point = hos_rate_decile,
  title = "Overall Hospitalization",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "Overall Hospitalization"
)
```

## 5.5 Platinum-Related Hospitalization

```{r}
#| label: plot-platinum-hosp
loess_plot(
  data = final_master, x = dd_percentile, y = platinum_related_hosp,
  x_point = dd_decile * 10, y_point = platinum_related_hos_rate_decile,
  title = "Hospitalization for Platinum-Associated AEs",
  xlab = "Percentile of Dose Discrepancy (REDCap - CKD-EPI Cr-Cys)",
  ylab = "Hospitalization for Platinum-Associated AEs"
)
```

# 6 LOESS Plots: AE Rates by Actual Dose Discrepancy (mg)

## 6.1 Grade 2 Anemia

```{r}
#| label: plot-anemia-2-raw
loess_plot_raw(
  data = final_master, x = dose_discrepancy, y = Anemia_g2_90days,
  title = "Grade >= 2 Anemia",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "Grade >= 2 Anemia"
)
```

## 6.2 Grade 3 Thrombocytopenia

```{r}
#| label: plot-throm-3-raw
loess_plot_raw(
  data = final_master, x = dose_discrepancy, y = Throm_g3_90days,
  title = "Grade >= 3 Thrombocytopenia",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "Grade >= 3 Thrombocytopenia"
)
```

## 6.3 Grade 3 AKI

```{r}
#| label: plot-aki-3-raw
loess_plot_raw(
  data = final_master, x = dose_discrepancy, y = AKI_g3_90days,
  title = "Grade >= 3 Creatinine Increased",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "Grade >= 3 Creatinine Increased"
)
```

## 6.4 Overall Hospitalization

```{r}
#| label: plot-hosp-raw
loess_plot_raw(
  data = final_master, x = dose_discrepancy, y = hosp_90,
  title = "Overall Hospitalization",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "Overall Hospitalization"
)
```

## 6.5 Platinum-Related Hospitalization

```{r}
#| label: plot-platinum-hosp-raw
loess_plot_raw(
  data = final_master, x = dose_discrepancy, y = platinum_related_hosp,
  title = "Hospitalization for Platinum-Associated AEs",
  xlab = "Dose Discrepancy (mg): Actual - Predicted",
  ylab = "Hospitalization for Platinum-Associated AEs"
)
```

# 7 Dose Discrepancy Plots

## 7.1 Actual (REDCap) vs Predicted (CKD-EPI Cr-Cys) Dose Scatter

```{r}
#| label: plot-scatter-dose
ggplot(final_master, aes(x = carbo_dose_cre_cys, y = carbo_dose_redcap)) +
  geom_point(alpha = 0.6, color = "black") +
  geom_abline(intercept = 0, slope = 1, linetype = "solid", color = "red") +
  labs(x = "Predicted Dose — CKD-EPI Cr-Cys (mg)",
       y = "Actual Dose — REDCap (mg)",
       title = "Actual vs Predicted Carboplatin Dose") +
  theme_bw() + theme(panel.grid.minor = element_blank())
```

## 7.2 Dose Discrepancy Distribution

```{r}
#| label: plot-dose-diff
ggplot(final_master, aes(x = dose_discrepancy)) +
  geom_histogram(color = "black", fill = "#1F78B4", alpha = 0.7, bins = 40) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "red", linewidth = 0.8) +
  labs(title = "Dose Discrepancy: Actual (REDCap) - Predicted (CKD-EPI Cr-Cys)",
       x = "Dose Discrepancy (mg)",
       y = "Number of Patients",
       subtitle = "Positive = patient received more than Cr-Cys predicts") +
  theme_minimal(base_size = 14)
```

## 7.3 Scatter by Sex

```{r}
#| label: plot-scatter-sex
ggplot(final_master, aes(x = carbo_dose_cre_cys, y = carbo_dose_redcap, color = sex)) +
  geom_point(alpha = 0.6) +
  geom_abline(intercept = 0, slope = 1, linetype = "solid", color = "grey50") +
  scale_color_manual(values = c("Male" = "black", "Female" = "red"), name = "Sex") +
  labs(x = "Predicted Dose — CKD-EPI Cr-Cys (mg)",
       y = "Actual Dose — REDCap (mg)",
       title = "Actual vs Predicted Dose by Sex") +
  theme_bw() + theme(panel.grid.minor = element_blank())
```

## 7.4 Scatter by BMI

```{r}
#| label: plot-scatter-bmi
ggplot(final_master, aes(x = carbo_dose_cre_cys, y = carbo_dose_redcap, color = bmi_30)) +
  geom_point(alpha = 0.6) +
  geom_abline(intercept = 0, slope = 1, linetype = "solid", color = "grey50") +
  scale_color_manual(values = c("<30" = "black", ">=30" = "red"), name = "BMI") +
  labs(x = "Predicted Dose — CKD-EPI Cr-Cys (mg)",
       y = "Actual Dose — REDCap (mg)",
       title = "Actual vs Predicted Dose by BMI") +
  theme_bw() + theme(panel.grid.minor = element_blank())
```

## 7.5 Scatter by Age

```{r}
#| label: plot-scatter-age
ggplot(final_master, aes(x = carbo_dose_cre_cys, y = carbo_dose_redcap, color = age_70)) +
  geom_point(alpha = 0.6) +
  geom_abline(intercept = 0, slope = 1, linetype = "solid", color = "grey50") +
  scale_color_manual(values = c("<70" = "black", ">=70" = "red"), name = "Age") +
  labs(x = "Predicted Dose — CKD-EPI Cr-Cys (mg)",
       y = "Actual Dose — REDCap (mg)",
       title = "Actual vs Predicted Dose by Age") +
  theme_bw() + theme(panel.grid.minor = element_blank())
```

# 8 Cumulative Incidence Plots

## 8.1 Platinum-Related Hospitalization (Side Effect)

```{r}
#| label: cuminc-side-effect
fit_side_effect <- cuminc(
  Surv(cmp_time_side_effect, cmp_status_side_effect) ~ cr_cys_7,
  data = final_master
)

ggcuminc(fit_side_effect) +
  labs(
    title = "Platinum-Related Hospitalization",
    x = "Follow-up Time (Days)",
    y = "Cumulative Incidence"
  ) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  theme_classic(base_size = 14) +
  theme(
    plot.title    = element_text(face = "bold", size = 16),
    axis.title    = element_text(size = 14),
    axis.text     = element_text(size = 12),
    legend.title  = element_blank(),
    legend.text   = element_text(size = 12)
  ) +
  scale_color_manual(values = c("red", "blue"))
```
