---
title: "copy 709"
output: html_document
date: "2025-07-24"
---

# Read Redcap 
```{r,include=FALSE}
library(tidyverse)
library(tableone)
library(writexl)
library(gtsummary)
library(survival)
library(ggplot2)
library(readxl)
library(ggpubr)
library(splines)
library(xlsx)
library(lattice)
library(mice)
library(DescTools)
library(survminer)
library(cmprsk)
library(tidycmprsk)



master <- read_csv("/Users/to909/Downloads/CystatinCInPatientsO_DATA_2025-07-24_1327.csv")

```

# Create hosp variables
```{r,include=FALSE}



standardize_colnames <- function(df) {
  # Replace non-alphanumeric characters with underscore
  names(df) <- gsub("[^[:alnum:]_]", "_", names(df))
  
  # Reduce multiple underscores to a single underscore
  names(df) <- gsub("_+", "_", names(df))
  
  # Remove underscore if it's at the end of the name
  names(df) <- gsub("_$", "", names(df))
  
  # Return the cleaned dataframe
  return(df)
}

master <- standardize_colnames(master)




master <- master %>%
   rename(ed_visit_diff=er_visit_diff,
         ed_visit_date=er_visit_date,
         ed_status_90d=er_status_90d,
         other_ed=other_ed_visit) %>% 
  rename_with(~ gsub("^hosp_visit_", "hosp_visit_0_", .x), starts_with("hosp_visit_")) %>%
  rename_with(~ gsub("^other_hosp_", "hosp_visit_", .x), starts_with("other_hosp_")) %>% 
  rename_with(~ gsub("_visit", "", .x) %>% 
                gsub("_(\\d+)_", "_\\1_reason_", .), starts_with("other_ed_visit_")) %>% 
  rename_with(~ gsub("^ed_visit_", "ed_visit_0_", .x), starts_with("ed_visit_")) %>% 
  rename_with(~ gsub("^other_ed_", "ed_visit_", .x), starts_with("other_ed_")) %>% 
  mutate(other_hosp=ifelse(other_hosp!=1 |is.na(other_hosp),0,1),
         other_ed=ifelse(other_ed!=1 |is.na(other_ed),0,1),
    
    
        extra_hosp_n = ifelse(other_hosp == 1,
                          rowSums(across(hosp_extra_1:hosp_extra_5), na.rm = TRUE),
                          0),
         extra_ed_n = ifelse(other_ed == 1,
                    rowSums(across(ed_extra_1:ed_extra_3)),
                    0)

         )



check_vars_hosp <- grep("^hosp_visit_\\d+_reason_|^hosp_visit_\\d+_diff", names(master), value = TRUE)
check_vars_side_effect <- grep("^hosp_visit_\\d+_reason_[1-7]|^hosp_visit_\\d+_diff", names(master), value = TRUE)
# check_vars_ed <- grep("^ed_visit_\\d+_reason_[1-7]|^ed_visit_\\d+_diff", names(master1), value = TRUE)

master <- master %>% 
  mutate(other_hosp=ifelse(other_hosp!=1 |is.na(other_hosp),0,1),
    
    
    
        extra_hosp_n = ifelse(other_hosp == 1,
                          rowSums(across(hosp_extra_1:hosp_extra_5), na.rm = TRUE),
                          0)
         )

```


# create hosp reason 1-11 hosp
```{r,include=FALSE}

create_events_and_times_1_11 <- function(data) {
    # Initialize hospital event and time variables
    for (i in 1:11) {
        data[[paste0("event_hosp_", i)]] <- 0
        data[[paste0("time_to_event_hosp_", i)]] <- NA
    }

    # Process each row
    for (i in seq_len(nrow(data))) {
        # If baseline hospital visit is missing, set all to 0/NA
        if (is.na(data[i, "hosp_visit_0_diff"])) {
            for (j in 1:11) {
                data[i, paste0("event_hosp_", j)] <- 0
                data[i, paste0("time_to_event_hosp_", j)] <- NA
            }
        } else {
            # Baseline hospital visit
            for (j in 1:11) {
                if (!is.na(data[i, paste0("hosp_visit_0_reason_", j)]) &&
                    data[i, paste0("hosp_visit_0_reason_", j)] == 1) {
                    data[i, paste0("event_hosp_", j)] <- 1
                    data[i, paste0("time_to_event_hosp_", j)] <- data[i, "hosp_visit_0_diff"]
                }
            }
        }

        # Additional hospital visits
        if (!is.na(data[i, "other_hosp"]) && data[i, "other_hosp"] == 1) {
            extra_hosp_n <- as.numeric(data[i, "extra_hosp_n"])
            if (!is.na(extra_hosp_n) && extra_hosp_n > 0) {
                for (visit in 1:extra_hosp_n) {
                    for (j in 1:11) {
                        if (!is.na(data[i, paste0("event_hosp_", j)]) &&
                            data[i, paste0("event_hosp_", j)] == 0 &&
                            !is.na(data[i, paste0("hosp_visit_", visit, "_reason_", j)]) &&
                            data[i, paste0("hosp_visit_", visit, "_reason_", j)] == 1) {
                            data[i, paste0("event_hosp_", j)] <- 1
                            data[i, paste0("time_to_event_hosp_", j)] <- data[i, paste0("hosp_visit_", visit, "_diff")]
                        }
                    }
                }
            }
        }
    }

    return(data)
}



master <- create_events_and_times_1_11(master)
check_vars_event <- grep("^event_hosp_|^time_to_event_hosp_", names(master), value = TRUE)

```




# Combine event 1 -7 side effect 
```{r,include=FALSE}



side_effect <- master %>%
  select(record_id, matches("^event_hosp_[1-7]$|^time_to_event_hosp_[1-7]$")) %>%
  rowwise() %>%
  mutate(
    side_effect = if_else(any(c_across(starts_with("event_hosp_")) == 1, na.rm = TRUE), 1, 0),
    time_to_side_effect = {
      if (side_effect == 1) {
        times <- c_across(starts_with("time_to_event_hosp_"))[c_across(starts_with("event_hosp_")) == 1]
        if (any(!is.na(times))) min(times, na.rm = TRUE) else NA_real_
      } else {
        NA_real_
      }
    }
  ) %>%
  ungroup() %>% select(record_id,side_effect,time_to_side_effect)

side_effect <- side_effect %>% mutate(
  side_effect = case_when(
    side_effect == 1 & time_to_side_effect > 90 ~ 0,
    T ~ side_effect
  ),
  time_to_side_effect = case_when(
    side_effect == 1 & time_to_side_effect > 90 ~ 90,
    side_effect ==
      0 ~ 90,
    T ~ time_to_side_effect
    
  )
)
      
                          
```


# create drugs
```{r,include=FALSE}

create_drug_indicators <- function(data) {
  
  # Create indicator for Bevacizumab
  data$Bevacizumab <- ifelse(grepl("Bevacizumab|Avastin", data$regimen_dose, ignore.case = TRUE), 1, 0)
  
  # Create indicator for Paclitaxel
  data$Paclitaxel <- ifelse(grepl("Paclitaxel|Taxol|Abraxane", data$regimen_dose, ignore.case = TRUE), 1, 0)
  
  # Create indicator for Pemetrexed
  data$Pemetrexed <- ifelse(grepl("Pemetrexed|pem\\b", data$regimen_dose, ignore.case = TRUE), 1, 0)
  
  # Create indicator for Durvalumab
  data$Durvalumab <- ifelse(grepl("Durvalumab|Durva", data$regimen_dose, ignore.case = TRUE), 1, 0)
  
  # Create indicator for Doxorubicin
  data$Doxorubicin <- ifelse(grepl("Doxorubicin|Adriamycin", data$regimen_dose, ignore.case = TRUE), 1, 0)
  
  # Create indicator for Pembrolizumab
  data$Pembrolizumab <- ifelse(grepl("Pembrolizumab|Pembro", data$regimen_dose, ignore.case = TRUE), 1, 0)
  
  # Create indicator for Etoposide
  data$Etoposide <- ifelse(grepl("Etoposide|etop\\b", data$regimen_dose, ignore.case = TRUE), 1, 0)
  
  # Create indicator for Gemcitabine
  data$Gemcitabine <- ifelse(grepl("Gemcitabine|\\bGem\\b", data$regimen_dose, ignore.case = TRUE), 1, 0)
  
  # Create indicator for Atezolizumab
  data$Atezolizumab <- ifelse(grepl("Atezolizumab", data$regimen_dose, ignore.case = TRUE), 1, 0)
  
  # Create indicator for Pertuzumab
  data$Pertuzumab <- ifelse(grepl("Pertuzumab", data$regimen_dose, ignore.case = TRUE), 1, 0)
  
  # Create indicator for Trastuzumab
  data$Trastuzumab <- ifelse(grepl("Trastuzumab|Traztuzumab|Transtuzumab|Herceptin", 
                                   data$regimen_dose, ignore.case = TRUE), 1, 0)
  
  # Create indicator for Docetaxel
  data$Docetaxel <- ifelse(grepl("Docetaxel|Taxotere", data$regimen_dose, ignore.case = TRUE), 1, 0)
  
  # Create indicator for Fluorouracil
  data$Fluorouracil <- ifelse(grepl("Fluorouracil|5FU", data$regimen_dose, ignore.case = TRUE), 1, 0)
  
  # Create indicator for Methotrexate
  data$Methotrexate <- ifelse(grepl("Methotrexate", data$regimen_dose, ignore.case = TRUE), 1, 0)
  
  # Create indicator for Vinblastine
  data$Vinblastine <- ifelse(grepl("Vinblastine", data$regimen_dose, ignore.case = TRUE), 1, 0)
  
  # Create indicator for Administered alone (absence of all the above drugs)
  all_drugs <- c("Bevacizumab", "Paclitaxel", "Pemetrexed", "Durvalumab", "Doxorubicin",
                 "Pembrolizumab", "Etoposide", "Gemcitabine", "Atezolizumab", "Pertuzumab",
                 "Trastuzumab", "Docetaxel", "Fluorouracil", "Methotrexate", "Vinblastine")
  
  data$Administered_alone <- ifelse(rowSums(data[, all_drugs]) == 0, 1, 0)
  
  return(data)
}

```


#check 1  Read master 709 and combine Redcap
```{r,include=FALSE}
cleaned_master <- read_xlsx('/Users/to909/Downloads/master_709.xlsx') %>% rename(record_id=Record_ID)

cleaned_master <- standardize_colnames(cleaned_master)

cleaned_master <- cleaned_master %>% select(record_id,32:96,99:116)



final_master <- master %>% filter(record_id %in% cleaned_master$record_id) %>% merge(side_effect,by="record_id",all.x = T) 

final_master <- final_master %>% merge(cleaned_master,by="record_id",all.x = T)

final_master <- create_drug_indicators(final_master)



                                       
# select(record_id,Last_Known_Follow_Up,Baseline_Sample_Date,Patient_Status,baseline_creatinine)




#check 2 create new variables not in  data



final_master <- final_master  %>% rename(Last_Known_Follow_Up=fu_date,Baseline_Sample_Date=bl_date,
                                        Patient_Status=pt_status,EMPI=empi,
                                        Platin_Group_carboplatin_vs_cisplatin=platin_group,
                                        IF_cisplatin_add_dose_mg_m_2_number_only_IF_carboplatin_add_AUC_number_only=platin_dose,
                                        )

final_master$Last_Known_Follow_Up <- as.Date(final_master$Last_Known_Follow_Up)
final_master$Baseline_Sample_Date <- as.Date(final_master$Baseline_Sample_Date)
final_master$IF_cisplatin_add_dose_mg_m_2_number_only_IF_carboplatin_add_AUC_number_only <- as.numeric(final_master$IF_cisplatin_add_dose_mg_m_2_number_only_IF_carboplatin_add_AUC_number_only)
final_master$baseline_cre_egfr <- as.numeric(final_master$baseline_cre_egfr)

final_master <- final_master %>% mutate(days_last_follow_up=as.numeric(Last_Known_Follow_Up - Baseline_Sample_Date))

final_master <- final_master %>% mutate(Patient_Status=case_when(Patient_Status==1 ~ "Alive",
                                                                 Patient_Status==2 ~ "On Hospice",
                                                                 Patient_Status==3 ~ "Dead"))
final_master <- final_master %>% mutate(
  time_to_death_90 = ifelse(
    days_last_follow_up > 90,
    90,
    days_last_follow_up
  ),
  time_to_death_90_status = case_when(days_last_follow_up> 90 ~ 0,
 days_last_follow_up<= 90 & Patient_Status == "Dead" ~ 2,
 days_last_follow_up<= 90 & Patient_Status != "Dead" ~ 0),
 death_90=ifelse(time_to_death_90_status==2,1,0))

for (i in 1:11) {
  event_col <- paste0("event_hosp_", i)
  time_col <- paste0("time_to_event_hosp_", i)
  
  final_master[[time_col]][final_master[[event_col]] == 0] <- 90
}

# final_master <- final_master %>% mutate(side_effect=ifelse(side_effect==1,2,0))
###### check 

cmp_variable <- function(data, event_time, event_status, name) {
  # Enquote the time and status variables to allow their evaluation within the data context
  event_time <- enquo(event_time)
  event_status <- enquo(event_status)
  
  
  # Create dynamic names for the new columns
  cmp_time_name <- paste0("cmp_time_", name)
  cmp_status_name <- paste0("cmp_status_", name)
  
  # Add new columns to the dataset using mutate()
  data %>%
    mutate(
      !!cmp_time_name := ifelse(time_to_death_90 <= !!event_time ,time_to_death_90,!!event_time),
      !!cmp_status_name := ifelse(time_to_death_90 <= !!event_time,time_to_death_90_status,!!event_status)
    )
}



final_master <-  cmp_variable(final_master,event_time = time_to_side_effect, event_status = side_effect,name="side_effect")
final_master <-  cmp_variable(final_master,event_time = time_to_event_hosp_1, event_status = event_hosp_1,name="hosp_1")
final_master <-  cmp_variable(final_master,event_time = time_to_event_hosp_2, event_status = event_hosp_2,name="hosp_2")
final_master <-  cmp_variable(final_master,event_time = time_to_event_hosp_3, event_status = event_hosp_3,name="hosp_3")
final_master <-  cmp_variable(final_master,event_time = time_to_event_hosp_4, event_status = event_hosp_4,name="hosp_4")
final_master <-  cmp_variable(final_master,event_time = time_to_event_hosp_5, event_status = event_hosp_5,name="hosp_5")
final_master <-  cmp_variable(final_master,event_time = time_to_event_hosp_6, event_status = event_hosp_6,name="hosp_6")
final_master <-  cmp_variable(final_master,event_time = time_to_event_hosp_7, event_status = event_hosp_7,name="hosp_7")
final_master <-  cmp_variable(final_master,event_time = time_to_event_hosp_8, event_status = event_hosp_7,name="hosp_8")
final_master <-  cmp_variable(final_master,event_time = time_to_event_hosp_9, event_status = event_hosp_7,name="hosp_9")
final_master <-  cmp_variable(final_master,event_time = time_to_event_hosp_10, event_status = event_hosp_7,name="hosp_10")
final_master <-  cmp_variable(final_master,event_time = time_to_event_hosp_11, event_status = event_hosp_7,name="hosp_11")





```



# rpdr 
```{r,include=FALSE}


#dia
dia <- read.table("/Users/to909/Partners HealthCare Dropbox/Tianqi Ouyang/Thoracic Oncology Spreadsheets/RPDR 800/mes98_051625135308675085_Dia.txt", sep = '|',
                  fill = TRUE,
                  quote = "",
                  header = T)

dia$Date <- as.Date(dia$Date,"%m/%d/%Y")



lab <- read.table('/Users/to909/Partners HealthCare Dropbox/Tianqi Ouyang/Thoracic Oncology Spreadsheets/RPDR 800/mes98_051625135308675085_Lab.txt', sep = '|',
                  fill = TRUE,
                  quote = "",
                  header = T)%>% select(EMPI,Seq_Date_Time,Result,Group_Id,Test_Description)  

lab$Seq_Date_Time <- as.Date(lab$Seq_Date_Time, "%m/%d/%Y")

master_list <- final_master %>% select(EMPI,Baseline_Sample_Date)

master_lab <- merge(master_list,lab,by="EMPI",all.y = T)
master_dia <- merge(master_list,dia,by="EMPI",all.y = T)


``` 

# create missing labs pre_HGB_45days
```{r}
###### pre lab  index data included closest date 
pre_lab <- function(data, month, time, index_date, Group_Id) {
  index_date <- enquo(index_date)
  if (month) {
    time_value <- time * 30
  } else {
    time_value <- time
  }
  
  
  lab_name <- paste0("pre_", Group_Id, "_", time_value, "days")
  lab_date_name <- paste0("pre_", Group_Id, "_", time_value, "days_date")
  
  result <- data %>% 
    filter(Group_Id == !!Group_Id, grepl("^\\d+\\.\\d+$", Result)) %>% 
    filter(!is.na(Result)) %>% 
    mutate(Result = as.numeric(Result)) %>% 
    filter(Seq_Date_Time >= (!!index_date) - time_value, Seq_Date_Time <= !!index_date) %>% 
    arrange(EMPI, desc(Seq_Date_Time)) %>% 
    distinct(EMPI, .keep_all = TRUE) %>% 
    rename(!!lab_name := Result,
           !!lab_date_name := Seq_Date_Time) %>% 
    select(EMPI,
           !!lab_name, !!lab_date_name)
  
  return(result)
}

###### outcome Lab 


pre_HGB_45days <- pre_lab(master_lab, month=F, time=45, index_date=Baseline_Sample_Date, Group_Id="HGB")

pre_HGB_45days <- pre_lab(master_lab, month=F, time=45, index_date=Baseline_Sample_Date, Group_Id="HGB")
```





# Jiaxuan's code create variables

```{r,include=FALSE}

final_master <- final_master  %>%
  mutate(across(
    .cols = c( 
              post_Anemia_2_cutpoint_90days_date, post_Anemia_3_cutpoint_90days_date, 
              # post_Neutro_2_cutpoint_90days_date, post_Neutro_3_cutpoint_90days_date, 
              post_Throm_2_cutpoint_90days_date, post_Throm_3_cutpoint_90days_date, 
              post_AKI_2_cutpoint_90days_date,post_AKI_3_cutpoint_90days_date),
    .fns = ~as.Date(., format='%m/%d/%Y')
  ))


final_master <- final_master %>%
  mutate(bmi_cat = case_when(bmi< 18.5 ~ 1,
                             bmi >= 18.5 & bmi < 25 ~ 2,
                             bmi >= 25 & bmi < 30 ~ 3,
                             bmi >= 30 ~ 4,
                             TRUE ~ NA_real_
                             ))

table(final_master$bmi_cat)


##platinum categories
final_master <- final_master%>%
  mutate(carbo = ifelse(Platin_Group_carboplatin_vs_cisplatin == "Carboplatin",1,0))%>%
   mutate(carbo_dose = case_when(
     carbo==1 ~IF_cisplatin_add_dose_mg_m_2_number_only_IF_carboplatin_add_AUC_number_only,
     carbo==0~NA
   ))%>%
  mutate(cis = ifelse(Platin_Group_carboplatin_vs_cisplatin == "Cisplatin",1,0))%>%
   mutate(cis_dose = case_when(
     cis==1 ~IF_cisplatin_add_dose_mg_m_2_number_only_IF_carboplatin_add_AUC_number_only,
     cis==0~NA
   ))%>%
  mutate(carbo_AUC =case_when(
     carbo==1 ~IF_cisplatin_add_dose_mg_m_2_number_only_IF_carboplatin_add_AUC_number_only,
     carbo==0~NA
   ))%>% 
 mutate(cis_recommend =case_when(
     cis==1 ~IF_cisplatin_add_dose_mg_m_2_number_only_IF_carboplatin_add_AUC_number_only,
     cis==0~NA
   ))


final_master <- final_master%>%
  mutate(cis_group = case_when(
    cis_recommend < 40 ~1,
    cis_recommend>=40 & cis_recommend<60 ~2,
    cis_recommend >=60 ~ 3,
    TRUE ~ NA
  ))



#generate new variable dose: 0 = low dose; 1= high dose


final_master<- final_master %>%
  mutate(dose_1 = case_when(
    carbo_AUC >= 5 | cis_dose >=75 ~ 1,
    carbo_AUC < 5 | cis_dose < 75 ~ 0,
    TRUE ~ NA_real_
  ))%>%
  mutate (dose_1 = as.factor(dose_1))
  

##generate carbo_auc_cat
final_master <- final_master%>%
  mutate(carbo_AUC_cat = case_when(
    carbo_AUC<= 4 ~ 1,
    carbo_AUC>= 5 ~2,
    TRUE ~  0
  ))

table(final_master$carbo_AUC_cat)


## generate cis_dose_cat


final_master <- final_master%>%
  mutate(cis_dose_cat = case_when(
    cis_dose< 75  ~ 1,
    cis_dose >= 75  ~ 2,
    TRUE ~ 0
  ))

table(final_master$cis_dose_cat)

##generate outcomes as Anemia_g2_90days,Throm_g2_90days,Neutro_g2_90days,AKI_g2_90days,and grade3 AEs

final_master <- final_master%>%
  mutate(Anemia_g2_90days = ifelse(!is.na(post_Anemia_2_cutpoint_90days),1,0))%>%
  mutate(Anemia_g3_90days = ifelse(!is.na(post_Anemia_3_cutpoint_90days),1,0))%>%
  mutate(Throm_g2_90days = ifelse(!is.na(post_Throm_2_cutpoint_90days),1,0))%>%
  mutate(Throm_g3_90days = ifelse(!is.na(post_Throm_3_cutpoint_90days),1,0))%>%
  # mutate(Neutro_g2_90days = ifelse(!is.na(post_Neutro_2_cutpoint_90days),1,0))%>%
  # mutate(Neutro_g3_90days=ifelse(!is.na(post_Neutro_3_cutpoint_90days),1,0))%>%
  mutate(AKI_g2_90days = ifelse(!is.na(post_AKI_2_cutpoint_90days),1,0))%>%
  mutate(AKI_g3_90days = ifelse(!is.na(post_AKI_3_cutpoint_90days),1,0))


## generate time to AEs
final_master <- final_master%>%
  mutate(time_to_anemia_2 = post_Anemia_2_cutpoint_90days_date - Baseline_Sample_Date)%>%
  mutate(time_to_anemia_3 = post_Anemia_3_cutpoint_90days_date - Baseline_Sample_Date)%>%
  mutate(time_to_throm_2 = post_Throm_2_cutpoint_90days_date - Baseline_Sample_Date)%>%
  mutate(time_to_throm_3 = post_Throm_3_cutpoint_90days_date - Baseline_Sample_Date)%>%
  mutate(time_to_aki_2 = post_AKI_2_cutpoint_90days_date - Baseline_Sample_Date)%>%
  mutate(time_to_aki_3 = post_AKI_3_cutpoint_90days_date - Baseline_Sample_Date)


final_master <- final_master %>%
  mutate(across(
    c(time_to_anemia_2, time_to_anemia_3,
      time_to_throm_2, time_to_throm_3,
      time_to_aki_2, time_to_aki_3),
    ~ ifelse(is.na(.), 0, .)
  ))


##filter cystatin C isn't NA(3 patient), platinum isn't NA(1 patient)
final_master <- final_master %>%
  mutate(cys_c_baseline = as.numeric(cys_c_baseline)) %>%
  filter(!is.na(cys_c_baseline)) %>%
  filter(!is.na(Platin_Group_carboplatin_vs_cisplatin))



library(dplyr)

hosp <-  final_master %>%
  dplyr::select(record_id,matches("hos|ed|extra|egfr|exposure"))



## we have other exposures
final_master<- final_master%>%
  mutate(exposure_epi_30 = ifelse(baseline_cys_c_egfr < 0.7*baseline_cre_egfr,1,0))


final_master<- final_master%>%
  mutate(exposure_cg_30 = ifelse(ckd_epi_gfr_cre_cys_unindex < 0.7*cockcroft,1,0))


final_master<- final_master%>%
  mutate(exposure_cg_15 = ifelse(ckd_epi_gfr_cre_cys_unindex < 0.85*cockcroft,1,0))

##generate new exposure as cr/cys 
final_master$cr_cys <-final_master$baseline_creatinine/final_master$cys_c_baseline

  
final_master<- final_master%>%
  mutate(cr_cys_cat = case_when(
    cr_cys < 0.5 ~1,
    cr_cys >=0.5 & cr_cys <0.7 ~ 2,
    cr_cys >=0.7 & cr_cys <0.9 ~ 3,
    cr_cys >= 0.9  ~ 4
  )
           )

final_master$cr_cys_cat <- factor(final_master$cr_cys_cat, 
                           levels = c("1", "2", "3", "4"), 
                           labels = c("< 0.5", "0.5-0.7", "0.7-0.9", "≥ 0.9")) 


table(final_master$cr_cys_cat)

##generate new exposure as cr/cys < 0.7
final_master$cr_cys_7 <-ifelse(final_master$cr_cys < 0.7, 1, 0) 
table(final_master$cr_cys_7)


##rename the side_effect_hos to platinum_related_hosp


##lumping all grade 2 AEs as grade_2_aes; the same with grade_3_aes
final_master <- final_master%>%
  mutate( grade_2_aes = case_when(
    Anemia_g2_90days == 1 | Throm_g2_90days == 1 | AKI_g2_90days == 1 ~ 1,
    TRUE ~ 0
  ) ) %>%
  
mutate( grade_3_aes = case_when(
    Anemia_g3_90days == 1 | Throm_g3_90days == 1 | AKI_g3_90days == 1 ~ 1,
    TRUE ~ 0
  ) ) 

table(final_master$cr_cys_7,final_master$grade_2_aes)

table(final_master$cr_cys_7,final_master$grade_3_aes)



final_master <- final_master%>%
  mutate(age_cat = case_when(
    age <= 65 ~ 1,
    age> 65 & age <= 80 ~2,
    age> 80  ~3
  ))%>%
  mutate(ici = ifelse(Atezolizumab == 1 | Pembrolizumab == 1 | Durvalumab == 1 , 1 , 0))%>%
  mutate(ckd_stage_cg = case_when(
    cockcroft >= 90 ~ 1,
    cockcroft >= 60 & cockcroft < 90 ~ 2,
    cockcroft >= 30 & cockcroft < 60 ~ 3,
    cockcroft >= 15 & cockcroft < 30 ~ 4,
    cockcroft < 15  ~ 5))%>%
  mutate(ckd_stage_cg = as.factor(ckd_stage_cg))

```




# create charlson score
```{r}
library(comorbidity)

### Charlson comorbidity index
ici_diag <-  dia %>% subset(select = c(EMPI, Diagnosis_Name, Date, Code, Code_Type))
ici_diag <- ici_diag %>% merge(final_master,by="EMPI",all.y = T)
ici_diag$Date <- as.Date(ici_diag$Date, "%m/%d/%Y")
ici_diag_pre <- subset(ici_diag, Date < Baseline_Sample_Date)

leukemia <- ici_diag_pre[grep("leukemia", ici_diag_pre$Diagnosis_Name, ignore.case = TRUE), ]
leukemia <- leukemia[!grepl("lymphoma", leukemia$Diagnosis_Name, ignore.case = TRUE),]
leukemia = as.data.frame(table(leukemia$EMPI))
names(leukemia)[names(leukemia) == "Var1"] <- "EMPI"
names(leukemia)[names(leukemia) == "Freq"] <- "leukemia"
leukemia$leukemia[leukemia$leukemia >0] =1

lymphoma <- ici_diag_pre[grep("lymphoma", ici_diag_pre$Diagnosis_Name, ignore.case = TRUE), ]
lymphoma <- lymphoma[!grepl("leukemia", lymphoma$Diagnosis_Name, ignore.case = TRUE),]
lymphoma = as.data.frame(table(lymphoma$EMPI))
names(lymphoma)[names(lymphoma) == "Var1"] <- "EMPI"
names(lymphoma)[names(lymphoma) == "Freq"] <- "lymphoma"
lymphoma$lymphoma[lymphoma$lymphoma >0] =1

leuk_lymph = merge(leukemia, lymphoma, by = "EMPI", all = T)

diag_icd9 <- subset(ici_diag_pre, Code_Type == "ICD9")
diag_icd10 <- subset(ici_diag_pre, Code_Type == "ICD10")

diag_icd9 <- subset(diag_icd9, select = c("EMPI", "Code"))
diag_icd10 <- subset(diag_icd10, select = c("EMPI", "Code"))

diag_icd9 <- diag_icd9[!(diag_icd9$Code == ""),]
diag_icd10 <- diag_icd10[!(diag_icd10$Code == ""),]

charlson9 <- comorbidity(x = diag_icd9, id = "EMPI", code = "Code", map = "charlson_icd9_quan", assign0 = FALSE)
charlson10 <- comorbidity(x = diag_icd10, id = "EMPI", code = "Code", map = "charlson_icd10_quan", assign0 = FALSE)

charlson = merge(charlson9, charlson10, by = "EMPI", all = T)
charlson[is.na(charlson)] = 0


charlson$ami = pmax(charlson$mi.x, charlson$mi.y)
charlson$chf = pmax(charlson$chf.x, charlson$chf.y)
charlson$pvd = pmax(charlson$pvd.x, charlson$pvd.y)
charlson$cevd = pmax(charlson$cevd.x, charlson$cevd.y)
charlson$dementia = pmax(charlson$dementia.x, charlson$dementia.y)
charlson$copd = pmax(charlson$cpd.x, charlson$cpd.y)
charlson$rheumd = pmax(charlson$rheumd.x, charlson$rheumd.y)
charlson$pud = pmax(charlson$pud.x, charlson$pud.y)
charlson$mld = pmax(charlson$mld.x, charlson$mld.y)
charlson$diab = pmax(charlson$diab.x, charlson$diab.y)
charlson$diabwc = pmax(charlson$diabwc.x, charlson$diabwc.y)
charlson$hp = pmax(charlson$hp.x, charlson$hp.y)
charlson$rend = pmax(charlson$rend.x, charlson$rend.y)
charlson$canc = pmax(charlson$canc.x, charlson$canc.y)
charlson$msld = pmax(charlson$msld.x, charlson$msld.y)
charlson$metacanc = pmax(charlson$metacanc.x, charlson$metacanc.y)
charlson$aids = pmax(charlson$aids.x, charlson$aids.y)
charlson = charlson %>% subset(select = c(EMPI, ami, chf, pvd, cevd, dementia, copd, rheumd, pud, mld,
                                          diab, diabwc, hp, rend, canc, msld, metacanc, aids))
charlson$canc = 1
charlson = merge(charlson, leuk_lymph, by = "EMPI", all = T)
charlson[is.na(charlson)] = 0

ages = final_master %>% subset(select = c(EMPI, age))

charlson = merge(charlson, ages, by.x = 1, by.y = 1)

charlson$score = charlson$ami + charlson$chf + charlson$pvd + charlson$cevd +
  charlson$dementia + charlson$copd + charlson$rheumd + charlson$pud +
  ifelse(charlson$mld == 1 & charlson$msld == 0, 1, 0) + ifelse(charlson$msld ==1, 3, 0) +
  charlson$diab + charlson$diabwc + charlson$hp*2 + charlson$rend*2 + charlson$canc*2 +
  charlson$metacanc*4 + charlson$aids*6 + charlson$leukemia*2 + charlson$lymphoma*2 +
  ifelse(charlson$age >= 50 & charlson$age <60, 1, 0) +
  ifelse(charlson$age >= 60 & charlson$age <70, 2, 0) +
  ifelse(charlson$age >= 70 & charlson$age <80, 3, 0) +
  ifelse(charlson$age >= 80, 4, 0)

charlson_sc = charlson %>% subset(select = c(EMPI, score))
charlson_sc$cci = ifelse(charlson_sc$score<3, "mild", ifelse(charlson_sc$score >= 3 & charlson_sc$score <5, "moderate", "severe"))
```


#12 add varibles to data  and rename 
```{r}
final_master <- final_master %>% merge(charlson_sc,by="EMPI",all.x = T) 

final_master <- final_master %>% rename(baseline_cre = baseline_creatinine,
         baseline_cystatin_c = cys_c_baseline,
         cancer_stage = tumor_stage)

```




# add new RPDR
```{r,include=FALSE}


#Lab

lab <- read.table('/Users/to909/Partners HealthCare Dropbox/Tianqi Ouyang/Thoracic Oncology Spreadsheets/RPDR 800/mes98_071025164203189492_Lab.txt', sep = '|',
                  fill = TRUE,
                  quote = "",
                  header = T)%>% select(EMPI,Seq_Date_Time,Result,Group_Id,Test_Description)  

lab$Seq_Date_Time <- as.Date(lab$Seq_Date_Time, "%m/%d/%Y")


master_list <- final_master %>% select(EMPI,Baseline_Sample_Date)
master_lab <- merge(master_list,lab,by="EMPI",all.x = T)
master_lab <- master_lab %>% mutate(Group_Id=ifelse(is.na(Group_Id),"NA",Group_Id))


```

# add NA MG K 
```{r,include=FALSE}
pre_NA_45days <- pre_lab(master_lab, month=F, time=45, index_date=Baseline_Sample_Date, Group_Id="NA")
pre_MG_45days <- pre_lab(master_lab, month=F, time=45, index_date=Baseline_Sample_Date, Group_Id="MG")
pre_K_45days <- pre_lab(master_lab, month=F, time=45, index_date=Baseline_Sample_Date, Group_Id="K")

pre_K_45days <- pre_K_45days %>% mutate(ifelse(pre_K_45days_date=="2023-08-09" & EMPI=="107667951" ,7.7,pre_K_45days))
# 107667951 - 7.7 baseline 
final_master <- final_master %>% merge(pre_NA_45days,by="EMPI",all.x = T)
final_master <- final_master %>% merge(pre_MG_45days,by="EMPI",all.x = T)
final_master <- final_master %>% merge(pre_K_45days,by="EMPI",all.x = T)

```


# create Hypokalemia_value Hypomagnesemia_value Hyponatremia_value
```{r}
final_master$Baseline_Sample_Date <- as.Date(final_master$Baseline_Sample_Date)


## post lab cutoff function 
post_lab_less_than_cutpoint <- function(data,days,index_date,Group_ID,Group_ID_name,outcome_name,cutpoint) {
  index_date <- enquo(index_date)
  lab_name <- paste0("post_", Group_ID_name, "_cutpoint_", days, "days")
  lab_date_name <- paste0("post_", Group_ID_name, "_cutpoint_", days, "days_date")
  
  result <- data %>% 
    filter(Group_Id %in% Group_ID) %>% 
    filter(grepl("^[><]?\\d+\\.?\\d* ?$",Result)) %>% 
    mutate(Result=as.numeric(parse_number(Result))) %>% 
    filter(!is.na(Result)) %>% 
    filter(Seq_Date_Time > (!!index_date), Seq_Date_Time <= !!index_date + days) %>%
    filter(Result<cutpoint) %>% 
    arrange(EMPI,Seq_Date_Time) %>% 
    distinct(EMPI, .keep_all = TRUE) %>% 
    rename(!!lab_name := Result,
           !!lab_date_name := Seq_Date_Time) %>% 
    select(EMPI,
           !!lab_name, !!lab_date_name)
  return(result)
}


#get cutoff outcome 

Hypokalemia_value <- post_lab_less_than_cutpoint(data=master_lab,days=90,index_date=Baseline_Sample_Date,Group_ID="K",Group_ID_name="Hypokalemia",cutpoint=3)
Hypomagnesemia_value <- post_lab_less_than_cutpoint(data=master_lab,days=90,index_date=Baseline_Sample_Date,Group_ID="MG",Group_ID_name="Hypomagnesemia",cutpoint=0.9)
Hyponatremia_value <- post_lab_less_than_cutpoint(data=master_lab,days=90,index_date=Baseline_Sample_Date,Group_ID="NA",Group_ID_name="Hyponatremia",cutpoint=125)


final_master <- final_master %>% merge(Hypokalemia_value,by="EMPI",all.x = T)
final_master <- final_master %>% merge(Hypomagnesemia_value,by="EMPI",all.x = T)
final_master <- final_master %>% merge(Hyponatremia_value,by="EMPI",all.x = T)


final_master <- final_master%>%
  mutate(time_to_Hypomagnesemia = post_Hypomagnesemia_cutpoint_90days_date - Baseline_Sample_Date)%>%
  mutate(time_to_Hypokalemia= post_Hypokalemia_cutpoint_90days_date - Baseline_Sample_Date) %>% 
  mutate(time_to_Hyponatremia = post_Hyponatremia_cutpoint_90days_date - Baseline_Sample_Date) %>% 
  mutate(Hypomagnesemia_90days = ifelse(!is.na(post_Hypomagnesemia_cutpoint_90days),1,0))%>%
  mutate(Hypokalemia_90days = ifelse(!is.na(post_Hypokalemia_cutpoint_90days),1,0)) %>% 
   mutate(Hyponatremia_90days = ifelse(!is.na(post_Hyponatremia_cutpoint_90days),1,0)) 
  

final_master <- final_master %>%
  mutate(
    time_to_Hypomagnesemia = ifelse(is.na(time_to_Hypomagnesemia), 90, time_to_Hypomagnesemia),
    time_to_Hypokalemia = ifelse(is.na(time_to_Hypokalemia), 90, time_to_Hypokalemia),
    time_to_Hyponatremia = ifelse(is.na(time_to_Hyponatremia), 90, time_to_Hyponatremia)
  )



final_master <-  cmp_variable(final_master,event_time = time_to_Hypomagnesemia, event_status = Hypomagnesemia_90days,name="Hypomagnesemia")
final_master <-  cmp_variable(final_master,event_time = time_to_Hypokalemia, event_status = Hypokalemia_90days,name="Hypokalemia")
final_master <-  cmp_variable(final_master,event_time = time_to_Hyponatremia, event_status = Hyponatremia_90days,name="Hyponatremia")

```






# create factors
```{r,include=FALSE}
# write_xlsx(final_master, path = '/Users/to909/Desktop/R code/final_master.xlsx')

final_master <- final_master %>%
  mutate(across(contains("cmp_status_"), as.factor))

final_master <- final_master%>%
  mutate(
         age_cat = case_when(
    age <= 65 ~ 1,
    age> 65 & age <= 80 ~2,
    age> 80  ~3
  ),
  ici = ifelse(Atezolizumab == 1 | Pembrolizumab == 1 | Durvalumab == 1 , 1 , 0))




```


```{r,include=FALSE}
#dia
dia <- read.table("/Users/to909/Partners HealthCare Dropbox/Tianqi Ouyang/Thoracic Oncology Spreadsheets/RPDR 800/mes98_051625135308675085_Dia.txt", sep = '|',
                  fill = TRUE,
                  quote = "",
                  header = T)

dia$Date <- as.Date(dia$Date,"%m/%d/%Y")



lab <- read.table('/Users/to909/Partners HealthCare Dropbox/Tianqi Ouyang/Thoracic Oncology Spreadsheets/RPDR 800/mes98_051625135308675085_Lab.txt', sep = '|',
                  fill = TRUE,
                  quote = "",
                  header = T)%>% select(EMPI,Seq_Date_Time,Result,Group_Id,Test_Description)  

lab$Seq_Date_Time <- as.Date(lab$Seq_Date_Time, "%m/%d/%Y")

master_list <- final_master %>% select(EMPI,Baseline_Sample_Date)


med <- read.table("/Users/to909/Partners HealthCare Dropbox/Tianqi Ouyang/Thoracic Oncology Spreadsheets/RPDR 800/mes98_051625135308675085_Med.txt",
                  sep = '|',
                  fill = TRUE,
                  quote = "",
                  header = T) %>% select(EMPI,Medication_Date,Medication)
med$Medication_Date <- as.Date(med$Medication_Date, "%m/%d/%Y")


master_lab <- merge(master_list,lab,by="EMPI",all.y = T)
master_dia <- merge(master_list,dia,by="EMPI",all.y = T)
  master_med <- merge(master_list,med,by="EMPI",all.y = T)



dia_list_name <- function(data, listed_names, index_date, excluded_names = NULL, med_data = NULL, med_names = NULL) {
  # 
  if (!is.null(excluded_names)) {
    excluded_pattern <- paste(
      gsub("([][()])", "\\\\\\1", excluded_names),  # 
      collapse = "|"
    )
  }
  
  if (is.null(excluded_names)) {
    dia_result <- data %>%  
      filter(Date <= {{index_date}}) %>% 
      filter(grepl(paste(listed_names, collapse = "|"), Diagnosis_Name, ignore.case = TRUE)) %>% 
      distinct(EMPI)
  } else {
    dia_result <- data %>%  
      filter(Date <= {{index_date}}) %>% 
      filter(
        grepl(paste(listed_names, collapse = "|"), Diagnosis_Name, ignore.case = TRUE),
        !grepl(excluded_pattern, Diagnosis_Name, ignore.case = TRUE)  # 
      ) %>% 
      distinct(EMPI)
  }
  
  if (!is.null(med_data)) {
    med_result <- med_data %>%  
      filter(Medication_Date <= {{index_date}}) %>% 
      filter(grepl(paste(med_names, collapse = "|"), Medication, ignore.case = TRUE)) %>% 
      distinct(EMPI)
  } else {
    med_result <- NULL
  }
  
  final_result <- rbind(dia_result, med_result) %>% 
    distinct(EMPI)
  
  return(final_result)
}
  


thyroid <- c ("hypothyroidism","hyperthyroidism","thyroiditis")
thyroid_med_list <- c ("Methimazole","Tapazole","Propylthiouracil","Potassium Iodide","Radioactive Iodine ","levothyroxine","Euthyrox", "Synthroid", "Eltroxin","Desiccated Thyroid Extract","Armour Thyroid")

thyroid_final <- dia_list_name(master_dia,listed_names = thyroid,med_data= master_med,med_names= thyroid_med_list,index_date = Baseline_Sample_Date)


final_master <- final_master %>% mutate(thyroid=ifelse(EMPI %in% thyroid_final$EMPI,1,0))

```

# add missing 
```{r}
# final_master <- final_master %>% mutate(cancer_stage=case_when(record_id==492 ~ 1,
#                                                                record_id==695 ~ 2,
#                                                                T ~ cancer_stage))
 write_xlsx(final_master, path = '/Users/to909/Desktop/R code/final_master.xlsx')
```


#Table one 
## for cre/cys ratio 

```{r}
##dose_1: carbo-AUC ≥ 5 mg/mL/min, or r cisplatin  ≥ 75 mg/m2
table_one_cc_ratio <- final_master%>%
  dplyr::select(age,age_cat,sex,Race,Ethnicity,cancer_stage,
                Platin_Group_carboplatin_vs_cisplatin,cis_dose,cis_dose_cat,carbo_dose, carbo_AUC, carbo_AUC_cat,dose_1,
                ici,Bevacizumab,Paclitaxel,Pemetrexed,Doxorubicin,Etoposide,Gemcitabine,Pertuzumab,Trastuzumab,Docetaxel,Fluorouracil,Methotrexate,Vinblastine,Administered_alone,
                dm,htn,cirrhosis,cad,hiv,ppi,ace_arb,diu,steroids,statins,nsaids,smoking,thyroid,
                score,bmi,bmi_cat,pre_HGB_45days,pre_PLT_45days,pre_ALB_45days,baseline_cystatin_c,baseline_cre,cockcroft,ckd_epi_gfr_cre_cys_unindex,ckd_stage_cg,cr_cys,cr_cys_7) %>%
  tbl_summary(statistic = list(age ~ "{mean} ({sd})"), 
              by = cr_cys_7,
            
    ) %>%
  add_overall() %>%
  add_p(
    test.args = list(
      all_categorical() ~ list(simulate.p.value = TRUE)
    )
  )
table_one_cc_ratio



all_vars <- c("age", "age_cat", "sex", "Race", "Ethnicity", "tumor_stage", "cancer_retype", 
  "Platin_Group_carboplatin_vs_cisplatin", "cis_dose", "cis_dose_cat", "carbo_dose", "carbo_AUC", "carbo_AUC_cat", "dose_1", 
  "ici", "Bevacizumab", "Paclitaxel", "Pemetrexed", "Doxorubicin", "Etoposide", "Gemcitabine", 
  "Pertuzumab", "Trastuzumab", "Docetaxel", "Fluorouracil", "Methotrexate", "Vinblastine", 
  "Administered_alone", "dm", "htn", "cirrhosis", "cad", "hiv_new", "ppi", "ace_arb", "diu", 
  "steroids", "statins", "nsaids", "smoking", "thyroid", "score", "ecog_values", "bmi", 
  "bmi_cat", "pre_WBC_45days", "pre_HGB_45days", "pre_PLT_45days", "pre_ALB_45days", 
  "baseline_cystatin_c", "baseline_cre", "cockcroft", "baseline_cre_egfr", 
  "baseline_cys_c_egfr", 
  "Baseline_Cystatin_C_Based_baseline_cre_egfr", 
  "baseline_cre_egfr_unindexed", 
  "baseline_cys_c_egfr_unindexed", "ckd_epi_gfr_cre_cys_unindex", "ckd_stage_cg", 
  "cr_cys", "cr_cys_7")




```









```{r}


tidycmprsk::crr(Surv(cmp_time_Hypokalemia,cmp_status_Hypokalemia)  ~ cr_cys_7 + age + sex +  bmi + smoking + steroids +  thyroid + cancer_stage  + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine +cockcroft+ pre_K_45days + ici+score,failcode=1,cencode=0, data = final_master) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))%>% add_n()

```


```{r}


tidycmprsk::crr(Surv(cmp_time_Hypomagnesemia,cmp_status_Hypomagnesemia)  ~ cr_cys_7 + age + sex +  bmi + smoking + steroids +  thyroid + cancer_stage  + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine +cockcroft+pre_MG_45days  + ici+score,failcode=1,cencode=0, data = final_master) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))%>% add_n()

```



```{r}


tidycmprsk::crr(Surv(cmp_time_Hyponatremia,cmp_status_Hyponatremia)  ~ cr_cys_7 + age + sex +  bmi + smoking + steroids +  thyroid + cancer_stage  + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine +cockcroft +pre_NA_45days+ ici+score,failcode=1,cencode=0, data = final_master) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3)) %>% add_n()


```



```{r}


tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect) ~ cr_cys_7 + age + sex +  bmi + smoking + steroids +  thyroid + cancer_stage  + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine +cockcroft + ici+score,failcode=1,cencode=0, data = final_master) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_anemia_2,cmp_status_anemia_2)  ~ cr_cys_7 + age + sex +  bmi + smoking + steroids +  thyroid + cancer_stage  + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine +cockcroft+ pre_HGB_45days + ici +score,failcode=1,cencode=0, data = final_master) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_anemia_3,cmp_status_anemia_3)  ~ cr_cys_7 + age + sex +  bmi + smoking + steroids +  thyroid + cancer_stage  + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine +cockcroft+ pre_HGB_45days+ ici +score,failcode=1,cencode=0, data = final_master) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_2,cmp_status_throm_2)  ~ cr_cys_7 + age + sex +  bmi + smoking + steroids +  thyroid + cancer_stage  + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine +cockcroft+ pre_PLT_45days+ ici+score,failcode=1,cencode=0, data = final_master) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_3,cmp_status_throm_3)  ~ cr_cys_7 + age + sex +  bmi + smoking + steroids +  thyroid + cancer_stage  + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine +cockcroft+pre_PLT_45days+ ici+score ,failcode=1,cencode=0, data = final_master) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


tidycmprsk::crr(Surv(cmp_time_aki_2,cmp_status_aki_2)  ~ cr_cys_7 + age + sex +  bmi + smoking + steroids +  thyroid + cancer_stage  + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine +cockcroft+ ici+score,failcode=1,cencode=0, data = final_master) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


tidycmprsk::crr(Surv(cmp_time_aki_3,cmp_status_aki_3)  ~ cr_cys_7 + age + sex +  bmi + smoking + steroids +  thyroid + cancer_stage  + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine +cockcroft+ ici+score,failcode=1,cencode=0, data = final_master) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_grade_2_aes,cmp_status_grade_2_aes)  ~ cr_cys_7 + age + sex +  bmi + smoking + steroids +  thyroid + cancer_stage  + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine +cockcroft+ pre_HGB_45days + pre_PLT_45days + ici+score,failcode=1,cencode=0, data = final_master) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


tidycmprsk::crr(Surv(cmp_time_grade_3_aes,cmp_status_grade_3_aes)  ~ cr_cys_7 + age + sex +  bmi + smoking + steroids +  thyroid + cancer_stage  + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine +cockcroft+pre_HGB_45days + pre_PLT_45days + ici+score,failcode=1,cencode=0, data = final_master) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

```





#1 
```{r}

library(tidycmprsk)
cuminc(Surv(cmp_time_side_effect, cmp_status_side_effect) ~ cr_cys_7, final_master) %>%
  ggcuminc() +
  add_confidence_interval() +
  add_risktable()+
   ggtitle("Cumulative Incidence of Side Effect by cr_cys_7 Group")



```



#1 
```{r}


cuminc(Surv(cmp_time_hosp_1, cmp_status_hosp_1) ~ cr_cys_7, final_master) %>%
  ggcuminc() +
  add_confidence_interval() +
  add_risktable()+
   ggtitle("Cumulative Incidence of cmp_time_hosp_1 by cr_cys_7 Group")

```





#2
```{r}

cuminc(Surv(cmp_time_hosp_2, cmp_status_hosp_2) ~ cr_cys_7, final_master) %>%
  ggcuminc() +
  add_confidence_interval() +
  add_risktable()+
   ggtitle("Cumulative Incidence of cmp_time_hosp_2 by cr_cys_7 Group")


```
#3 
```{r}
cuminc(Surv(cmp_time_hosp_3, cmp_status_hosp_3) ~ cr_cys_7, final_master) %>%
  ggcuminc() +
  add_confidence_interval() +
  add_risktable()+
   ggtitle("Cumulative Incidence of cmp_time_hosp_3 by cr_cys_7 Group")

```
#4
```{r}
cuminc(Surv(cmp_time_hosp_4, cmp_status_hosp_4) ~ cr_cys_7, final_master) %>%
  ggcuminc() +
  add_confidence_interval() +
  add_risktable()+
   ggtitle("Cumulative Incidence of cmp_time_hosp_4 by cr_cys_7 Group")

```
#5
```{r}
cuminc(Surv(cmp_time_hosp_5, cmp_status_hosp_5) ~ cr_cys_7, final_master) %>%
  ggcuminc() +
  add_confidence_interval() +
  add_risktable()+
   ggtitle("Cumulative Incidence of cmp_time_hosp_5 by cr_cys_7 Group")


```
#6
```{r}
cuminc(Surv(cmp_time_hosp_6, cmp_status_hosp_6) ~ cr_cys_7, final_master) %>%
  ggcuminc() +
  add_confidence_interval() +
  add_risktable()+
   ggtitle("Cumulative Incidence of cmp_time_hosp_6 by cr_cys_7 Group")


```



#7
```{r}

cuminc(Surv(cmp_time_hosp_7, cmp_status_hosp_7) ~ cr_cys_7, final_master) %>%
  ggcuminc() +
  add_confidence_interval() +
  add_risktable()+
   ggtitle("Cumulative Incidence of cmp_time_hosp_7 by cr_cys_7 Group")


```

#8
```{r}

cuminc(Surv(cmp_time_hosp_8, cmp_status_hosp_8) ~ cr_cys_7, final_master) %>%
  ggcuminc() +
  add_confidence_interval() +
  add_risktable()+
   ggtitle("Cumulative Incidence of cmp_time_hosp_8 by cr_cys_7 Group")

```

#9
```{r}

cuminc(Surv(cmp_time_hosp_9, cmp_status_hosp_9) ~ cr_cys_7, final_master) %>%
  ggcuminc() +
  add_confidence_interval() +
  add_risktable()+
   ggtitle("Cumulative Incidence of cmp_time_hosp_9 by cr_cys_7 Group")

```

#10
```{r}
cuminc(Surv(cmp_time_hosp_10, cmp_status_hosp_10) ~ cr_cys_7, final_master) %>%
  ggcuminc() +
  add_confidence_interval() +
  add_risktable()+
   ggtitle("Cumulative Incidence of cmp_time_hosp_10 by cr_cys_7 Group")


```

#11
```{r}

cuminc(Surv(cmp_time_hosp_11, cmp_status_hosp_11) ~ cr_cys_7, final_master) %>%
  ggcuminc() +
  add_confidence_interval() +
  add_risktable()+
   ggtitle("Cumulative Incidence of cmp_time_hosp_11 by cr_cys_7 Group")

```
