---
title: "Cystatin C/creatinine"
author: "jiaxuan lyu"
date: "2024-11"
output:
  html_document:
    theme: lumen  #lumen,cerulean,journal,flatly,readable,spacelab
    toc: true
    toc_float: true
    toc_depth: 4
    code_folding: hide
  pdf_document:
    toc: true
    toc_depth: '4'
editor_options:
  markdown:
    wrap: 72

---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
rm(list = ls())
library(readxl)
library(openxlsx)
library(dplyr)
library(tidyverse)
library(tableone)
library(writexl)
library(gtsummary)
library(survival)
library(ggplot2)
library(ggpubr)
library(splines)
library(lattice)
library(mice)
library(DescTools)
library(survminer)
library(finalfit)
library(tidycmprsk)
library(sqldf)
library(ggsurvfit)
```


#establising the dataset
##merge several datasets
```{r}
df<- read.xlsx("/Users/jiaxuanlyu/Partners HealthCare Dropbox/Jiaxuan Lyu/Thoracic Oncology Spreadsheets/Jiaxuan’s file/dataset of 441 pts/final_data_updated_1203.xlsx")

cystatin <-read.xlsx("/Users/jiaxuanlyu/Partners HealthCare Dropbox/Jiaxuan Lyu/Thoracic Oncology Spreadsheets/Jiaxuan’s file/dataset of 441 pts/CystatinCInPatientsO-SiYuanScienceMeeting_DATA_LABELS_2024-1203_updated_hos_revised_0519.xlsx")
outcomes <- read.xlsx("/Users/jiaxuanlyu/Partners HealthCare Dropbox/Jiaxuan Lyu/Thoracic Oncology Spreadsheets/Jiaxuan’s file/dataset of 441 pts/Outcome_updated_platinum_ae_051925.xlsx")
ecog <- read.xlsx("/Users/jiaxuanlyu/Partners HealthCare Dropbox/Jiaxuan Lyu/Thoracic Oncology Spreadsheets/Jiaxuan’s file/dataset of 441 pts/CysC Manuscript ECOG.xlsx")
drug <- read.xlsx("/Users/jiaxuanlyu/Partners HealthCare Dropbox/Jiaxuan Lyu/Thoracic Oncology Spreadsheets/Jiaxuan’s file/dataset of 441 pts/Drugs.xlsx")


selected_cystatin <- cystatin%>%
  dplyr::select(-"Date.of.Birth")
final <- df%>%
  left_join(selected_cystatin, by="EMPI")
head(final)
names(final)

library(dplyr)
final <- final %>%
  dplyr::rename(cancer_type = "Lung.Breast.Upper.GI/esophagus/gastric.Lower.GI/colon/rectum.Genitourinary/RCC/bladder/urethral.(TCC).Mesothelioma.Gyn/ovarian/uterus/cervix.HEENT/Laryngeal/tonsils/head.and.neck.Other",
    height = "Height.(cm)",
    weight = "Weight.(kg)",
    cancer_stage = "Local/neoadjuvant/limited/stage.I/stage.II.Advanced/metastatic/stage.III/.stage.IV",
         platin = "Platin.Group.(carboplatin.vs.cisplatin)" ,
         treatment_regimen = "Treatment.Regimen",
         platin_dose = "Cisplatin/Carboplatin.Dose.Administered"  ,
         baseline_cre = "Baseline.Creatinine.Value",
         baseline_cystatin_c = "Baseline.Cystatin.C.Value",
         patient_status = "Patient.Status",
         dose_AUC = "IF.cisplatin.add.dose.mg/m^2.(number.only).IF.carboplatin.add.AUC.(number.only)",
    detailed_cancer_type = "Cancer.Type.-.answer.only.if.you.chose.'Other'.on.previous.question",
    hosp_90 = "Was.the.patient.hospitalized.within.90.days?",
   ed_wo_hos90 ="Was.the.patient.seen.in.the.ER.and.discharged.without.hospitalization.within.90.days?",
   hosp_90_date = "Date.of.FIRST.Hospitalization"   
    )

final <- final%>%
  mutate(hosp_90 = case_when(
    hosp_90 == "yes" ~ 1,
    hosp_90 == "no" ~ 0,
    TRUE ~ NA_real_  # 
  )) %>%
  mutate(hosp_90 = as.factor(hosp_90))  
  
  
final <- final%>%
  left_join(outcomes, by="record_id")


final <- final %>%
  left_join(
    ecog %>% select(EMPI, ecog_values),
    by = "EMPI"
  )

final <- final%>%select(-c(Pemetrexed,Gemcitabine,Bevacizumab,Atezolizumab,Pembrolizumab,Durvalumab,Paclitaxel))%>%
  left_join(
    drug%>%select(EMPI,Bevacizumab,Paclitaxel,Pemetrexed,Durvalumab,Doxorubicin,Pembrolizumab,Etoposide,Gemcitabine,Atezolizumab,Pertuzumab,Trastuzumab,Docetaxel,Fluorouracil,Methotrexate,Vinblastine,Administered_alone),
     by = "EMPI"
  )


final$hosp_90_factor <- as.factor(final$hosp_90 )


##make sure we re-catogoried the cancer type as  1: thoracic 2: breast 3:GI 4:GU 5:GYN 6:HEENT 7:others

final <- final %>%
  mutate(cancer_type = case_when(
    detailed_cancer_type %in% c("Cholangiocarcinoma", "Gallbladder adenocarcinoma", "Gallbladder cancer") ~ 10,
    TRUE ~ cancer_type
  ))


final <- final%>%
  mutate(male = ifelse (Sex=="Male",1,0))
final <- final%>%
  mutate(sex = ifelse (Sex=="Male",1,0))
```

## make sure the HIV diagnosis, thyroid disease and calculate charlson score

```{r}
library(readr)

final_date <- final %>% 
  dplyr::select(EMPI,Baseline_sample_Date,Age)
final_date$Baseline_sample_Date <- as.Date(final_date$Baseline_sample_Date, origin = "1899-12-30")

#dia
dia <- read.table("/Users/jiaxuanlyu/Desktop/Cystatin C/RPDR/mes98_101324125713455528_Dia.txt", sep = '|',
                  fill = TRUE,
                  quote = "",
                  header = T)

dia$Date <- as.Date(dia$Date,"%m/%d/%Y")


med <- read.table("/Users/jiaxuanlyu/Desktop/Cystatin C/RPDR/mes98_101324125713455528_Med.txt",
                  sep = '|',
                  fill = TRUE,
                  quote = "",
                  header = T) %>% select(EMPI,Medication_Date,Medication)
med$Medication_Date <- as.Date(med$Medication_Date, "%m/%d/%Y")


final_list <- final %>% select(EMPI,Baseline.Sample.Date)
final_list$Baseline.Sample.Date <- as.Date(final_list$Baseline.Sample.Date)

final_med<- final_list %>% merge(med,by="EMPI",all.y = T)
final_dia<- final_list %>% merge(dia,by="EMPI",all.y = T)



################## names
dia_list_name <- function(data, listed_names, index_date, excluded_names = NULL, med_data = NULL, med_names = NULL) {
  # 
  if (!is.null(excluded_names)) {
    excluded_pattern <- paste(
      gsub("([][()])", "\\\\\\1", excluded_names),  # 
      collapse = "|"
    )
  }
  
  if (is.null(excluded_names)) {
    dia_result <- data %>%  
      filter(Date <= {{index_date}}) %>% 
      filter(grepl(paste(listed_names, collapse = "|"), Diagnosis_Name, ignore.case = TRUE)) %>% 
      distinct(EMPI)
  } else {
    dia_result <- data %>%  
      filter(Date <= {{index_date}}) %>% 
      filter(
        grepl(paste(listed_names, collapse = "|"), Diagnosis_Name, ignore.case = TRUE),
        !grepl(excluded_pattern, Diagnosis_Name, ignore.case = TRUE)  # 
      ) %>% 
      distinct(EMPI)
  }
  
  if (!is.null(med_data)) {
    med_result <- med_data %>%  
      filter(Medication_Date <= {{index_date}}) %>% 
      filter(grepl(paste(med_names, collapse = "|"), Medication, ignore.case = TRUE)) %>% 
      distinct(EMPI)
  } else {
    med_result <- NULL
  }
  
  final_result <- rbind(dia_result, med_result) %>% 
    distinct(EMPI)
  
  return(final_result)
}

### 
no_hiv <- c(
  "1 - Hives-Oncall",
  "Contact with and (suspected) exposure to human immunodeficiency virus [hiv]",
  "Encounter for screening for human immunodeficiency virus [hiv]",
  "counseling",
  "Inconclusive laboratory evidence of human immunodeficiency virus [hiv]",
  "Infectious And Parasitic Diseases Including Hiv W O.R. Procedure (APR v30)",
  "Family history of human immunodeficiency virus [hiv] disease",
  "HIV exposure-Oncall"
)


hiv <- c("hiv","human immunodeficiency virus")

hiv_med_list <- c("abacavir", "ziagen", "emtricitabine", "emtriva", "lamivudine",  "tenofovir", "viread",
                  "zidovudine", "retrovir", "doravirine", "pifeltro", "efavirenz", "sustiva", "etravirine",
                  "intelence", "nevirapine", "viramune", "rilpivirine", "edurant", "atazanavir", "reyataz",
                  "darunavir", "prezista", "fosamprenavir", "lexiva", "ritonavir", "norvir", "saquinavir",
                  "invirase", "tipranavir", "aptivus", "enfuvirtide", "fuzeon", "maraviroc", "selzentry",
                  "cabotegravir", "vocabria", "dolutegravir", "tivicay", "raltegravir", "isentress", "fostemsavir",
                  "rukobia", "ibalizumab-uiyk", "trogarzo", "tybost", "epzicom", "triumeq", "trizivir",
                  "evotaz", "biktarvy", "bictegravir", "alafenamide", "cabenuva", "prezcobix", "symtuza", "dovato",
                  "juluca", "delstrigo", "atripla", "symfi", "genvoya", "stribild", "odefsey", "complera", "descovy",
                  "truvada", "cimduo", "combivir", "kaletra", "lopinavir", "elvitegravir", "disoproxil", "vitekta",
                  "didanosine", "stavudine", "videx", "zerit", "delavirdine", "rescriptor", "indinavir",
                  "crixivan", "nelfinavir", "viracept", "fortovase")

###I excluded "cobicistat", vemlidy,epivir

hiv_1 <- dia_list_name(final_dia,listed_names = hiv, excluded_names=no_hiv,med_data= final_med,med_names= hiv_med_list,index_date = Baseline.Sample.Date)

##which is consist with our primary data

## check these patients' diagnosis

## then i found the reason why the HIV prevalence is so high, some patients diagnosised with"heptitis" but with medication of anti varius , which should be excluded.

library(dplyr)
hiv_patients_1 <- hiv_1 %>%
  left_join(dia, by = "EMPI")%>%
  left_join(med,by = "EMPI")%>%
  filter(
    # including HIV dignosis
    str_detect(Diagnosis_Name, regex("hiv|human immunodeficiency virus", ignore_case = TRUE)),
    #exclude hepatitis B or hepatitis C
    !str_detect(Diagnosis_Name, regex("hepatitis B|hepatitis C", ignore_case = TRUE))
  )
hiv_patients_1 <- hiv_patients_1 %>%
  distinct(EMPI, .keep_all = TRUE)


final$hiv_new <- ifelse(final$EMPI %in% hiv_patients_1$EMPI, 1, 0)



thyroid <- c ("hypothyroidism","hyperthyroidism","thyroiditis")
thyroid_med_list <- c ("Methimazole","Tapazole","Propylthiouracil","Potassium Iodide","Radioactive Iodine ","levothyroxine","Euthyrox", "Synthroid", "Eltroxin","Desiccated Thyroid Extract","Armour Thyroid")

thyroid_final <- dia_list_name(final_dia,listed_names = thyroid,med_data= final_med,med_names= thyroid_med_list,index_date = Baseline.Sample.Date)


library(dplyr)

final$thyroid <- ifelse(final$EMPI %in% thyroid_final$EMPI, 1, 0)



##charlson complex index

#dems
dems <- read.table("/Users/jiaxuanlyu/Partners HealthCare Dropbox/Jiaxuan Lyu/Thoracic Oncology Spreadsheets/RPDR/mes98_101324125713455528_Dem.txt", sep = '|',
                   fill = TRUE,
                   quote = "",
                   header = T)

dems$Date_Of_Death


lab <- read.table("/Users/jiaxuanlyu/Partners HealthCare Dropbox/Jiaxuan Lyu/Thoracic Oncology Spreadsheets/RPDR/mes98_101324125713455528_Lab.txt", sep = '|',
                  fill = TRUE,
                  quote = "",
                  header = T)%>%
  dplyr::select(EMPI,Seq_Date_Time,Result,Group_Id,Test_Description)  

lab$Seq_Date_Time <- as.Date(lab$Seq_Date_Time, "%m/%d/%Y")


last_cre <- lab  %>% 
  filter(Group_Id =="CRE") %>% 
  filter(grepl("^[><]?\\d+\\.?\\d* ?$",Result)) %>% 
  mutate(Result=as.numeric(parse_number(Result))) %>% 
  filter(!is.na(Result)) %>% 
  arrange(EMPI,desc(Seq_Date_Time)) %>% distinct(EMPI,.keep_all = T)



library(comorbidity)

### Charlson comorbidity index
ici_diag <-  dia %>% subset(select = c(EMPI, Diagnosis_Name, Date, Code, Code_Type))
ici_diag <- ici_diag %>% merge(final_date,by="EMPI",all.y = T)
ici_diag$Date <- as.Date(ici_diag$Date, "%m/%d/%Y")
ici_diag_pre <- subset(ici_diag, Date < Baseline_sample_Date)

leukemia <- ici_diag_pre[grep("leukemia", ici_diag_pre$Diagnosis_Name, ignore.case = TRUE), ]
leukemia <- leukemia[!grepl("lymphoma", leukemia$Diagnosis_Name, ignore.case = TRUE),]
leukemia = as.data.frame(table(leukemia$EMPI))
names(leukemia)[names(leukemia) == "Var1"] <- "EMPI"
names(leukemia)[names(leukemia) == "Freq"] <- "leukemia"
leukemia$leukemia[leukemia$leukemia >0] =1

lymphoma <- ici_diag_pre[grep("lymphoma", ici_diag_pre$Diagnosis_Name, ignore.case = TRUE), ]
lymphoma <- lymphoma[!grepl("leukemia", lymphoma$Diagnosis_Name, ignore.case = TRUE),]
lymphoma = as.data.frame(table(lymphoma$EMPI))
names(lymphoma)[names(lymphoma) == "Var1"] <- "EMPI"
names(lymphoma)[names(lymphoma) == "Freq"] <- "lymphoma"
lymphoma$lymphoma[lymphoma$lymphoma >0] =1

leuk_lymph = merge(leukemia, lymphoma, by = "EMPI", all = T)

diag_icd9 <- subset(ici_diag_pre, Code_Type == "ICD9")
diag_icd10 <- subset(ici_diag_pre, Code_Type == "ICD10")

diag_icd9 <- subset(diag_icd9, select = c("EMPI", "Code"))
diag_icd10 <- subset(diag_icd10, select = c("EMPI", "Code"))

diag_icd9 <- diag_icd9[!(diag_icd9$Code == ""),]
diag_icd10 <- diag_icd10[!(diag_icd10$Code == ""),]

charlson9 <- comorbidity(x = diag_icd9, id = "EMPI", code = "Code", map = "charlson_icd9_quan", assign0 = FALSE)
charlson10 <- comorbidity(x = diag_icd10, id = "EMPI", code = "Code", map = "charlson_icd10_quan", assign0 = FALSE)

charlson = merge(charlson9, charlson10, by = "EMPI", all = T)
charlson[is.na(charlson)] = 0


charlson$ami = pmax(charlson$mi.x, charlson$mi.y)
charlson$chf = pmax(charlson$chf.x, charlson$chf.y)
charlson$pvd = pmax(charlson$pvd.x, charlson$pvd.y)
charlson$cevd = pmax(charlson$cevd.x, charlson$cevd.y)
charlson$dementia = pmax(charlson$dementia.x, charlson$dementia.y)
charlson$copd = pmax(charlson$cpd.x, charlson$cpd.y)
charlson$rheumd = pmax(charlson$rheumd.x, charlson$rheumd.y)
charlson$pud = pmax(charlson$pud.x, charlson$pud.y)
charlson$mld = pmax(charlson$mld.x, charlson$mld.y)
charlson$diab = pmax(charlson$diab.x, charlson$diab.y)
charlson$diabwc = pmax(charlson$diabwc.x, charlson$diabwc.y)
charlson$hp = pmax(charlson$hp.x, charlson$hp.y)
charlson$rend = pmax(charlson$rend.x, charlson$rend.y)
charlson$canc = pmax(charlson$canc.x, charlson$canc.y)
charlson$msld = pmax(charlson$msld.x, charlson$msld.y)
charlson$metacanc = pmax(charlson$metacanc.x, charlson$metacanc.y)
charlson$aids = pmax(charlson$aids.x, charlson$aids.y)
charlson = charlson %>% subset(select = c(EMPI, ami, chf, pvd, cevd, dementia, copd, rheumd, pud, mld,
                                          diab, diabwc, hp, rend, canc, msld, metacanc, aids))
charlson$canc = 1
charlson = merge(charlson, leuk_lymph, by = "EMPI", all = T)
charlson[is.na(charlson)] = 0

ages = final_date %>% subset(select = c(EMPI, Age))

charlson = merge(charlson, ages, by.x = 1, by.y = 1)

charlson$score = charlson$ami + charlson$chf + charlson$pvd + charlson$cevd +
  charlson$dementia + charlson$copd + charlson$rheumd + charlson$pud +
  ifelse(charlson$mld == 1 & charlson$msld == 0, 1, 0) + ifelse(charlson$msld ==1, 3, 0) +
  charlson$diab + charlson$diabwc + charlson$hp*2 + charlson$rend*2 + charlson$canc*2 +
  charlson$metacanc*4 + charlson$aids*6 + charlson$leukemia*2 + charlson$lymphoma*2 +
  ifelse(charlson$Age >= 50 & charlson$Age <60, 1, 0) +
  ifelse(charlson$Age >= 60 & charlson$Age <70, 2, 0) +
  ifelse(charlson$Age >= 70 & charlson$Age <80, 3, 0) +
  ifelse(charlson$Age >= 80, 4, 0)

charlson_sc = charlson %>% subset(select = c(EMPI, score))
charlson_sc$cci = ifelse(charlson_sc$score<3, "mild", ifelse(charlson_sc$score >= 3 & charlson_sc$score <5, "moderate", "severe"))

```

##pre_HGB_45days is missing
```{r}
final_lab <- final %>% merge(lab,by="EMPI",all.y = T)

#lab result before index_date 
pre_lab <- function(data, month, time, index_date, Group_ID,Group_ID_name) {
  index_date <- enquo(index_date)
  if (month) {
    time_value <- time * 30
  } else {
    time_value <- time
  }
  
  
  lab_name <- paste0("pre_", Group_ID_name, "_", time_value, "days")
  lab_date_name <- paste0("pre_", Group_ID_name, "_", time_value, "days_date")
  
  result <- data %>% 
    filter(Group_Id %in% Group_ID) %>% 
    filter(grepl("^[><]?\\d+\\.?\\d* ?$",Result)) %>% 
    mutate(Result=as.numeric(parse_number(Result))) %>% 
    filter(!is.na(Result)) %>% 
    filter(Baseline_sample_Date >= (!!index_date) - time_value, Baseline_sample_Date<= !!index_date) %>% 
    arrange(EMPI, desc(Baseline_sample_Date)) %>% 
    distinct(EMPI, .keep_all = TRUE) %>% 
    rename(!!lab_name := Result,
           !!lab_date_name := Baseline_sample_Date) %>% 
    select(EMPI,
           !!lab_name, !!lab_date_name)
  
  return(result)
}
###### outcome Lab 

# Convert to data.table
library(data.table)
setDT(final_lab)

pre_HGB_45days <- pre_lab(final_lab, month = F, time = 45, 
                         index_date = Baseline_sample_Date, 
                         Group_ID = "HGB", Group_ID_name = "HGB")

```


##merge the cci score,and pre_HGB_45days with final dataset
```{r}

duplicates <- charlson_sc %>%
  group_by(EMPI) %>%
  filter(n() > 1) %>%
  ungroup() ## check there is no duplicated EMPI

final <- final%>%
  left_join(charlson_sc, by = "EMPI")


final <- final%>%
  left_join(pre_HGB_45days, by = "EMPI")

final <- final%>%
  mutate(mortality_90 = ifelse(death_90==2,1,0))

write_xlsx(final, path = "/Users/jiaxuanlyu/Partners HealthCare Dropbox/Jiaxuan Lyu/Thoracic Oncology Spreadsheets/Jiaxuan’s file/dataset of 441 pts/cystatin_c_project_051925.xlsx")
```


# you can use the final dataset
```{r}
final<- read.xlsx("/Users/jiaxuanlyu/Partners HealthCare Dropbox/Jiaxuan Lyu/Thoracic Oncology Spreadsheets/Jiaxuan’s file/dataset of 441 pts/cystatin_c_project_051925.xlsx")


final$hosp_90
  


#cancer_retype: don't need to do it again;already done
final <- final%>%
  mutate(cancer_retype = case_when(
    cancer_type == 1 ~ 1,
    cancer_type == 2 ~ 2,
    cancer_type == 3 ~ 3,
    cancer_type == 4 ~ 3,
    cancer_type == 10 ~ 3,
    cancer_type == 9 & str_detect(tolower(detailed_cancer_type), "pancreatic") ~ 3, 
    cancer_type == 5 ~ 4,
    cancer_type == 7 ~ 5,
     cancer_type == 6 ~ 7,
     cancer_type == 8 ~ 6,
    cancer_type == 9 & !str_detect(tolower(detailed_cancer_type), "pancreatic") ~ 7,
      TRUE ~ NA_integer_  # 
  ))


```


#create variables

```{r}
##ICI shouldn't contain Bevacizumab, it belongs to VEGF
final <- final%>%
  mutate(ici = ifelse(Atezolizumab == 1 | Pembrolizumab == 1 | Durvalumab == 1 , 1 , 0))

##height
final <- final%>%
  mutate(height_inch = height/2.54)

##BSA
final=final%>%
  mutate(BSA=0.007184 * (weight ^ 0.425) * ((height) ^ 0.725))

##recalculate cockcroft eGFR using real weight

Cockcroft <- function(age,weight,male,cre){
  if(male==0){
  value=(140-age)*weight*0.85/(72*cre)}
  else{
  value=(140-age)*weight/(72*cre) 
  }
}

final$egfr_cock <- mapply(Cockcroft,final$Age,final$weight,final$male,final$baseline_cre) 


## reclculated  ckd-epi egfr 

ckd_epi_gfr <- function(cre, male, age) {
  k <- ifelse(male == 1, 0.9, 0.7)
  a <- ifelse(male == 1, -0.302, -0.241)
  m <- ifelse(male == 1, 1, 1.012)
  gfr <- 142 * min(c(cre/k,1))^a * max(c(cre/k,1))^-1.2 * 0.9938^age * m
  return(gfr)
}
final$egfr_cre<-mapply(ckd_epi_gfr,final$baseline_cre,final$male,final$Age)

final$egfr_cre_unindexed <- final$egfr_cre * final$BSA/1.73


## reclculated  egfr based on creatinine and cystatin function without race

library(nephro)
final$egfr_cystatin_cre = CKDEpi_RF.creat.cys(final$baseline_cre,final$baseline_cystatin_c,final$sex,final$Age)

## reclculated  egfr based on just cystatin function without race

final$egfr_cystatin = CKDEpi.cys(final$baseline_cystatin_c,final$sex,final$Age)

final$egfr_cystatin_unindexed <-final$egfr_cystatin * final$BSA/1.73


##generate unindexed combined egfr
final <- final%>%
  mutate(egfr_cystatin_cre_unindexed = egfr_cystatin_cre * BSA/1.73)

## age categories
final <- final%>%
  mutate(age_cat = case_when(
    Age <= 65 ~ 1,
    Age> 65 & Age <= 80 ~2,
    Age> 80  ~3
  ))

table(final$age_cat)

## BMI categories
library(dplyr)

final <- final %>%
  mutate(bmi = weight / ((height/100) ^ 2))

final <- final %>%
  mutate(bmi_cat = case_when(bmi< 18.5 ~ 1,
                             bmi >= 18.5 & bmi < 25 ~ 2,
                             bmi >= 25 & bmi < 30 ~ 3,
                             bmi >= 30 ~ 4,
                             TRUE ~ NA_real_
                             ))

table(final$bmi_cat)


##platinum categories

final <- final%>%
  mutate(carbo = ifelse(platin == "Carboplatin",1,0))%>%
   mutate(carbo_dose = case_when(
     carbo==1 ~platin_dose,
     carbo==0~NA
   ))%>%
  mutate(cis = ifelse(platin == "Cisplatin",1,0))%>%
   mutate(cis_dose = case_when(
     cis==1 ~platin_dose,
     cis==0~NA
   ))%>%
  mutate(carbo_AUC =case_when(
     carbo==1 ~dose_AUC,
     carbo==0~NA
   ))%>% 
 mutate(cis_recommend =case_when(
     cis==1 ~dose_AUC,
     cis==0~NA
   ))%>%
  mutate(cis_AUC = case_when(
    cis==1 ~ dose_AUC,
    cis==0~NA
  ))


final <- final%>%
  mutate(cis_group = case_when(
    cis_recommend < 40 ~1,
    cis_recommend>=40 & cis_recommend<60 ~2,
    cis_recommend >=60 ~ 3,
    TRUE ~ NA
  ))



#generate new variable dose: 0 = low dose; 1= high dose


final<- final %>%
  mutate(dose_1 = case_when(
    carbo_AUC >= 5 | cis_AUC >=75 ~ 1,
    carbo_AUC < 5 | cis_AUC < 75 ~ 0,
    TRUE ~ NA_real_
  ))%>%
  mutate (dose_1 = as.factor(dose_1))
  
table(final$dose_1)
##generate carbo_auc_cat
final <- final%>%
  mutate(carbo_AUC_cat = case_when(
    carbo_AUC<= 4 ~ 1,
    carbo_AUC>= 5 ~2,
    TRUE ~  0
  ))

table(final$carbo_AUC_cat)


## generate cis_dose_cat


final <- final%>%
  mutate(cis_dose_cat = case_when(
    cis_AUC< 75  ~ 1,
    cis_AUC >= 75  ~ 2,
    TRUE ~ 0
  ))

table(final$cis_dose_cat)

##generate outcomes as Anemia_g2_90days,Throm_g2_90days,Neutro_g2_90days,AKI_g2_90days,and grade3 AEs

final <- final%>%
  mutate(Anemia_g2_90days = ifelse(!is.na(post_Anemia_2_cutpoint_90days),1,0))%>%
  mutate(Anemia_g3_90days = ifelse(!is.na(post_Anemia_3_cutpoint_90days),1,0))%>%
  mutate(Throm_g2_90days = ifelse(!is.na(post_Throm_2_cutpoint_90days),1,0))%>%
  mutate(Throm_g3_90days = ifelse(!is.na(post_Throm_3_cutpoint_90days),1,0))%>%
  mutate(Neutro_g2_90days = ifelse(!is.na(post_Neutro_2_cutpoint_90days),1,0))%>%
  mutate(Neutro_g3_90days=ifelse(!is.na(post_Neutro_3_cutpoint_90days),1,0))%>%
  mutate(AKI_g2_90days = ifelse(!is.na(post_AKI_2_cutpoint_90days),1,0))%>%
  mutate(AKI_g3_90days = ifelse(!is.na(post_AKI_3_cutpoint_90days),1,0))


## generate time to AEs
final <- final%>%
  mutate(time_to_anemia_2 = post_Anemia_2_cutpoint_90days_date - Baseline.Sample.Date)%>%
  mutate(time_to_anemia_3 = post_Anemia_3_cutpoint_90days_date - Baseline.Sample.Date)%>%
  mutate(time_to_throm_2 = post_Throm_2_cutpoint_90days_date - Baseline.Sample.Date)%>%
  mutate(time_to_throm_3 = post_Throm_3_cutpoint_90days_date - Baseline.Sample.Date)%>%
  mutate(time_to_neutro_2 = post_Neutro_2_cutpoint_90days_date - Baseline.Sample.Date)%>%
  mutate(time_to_neutro_3 = post_Neutro_3_cutpoint_90days_date - Baseline.Sample.Date)%>%
  mutate(time_to_aki_2 = post_AKI_2_cutpoint_90days_date - Baseline.Sample.Date)%>%
  mutate(time_to_aki_3 = post_AKI_3_cutpoint_90days_date - Baseline.Sample.Date)


final <- final %>%
  mutate(across(
    c(time_to_anemia_2, time_to_anemia_3,
      time_to_throm_2, time_to_throm_3,
      time_to_neutro_2, time_to_neutro_3,
      time_to_aki_2, time_to_aki_3),
    ~ ifelse(is.na(.), 0, .)
  ))


##filter cystatin C isn't NA(3 patient), platinum isn't NA(1 patient)
final <- final %>%
  mutate(baseline_cystatin_c = as.numeric(baseline_cystatin_c)) %>%
  filter(!is.na(baseline_cystatin_c)) %>%
  filter(!is.na(platin))



library(dplyr)

hosp <-  final %>%
  dplyr::select(record_id,matches("hos|ed|extra|egfr|exposure"))
head(hosp)

getwd()



## we have other exposures
final<- final%>%
  mutate(exposure_epi_30 = ifelse(egfr_cystatin < 0.7*egfr_cre,1,0))


final<- final%>%
  mutate(exposure_cg_30 = ifelse(egfr_cystatin_cre_unindexed < 0.7*egfr_cock,1,0))


final<- final%>%
  mutate(exposure_cg_15 = ifelse(egfr_cystatin_cre_unindexed < 0.85*egfr_cock,1,0))

##generate new exposure as cr/cys 
final$cr_cys <-final$baseline_cre/final$baseline_cystatin_c

  
final<- final%>%
  mutate(cr_cys_cat = case_when(
    cr_cys < 0.5 ~1,
    cr_cys >=0.5 & cr_cys <0.7 ~ 2,
    cr_cys >=0.7 & cr_cys <0.9 ~ 3,
    cr_cys >= 0.9  ~ 4
  )
           )

final$cr_cys_cat <- factor(final$cr_cys_cat, 
                           levels = c("1", "2", "3", "4"), 
                           labels = c("< 0.5", "0.5-0.7", "0.7-0.9", "≥ 0.9")) 


table(final$cr_cys_cat)

##generate new exposure as cr/cys < 0.7
final$cr_cys_7 <-ifelse(final$cr_cys < 0.7, 1, 0) 
table(final$cr_cys_7)


##rename the side_effect_hos to platinum_related_hosp


##lumping all grade 2 AEs as grade_2_aes; the same with grade_3_aes
final <- final%>%
  mutate( grade_2_aes = case_when(
    Anemia_g2_90days == 1 | Throm_g2_90days == 1 | AKI_g2_90days == 1 ~ 1,
    TRUE ~ 0
  ) ) %>%
  
mutate( grade_3_aes = case_when(
    Anemia_g3_90days == 1 | Throm_g3_90days == 1 | AKI_g3_90days == 1 ~ 1,
    TRUE ~ 0
  ) ) 

table(final$cr_cys_7,final$grade_2_aes)

table(final$cr_cys_7,final$grade_3_aes)

```



## prepareing exposures

```{r}
# exposure 1: cr/cys > 0.7             cr_cys_7
# exposure 2: 30% eGFR discrepancy = eGFR_cystatin   vs.  eGFR_cr             exposure_epi_30
# expisure 3: 15% eGFR discrepancy = eGFR_cock vs. eGFR_cys_cr_unindexed      exposure_cg_15


table(final$exposure_cg_15)

#sensitivity analysis
# eGFR discordance, defined by the ratio of eGFR-CR-CYS to CG-CrCl 

final <- final%>%
  mutate(egfr_combined_cg_ratio = egfr_cystatin_cre_unindexed / egfr_cock)
```

##generate time to event variables for lumped grade_2_aes and grade_3_aes
```{r}
###generate new variables: death within 90days,death within 1y
final$follow_up_time<-final$last_follow_up_date-final$Baseline_sample_Date
## we already have factor of death_90(0,2)

 ###mutate date format
final <- final %>%
  mutate(across(
    .cols = c(last_follow_up_date, Baseline_sample_Date,  
              post_Anemia_2_cutpoint_90days_date, post_Anemia_3_cutpoint_90days_date, 
              post_Neutro_2_cutpoint_90days_date, post_Neutro_3_cutpoint_90days_date, 
              post_Throm_2_cutpoint_90days_date, post_Throm_3_cutpoint_90days_date, 
              post_AKI_2_cutpoint_90days_date,post_AKI_3_cutpoint_90days_date),
    .fns = ~as.Date(., format='%m/%d/%Y')
  ))

final <- final %>%
  mutate(time_to_anemia_2 =post_Anemia_2_cutpoint_90days_date - Baseline_sample_Date )%>%
  mutate(time_to_anemia_3 =post_Anemia_3_cutpoint_90days_date - Baseline_sample_Date )%>%
  mutate(time_to_throm_2 =post_Throm_2_cutpoint_90days_date - Baseline_sample_Date )%>%
  mutate(time_to_throm_3 =post_Throm_3_cutpoint_90days_date - Baseline_sample_Date )%>%
 mutate(time_to_aki_2 =post_AKI_2_cutpoint_90days_date - Baseline_sample_Date )%>%
  mutate(time_to_aki_3 =post_AKI_3_cutpoint_90days_date - Baseline_sample_Date )



###generate time 
##for grade_2_aes

final <- final %>% 
  mutate(time_to_last = as.numeric(last_follow_up_date - Baseline_sample_Date)) %>%
  mutate(time_to_last = ifelse(time_to_last > 90, 90, time_to_last))%>%
  mutate(time_to_anemia_2 = ifelse(is.na(time_to_anemia_2),90, time_to_anemia_2))%>%
   mutate(time_to_anemia_3 = ifelse(is.na(time_to_anemia_3),90, time_to_anemia_3))%>%
   mutate(time_to_throm_2 = ifelse(is.na(time_to_throm_2),90, time_to_throm_2))%>%
   mutate(time_to_throm_3 = ifelse(is.na(time_to_throm_3),90, time_to_throm_3))%>%
   mutate(time_to_aki_2 = ifelse(is.na(time_to_aki_2),90, time_to_aki_2))%>%
   mutate(time_to_aki_3 = ifelse(is.na(time_to_aki_3),90, time_to_aki_3))
  
  

final <- final %>%
  rowwise() %>%
  mutate(time_grade_2_aes = {
    times <- c(time_to_anemia_2, time_to_throm_2, time_to_aki_2)
    non_zero_times <- times[times != 0]
    if(length(non_zero_times) == 0) 90 else min(non_zero_times)
  }) %>%
  ungroup()


final$time_grade_2_aes


final <- final %>%
  rowwise() %>%
  mutate(time_grade_3_aes = {
    times <- c(time_to_anemia_3, time_to_throm_3, time_to_aki_3)
    non_zero_times <- times[times != 0]
    if(length(non_zero_times) == 0) 90 else min(non_zero_times)
  }) %>%
  ungroup()


final$time_grade_3_aes


###generate competing variables

##grade_2_aes
final = final %>%
  mutate(cmp_time_grade_2_aes = case_when(
            time_to_last <= time_grade_2_aes ~ time_to_last,
            TRUE ~ time_grade_2_aes),
         cmp_status_grade_2_aes = case_when(
            time_to_last <= time_grade_2_aes ~ death_90,
            TRUE ~ grade_2_aes))

final$cmp_status_grade_2_aes
final$cmp_time_grade_2_aes

##grade_3_aes
final = final %>%
  mutate(cmp_time_grade_3_aes = case_when(
            time_to_last <= time_grade_3_aes ~ time_to_last,
            TRUE ~ time_grade_3_aes),
         cmp_status_grade_3_aes = case_when(
            time_to_last <= time_grade_3_aes ~ death_90,
            TRUE ~ grade_3_aes))

final$cmp_status_grade_3_aes
final$cmp_time_grade_3_aes



###mutate variables type
final <- final %>%
  dplyr::mutate(across(c(cmp_status_grade_2_aes,
                  cmp_status_grade_3_aes), as.factor))
```

##CKD stages using cock equation
```{r}

final<- final%>%
  mutate(ckd_stage_cg = case_when(
    egfr_cock >= 90 ~ 1,
    egfr_cock >= 60 & egfr_cock < 90 ~ 2,
    egfr_cock >= 30 & egfr_cock < 60 ~ 3,
    egfr_cock >= 15 & egfr_cock < 30 ~ 4,
    egfr_cock < 15  ~ 5))%>%
  mutate(ckd_stage_cg = as.factor(ckd_stage_cg))

table(final$ckd_stage_cg)

```


#Table one 
## for cre/cys ratio 

```{r}
##dose_1: carbo-AUC ≥ 5 mg/mL/min, or r cisplatin  ≥ 75 mg/m2
table_one_cc_ratio <- final%>%
  dplyr::select(Age,age_cat,sex,Race,Ethnicity,cancer_stage,cancer_retype,
                platin,cis_dose,cis_dose_cat,carbo_dose, carbo_AUC, carbo_AUC_cat,dose_1,
                ici,Bevacizumab,Paclitaxel,Pemetrexed,Doxorubicin,Etoposide,Gemcitabine,Pertuzumab,Trastuzumab,Docetaxel,Fluorouracil,Methotrexate,Vinblastine,Administered_alone,
                dm,htn,cirrhosis,cad,hiv_new,ppi,ace_arb,diu,steroids,statins,nsaids,smoking,thyroid,
                score,ecog_values,bmi,bmi_cat,pre_WBC_45days,pre_HGB_45days,pre_PLT_45days,pre_ALB_45days,baseline_cystatin_c,baseline_cre,egfr_cock,egfr_cre,egfr_cystatin,egfr_cystatin_cre,egfr_cre_unindexed,egfr_cystatin_unindexed,egfr_cystatin_cre_unindexed,ckd_stage_cg,cr_cys,cr_cys_7) %>%
  tbl_summary(statistic = list(Age ~ "{mean} ({sd})"), 
              by = cr_cys_7,
            
    ) %>%
  add_overall() %>%
  add_p(
    test.args = list(
      all_categorical() ~ list(simulate.p.value = TRUE)
    )
  )
table_one_cc_ratio
```


# Figure 2 loess plot about exposure and outcomes, Outcomes: overall hospitalization,Hospitalization for platinum-associated AEs,mortality, Anemia grade 3,Thrombo grade 3,Aki 2,Aki 3
## cc_ratio = cre/cys


###loess plot about cc_decile and outcomes
```{r}
library(ggplot2)
library(dplyr)


##seperate  population as decile ( population number in 10 groups)
library(dplyr)

final <- final %>%
  mutate(cc_decile = ntile(cr_cys, 10))%>%
  mutate(cc_decile = as.factor(cc_decile))
table(final$cc_decile)

##summarize cr_cys ratio value according to cc_decile
library(dplyr)

summary_by_decile <- final %>%
  group_by(cc_decile) %>%
  summarise(
    n        = n(),                                 # sample size
    min      = min(cr_cys, na.rm = TRUE),         # minimum
    q1       = quantile(cr_cys, 0.25, na.rm = TRUE),  # Q1
    median   = median(cr_cys, na.rm = TRUE),      # median
    mean     = mean(cr_cys, na.rm = TRUE),        # mean
    q3       = quantile(cr_cys, 0.75, na.rm = TRUE),  # Q3
    max      = max(cr_cys, na.rm = TRUE),         # maxmun
    sd       = sd(cr_cys, na.rm = TRUE)           # sd
  ) %>%
  ungroup()

print(summary_by_decile)


final <- final %>%
  group_by(cc_decile) %>%
  mutate(anemia_2_rate_decile = mean(Anemia_g2_90days, na.rm = TRUE))%>%
  mutate(anemia_3_rate_decile = mean(Anemia_g3_90days, na.rm = TRUE))%>%
   mutate(throm_2_rate_decile = mean(Throm_g2_90days, na.rm = TRUE))%>%  
   mutate(throm_3_rate_decile = mean(Throm_g3_90days, na.rm = TRUE))%>%  
   mutate(neutro_2_rate_decile = mean(Neutro_g2_90days, na.rm = TRUE))%>% 
  mutate(neutro_3_rate_decile = mean(Neutro_g3_90days, na.rm = TRUE))%>% 
  mutate(aki_2_rate_decile = mean(AKI_g2_90days, na.rm = TRUE))%>% 
  mutate(aki_3_rate_decile = mean(AKI_g3_90days, na.rm = TRUE))%>%  
  mutate(hos_rate_decile = mean(hosp_90, na.rm = TRUE))%>%  
  mutate(platinum_related_hos_rate_decile = mean(platinum_related_hosp, na.rm = TRUE))%>% 
  mutate(death_rate_decile = mean(death_90, na.rm = TRUE))%>%
  ungroup()

final <- final%>%
  mutate(cc_decile = as.numeric(cc_decile))%>%
  ungroup()
```



###loess plot about cc_percentile and outcomes as 0 or 1
```{r}

library(ggplot2)
library(dplyr)

final <- final %>%
  mutate(cc_percentile = ntile(cr_cys, 100))%>%
  mutate(cc_percentile = as.factor(cc_percentile))
table(final$cc_percentile)
  
final <- final%>%
  mutate(cc_percentile = as.numeric(cc_percentile))%>%
  ungroup()

##summarize cr_cys ratio value according to cc_ventile
library(dplyr)

summary_by_percentile <- final %>%
  group_by(cc_percentile) %>%
  summarise(
    n        = n(),                                 # 
    min      = min(cr_cys, na.rm = TRUE),         # 
    q1       = quantile(cr_cys, 0.25, na.rm = TRUE),  # 
    median   = median(cr_cys, na.rm = TRUE),      # 
    mean     = mean(cr_cys, na.rm = TRUE),        # 
    q3       = quantile(cr_cys, 0.75, na.rm = TRUE),  # 
    max      = max(cr_cys, na.rm = TRUE),         # 
    sd       = sd(cr_cys, na.rm = TRUE)           # 
  ) %>%
  ungroup()

print(summary_by_percentile,n=30)
print(summary_by_percentile,n=100)
```


###combine the plots as one

```{r}

library(scales)
plot_anemia_2 <- ggplot(final, aes(x = cc_percentile, y = Anemia_g2_90days)) +
  # adding point from decile results
  geom_point(aes(x = cc_decile * 10, y = anemia_2_rate_decile),  # cc_decile ranges 0-10,tranform to 0-100
             size = 6, color = "black", shape =19) +  # 
  # smooth line（percentile result）
  geom_smooth(method = "loess", se = TRUE, span = 0.75, color = "blue", size = 2) +
  # 
  scale_x_continuous(breaks = seq(0, 100, by = 10)) +
  labs(title = "Grade ≥ 2 Anemia",
       x = "Percentile of SCR/CYS ratio",
       y = "Grade ≥ 2 Anemia") +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  theme_minimal() +
  theme(
    legend.title = element_text(),
    legend.position = "right",
    axis.title.x = element_text(size = 30),
    axis.title.y = element_text(size = 30),
    axis.text.x = element_text(size = 30),
    axis.text.y = element_text(size = 30),
    plot.title = element_text(size = 45, face = "bold")
  ) +
  # yellow background
  annotate("rect", xmin = 1, xmax = 25, ymin = -Inf, ymax = Inf,
           alpha = 0.2, fill = "yellow")

# 
plot_anemia_2
```

```{r}
# plot
plot_anemia_3 <- ggplot(final, aes(x = cc_percentile, y = Anemia_g3_90days)) +
  geom_point(aes(x = cc_decile * 10, y = anemia_3_rate_decile),  
             size = 6, color = "black", shape =19) +  
  geom_smooth(method = "loess", se = TRUE, span = 0.75, color = "blue",size = 2) +
  scale_x_continuous(breaks = seq(0, 100, by = 10)) +
  labs(title = "Grade ≥ 3 Anemia",
       x = "Percentile of SCR/CYS ratio ",
       y = "Grade ≥ 3 Anemia") +
  scale_y_continuous(labels = percent_format(accuracy = 1))+  # Y-axis 
  theme_minimal() +  ## cleantable;classic;minimal
  theme(
    legend.title =element_text() ,
    legend.position = "right",
     axis.title.x = element_text(size = 30),  # X-axis title font size
    axis.title.y = element_text(size = 30),  # Y-axis title font size
    axis.text.x = element_text(size = 30),   # X-axis text font size
    axis.text.y = element_text(size = 30),
    plot.title = element_text(size = 45, face = "bold") # Y-axis text font size
  ) +
  # adding yellow area：assume decile 1-25 is Scr/CYS < 0.7 area
  annotate("rect", xmin = 1, xmax = 25, ymin = -Inf, ymax = Inf,
           alpha = 0.2, fill = "yellow")
plot_anemia_3
```

```{r}
# plot
plot_throm_3 <- ggplot(final, aes(x = cc_percentile, y = Throm_g3_90days)) +
  geom_point(aes(x = cc_decile * 10, y = throm_3_rate_decile),  
             size = 6, color = "black", shape =19) + 
  geom_smooth(method = "loess", se = TRUE, span = 0.75, color = "blue",size = 2) +
  scale_x_continuous(breaks = seq(0, 100, by = 10)) +
  labs(title = "Grade ≥ 3 Thrombocytopenia",
       x = "Percentile of SCR/CYS ratio",
       y = "Grade ≥ 3 Thrombocytopenia") +
  scale_y_continuous(labels = percent_format(accuracy = 1))+  # Y-axis 
  theme_minimal() +  ## cleantable;classic;minimal
  theme(
    legend.title =element_text() ,
    legend.position = "right",
     axis.title.x = element_text(size = 30),  # X-axis title font size
    axis.title.y = element_text(size = 30),  # Y-axis title font size
    axis.text.x = element_text(size = 30),   # X-axis text font size
    axis.text.y = element_text(size = 30),
    plot.title = element_text(size = 45, face = "bold") # Y-axis text font size
  ) +
  # adding yellow area：assume decile 1-25 is Scr/CYS < 0.7 area
  annotate("rect", xmin = 1, xmax = 25, ymin = -Inf, ymax = Inf,
           alpha = 0.2, fill = "yellow")
plot_throm_3
```

```{r}
# plot
plot_aki_3 <- ggplot(final, aes(x = cc_percentile, y = AKI_g3_90days)) +
 geom_point(aes(x = cc_decile * 10, y = aki_3_rate_decile),  
             size = 6, color = "black", shape =19) + 
  geom_smooth(method = "loess", se = TRUE, span = 0.75, color = "blue",size = 2) +
  scale_x_continuous(breaks = seq(0, 100, by = 10)) +
  labs(title = "Grade ≥ 3 Creatinine Increased",
       x = "Percentile of SCR/CYS ratio",
       y = "Grade ≥ 3 Creatinine Increased") +
  scale_y_continuous(labels = percent_format(accuracy = 1))+  # Y-axis 
  theme_minimal() +  ## cleantable;classic;minimal
  theme(
    legend.title =element_text() ,
    legend.position = "right",
     axis.title.x = element_text(size = 30),  # X-axis title font size
    axis.title.y = element_text(size = 30),  # Y-axis title font size
    axis.text.x = element_text(size = 30),   # X-axis text font size
    axis.text.y = element_text(size = 30),
    plot.title = element_text(size = 45, face = "bold") # Y-axis text font size
  ) +
  # adding yellow area：assume decile 1-25 is Scr/CYS < 0.7 area
  annotate("rect", xmin = 1, xmax = 25, ymin = -Inf, ymax = Inf,
           alpha = 0.2, fill = "yellow")
plot_aki_3
```
```{r}
library(ggplot2)
library(dplyr)

# plot
plot_hosp <-ggplot(final, aes(x = cc_percentile, y = hosp_90)) +
  geom_point(aes(x = cc_decile * 10, y = hos_rate_decile),  
             size = 6, color = "black", shape =19) + 
  geom_smooth(method = "loess", se = TRUE, span = 0.75, color = "blue",size = 2) +
  scale_x_continuous(breaks = seq(0, 100, by = 10)) +
  labs(title = "Overall Hospitalization",
       x = "Percentile of SCR/CYS ratio",
       y = "Overall Hospitalization") +
  scale_y_continuous(labels = percent_format(accuracy = 1))+  # Y-axis 
  theme_minimal() +  ## cleantable;classic;minimal
  theme(
    legend.title =element_text() ,
    legend.position = "right",
     axis.title.x = element_text(size = 30),  # X-axis title font size
    axis.title.y = element_text(size = 30),  # Y-axis title font size
    axis.text.x = element_text(size = 30),   # X-axis text font size
    axis.text.y = element_text(size = 30),
    plot.title = element_text(size = 45, face = "bold") # Y-axis text font size
  ) +
  # adding yellow area：assume decile 1-3 is Scr/CYS < 0.7 area
  annotate("rect", xmin = 1, xmax = 25, ymin = -Inf, ymax = Inf,
           alpha = 0.2, fill = "yellow")

plot_hosp
```

```{r}
library(ggplot2)
library(dplyr)

# plot
plot_hosp_side_effect <-ggplot(final, aes(x = cc_percentile, y = platinum_related_hos)) +
  geom_point(aes(x = cc_decile * 10, y = platinum_related_hos_rate_decile),  
             size = 6, color = "black", shape =19) + 
  geom_smooth(method = "loess", se = TRUE, span = 0.75, color = "blue",size = 2) +
  scale_x_continuous(breaks = seq(0, 100, by = 10)) +
  labs(title = "Hospitalization for platinum-assosiated AEs",
       x = "Percentile of SCR/CYS ratio",
       y = "Hospitalization for platinum-assosiated AEs") +
  scale_y_continuous(labels = percent_format(accuracy = 1))+  # Y-axis 
  theme_minimal() +  ## cleantable;classic;minimal
  theme(
    legend.title =element_text() ,
    legend.position = "right",
     axis.title.x = element_text(size = 30),  # X-axis title font size
    axis.title.y = element_text(size = 30),  # Y-axis title font size
    axis.text.x = element_text(size = 30),   # X-axis text font size
    axis.text.y = element_text(size = 30),
    plot.title = element_text(size = 45, face = "bold") # Y-axis text font size
  ) +
  # adding yellow area：assume ventile 1-25 is Scr/CYS < 0.7 area
  annotate("rect", xmin = 1, xmax = 25, ymin = -Inf, ymax = Inf,
           alpha = 0.2, fill = "yellow")
plot_hosp_side_effect
```

```{r}
library(ggplot2)
library(dplyr)

# plot
plot_mortality <- ggplot(final, aes(x = cc_percentile, y = mortality_90)) +
  geom_point(aes(x = cc_decile * 10, y = death_rate_decile),  
             size = 6, color = "black", shape =19) + 
  geom_smooth(method = "loess", se = TRUE, span = 0.75, color = "blue",size = 2) +
  scale_x_continuous(breaks = seq(0, 100, by = 10)) +
  labs(title = "Mortality",
       x = "Percentile of SCR/CYS ratio",
       y = "Mortality") +
  scale_y_continuous(labels = percent_format(accuracy = 1))+  # Y-axis 
  theme_minimal() +  ## cleantable;classic;minimal
  theme(
    legend.title =element_text() ,
    legend.position = "right",
     axis.title.x = element_text(size = 30),  # X-axis title font size
    axis.title.y = element_text(size = 30),  # Y-axis title font size
    axis.text.x = element_text(size = 30),   # X-axis text font size
    axis.text.y = element_text(size = 30),
    plot.title = element_text(size = 45, face = "bold") # Y-axis text font size
  ) +
  # adding yellow area：assume percentile 1-25 is Scr/CYS < 0.7 area
  annotate("rect", xmin = 1, xmax = 25, ymin = -Inf, ymax = Inf,
           alpha = 0.2, fill = "yellow")

plot_mortality
```

```{r}

# using plot_grid to create one plot

library(cowplot)
plot_percentile_combined <- plot_grid(plot_hosp_side_effect,plot_hosp, plot_mortality,plot_anemia_3,plot_throm_3,plot_aki_3,nrow = 2)

print (plot_percentile_combined) #save as 4000 * 2000
```


# sensitivity analysis: supplemental figure of loess plot
# The association between eGFR discordance and outcomes, defined by the ratio of actual body adjusted eGFR-CR-CYS to CG-CrCl 
#Outcomes: overall hospitalization, hospitalization for platinum-associated AEs, mortality and grade 3 AEs including anemia, thrombocytopenia, creatinine increased
## egfr_combined_cg_ratio = actual body adjusted eGFR-CR-CYS  / CG-CrCl

###loess plot about egfr_combined_cg_ratio _decile and outcomes


```{r}
library(ggplot2)
library(dplyr)

##seperate  population as decile ( population number in 10 groups)
library(dplyr)

final <- final %>%
  mutate(egfr_combined_cg_ratio_decile = ntile(egfr_combined_cg_ratio, 10))%>%
  mutate(egfr_combined_cg_ratio_decile= as.factor(egfr_combined_cg_ratio_decile))
table(final$egfr_combined_cg_ratio_decile)

##summarize cr_cys ratio value according to cc_decile
library(dplyr)

summary_by_decile <- final %>%
  group_by(egfr_combined_cg_ratio_decile) %>%
  summarise(
    n        = n(),                                 # sample size
    min      = min(egfr_combined_cg_ratio, na.rm = TRUE),         # minimum
    q1       = quantile(egfr_combined_cg_ratio, 0.25, na.rm = TRUE),  # Q1
    median   = median(egfr_combined_cg_ratio, na.rm = TRUE),      # median
    mean     = mean(egfr_combined_cg_ratio, na.rm = TRUE),        # mean
    q3       = quantile(egfr_combined_cg_ratio, 0.75, na.rm = TRUE),  # Q3
    max      = max(egfr_combined_cg_ratio, na.rm = TRUE),         # maxmun
    sd       = sd(egfr_combined_cg_ratio, na.rm = TRUE)           # sd
  ) %>%
  ungroup()

print(summary_by_decile)


final <- final %>%
  group_by(egfr_combined_cg_ratio_decile) %>%
  mutate(anemia_2_rate_decile_egfr = mean(Anemia_g2_90days, na.rm = TRUE))%>%
  mutate(anemia_3_rate_decile_egfr = mean(Anemia_g3_90days, na.rm = TRUE))%>%
   mutate(throm_2_rate_decile_egfr = mean(Throm_g2_90days, na.rm = TRUE))%>%  
   mutate(throm_3_rate_decile_egfr = mean(Throm_g3_90days, na.rm = TRUE))%>%  
   mutate(neutro_2_rate_decile_egfr = mean(Neutro_g2_90days, na.rm = TRUE))%>% 
  mutate(neutro_3_rate_decile_egfr = mean(Neutro_g3_90days, na.rm = TRUE))%>% 
  mutate(aki_2_rate_decile_egfr = mean(AKI_g2_90days, na.rm = TRUE))%>% 
  mutate(aki_3_rate_decile_egfr = mean(AKI_g3_90days, na.rm = TRUE))%>%  
  mutate(hos_rate_decile_egfr = mean(hosp_90, na.rm = TRUE))%>%  
  mutate(platinum_related_hos_rate_decile_egfr = mean(platinum_related_hos, na.rm = TRUE))%>% 
  mutate(death_rate_decile_egfr = mean(death_90, na.rm = TRUE))%>%
  ungroup()

final <- final%>%
  mutate(egfr_combined_cg_ratio_decile = as.numeric(egfr_combined_cg_ratio_decile))%>%
  ungroup()


```




```{r}
library(ggplot2)
library(dplyr)
final <- final%>%
  mutate(egfr_combined_cg_ratio_decile = as.numeric(egfr_combined_cg_ratio_decile))%>%
  ungroup()

###loess plot about egfr_combined_cg_ratio_percentile and outcomes as 0 or 1

library(ggplot2)
library(dplyr)

final <- final %>%
  mutate(egfr_combined_cg_ratio_percentile = ntile(egfr_combined_cg_ratio, 100))%>%
  mutate(egfr_combined_cg_ratio_percentile = as.factor(egfr_combined_cg_ratio_percentile))
  
final <- final%>%
  mutate(egfr_combined_cg_ratio_percentile = as.numeric(egfr_combined_cg_ratio_percentile))%>%
  ungroup()

##summarize 
library(dplyr)

summary_by_percentile <- final %>%
  group_by(egfr_combined_cg_ratio_percentile) %>%
  summarise(
    n        = n(),                                 
    min      = min(egfr_combined_cg_ratio, na.rm = TRUE),         
    q1       = quantile(egfr_combined_cg_ratio, 0.25, na.rm = TRUE),  
    median   = median(egfr_combined_cg_ratio, na.rm = TRUE),     
    mean     = mean(egfr_combined_cg_ratio, na.rm = TRUE),       
    q3       = quantile(egfr_combined_cg_ratio, 0.75, na.rm = TRUE),  
    max      = max(egfr_combined_cg_ratio, na.rm = TRUE),         
    sd       = sd(egfr_combined_cg_ratio, na.rm = TRUE)          
  ) %>%
  ungroup()

print(summary_by_percentile,n=30)
print(summary_by_percentile,n=100)
```




###combine the plots as one
```{r}
library(ggplot2)
library(dplyr)
library(scales)
# plot
plot_hosp_side_effect <-ggplot(final, aes(x = egfr_combined_cg_ratio_percentile, y = platinum_related_hos)) +
  geom_point(aes(x = egfr_combined_cg_ratio_decile * 10, y = platinum_related_hos_rate_decile_egfr),  
             size = 6, color = "black", shape =19) + 
  geom_smooth(method = "loess", se = TRUE, span = 0.75, color = "blue",size = 2) +
  scale_x_continuous(breaks = seq(0, 100, by = 10)) +
  labs(title = "Hospitalization for platinum-assosiated AEs",
       x = "Percentile of eGFR-CR-CYS/CG-CrCl ",
       y = "Hospitalization for platinum-assosiated AEs") +
  scale_y_continuous(labels = percent_format(accuracy = 1))+  # Y-axis 
  theme_minimal() +  ## cleantable;classic;minimal
  theme(
    legend.title =element_text() ,
    legend.position = "right",
     axis.title.x = element_text(size = 30),  # X-axis title font size
    axis.title.y = element_text(size = 30),  # Y-axis title font size
    axis.text.x = element_text(size = 30),   # X-axis text font size
    axis.text.y = element_text(size = 30),
    plot.title = element_text(size = 45, face = "bold") # Y-axis text font size
  ) +
  # adding yellow area：assume percentile 1-22 is EGFR-CR-CYS/CG-CrCl < 0.85 area
  annotate("rect", xmin = 1, xmax = 22, ymin = -Inf, ymax = Inf,
           alpha = 0.2, fill = "yellow")
plot_hosp_side_effect
```
```{r}
library(ggplot2)
library(dplyr)

# plot
plot_hosp <-ggplot(final, aes(x = egfr_combined_cg_ratio_percentile, y = hosp_90)) +
  geom_point(aes(x = egfr_combined_cg_ratio_decile * 10, y = hos_rate_decile_egfr),  
             size = 6, color = "black", shape =19) + 
  geom_smooth(method = "loess", se = TRUE, span = 0.75, color = "blue",size = 2) +
  scale_x_continuous(breaks = seq(0, 100, by = 10)) +
  labs(title = "Overall Hospitalization",
       x = "Percentile of eGFR-CR-CYS/CG-CrCl ",
       y = "Overall Hospitalization") +
  scale_y_continuous(labels = percent_format(accuracy = 1))+  # Y-axis 
  theme_minimal() +  ## cleantable;classic;minimal
  theme(
    legend.title =element_text() ,
    legend.position = "right",
     axis.title.x = element_text(size = 30),  # X-axis title font size
    axis.title.y = element_text(size = 30),  # Y-axis title font size
    axis.text.x = element_text(size = 30),   # X-axis text font size
    axis.text.y = element_text(size = 30),
    plot.title = element_text(size = 45, face = "bold") # Y-axis text font size
  ) +
  # adding yellow area：assume percentile 1-22 is EGFR-CR-CYS/CG-CrCl < 0.85 area
  annotate("rect", xmin = 1, xmax = 22, ymin = -Inf, ymax = Inf,
           alpha = 0.2, fill = "yellow")

plot_hosp
```

```{r}
library(ggplot2)
library(dplyr)

# plot
plot_mortality <- ggplot(final, aes(x = egfr_combined_cg_ratio_percentile, y = mortality_90)) +
  geom_point(aes(x = egfr_combined_cg_ratio_decile * 10, y = death_rate_decile_egfr),  
             size = 6, color = "black", shape =19) + 
  geom_smooth(method = "loess", se = TRUE, span = 0.75, color = "blue",size = 2) +
  scale_x_continuous(breaks = seq(0, 100, by = 10)) +
  labs(title = "Mortality",
       x = "Percentile of eGFR-CR-CYS/CG-CrCl ",
       y = "Mortality") +
  scale_y_continuous(labels = percent_format(accuracy = 1))+  # Y-axis 
  theme_minimal() +  ## cleantable;classic;minimal
  theme(
    legend.title =element_text() ,
    legend.position = "right",
     axis.title.x = element_text(size = 30),  # X-axis title font size
    axis.title.y = element_text(size = 30),  # Y-axis title font size
    axis.text.x = element_text(size = 30),   # X-axis text font size
    axis.text.y = element_text(size = 30),
    plot.title = element_text(size = 45, face = "bold") # Y-axis text font size
  ) +
  # adding yellow area：assume percentile 1-22 is EGFR-CR-CYS/CG-CrCl < 0.85 area
  annotate("rect", xmin = 1, xmax = 22, ymin = -Inf, ymax = Inf,
           alpha = 0.2, fill = "yellow")

plot_mortality
```

```{r}
# plot
plot_anemia_3 <- ggplot(final, aes(x = egfr_combined_cg_ratio_percentile, y = Anemia_g3_90days)) +
  geom_point(aes(x = egfr_combined_cg_ratio_decile * 10, y = anemia_3_rate_decile_egfr),  
             size = 6, color = "black", shape =19) +  
  geom_smooth(method = "loess", se = TRUE, span = 0.75, color = "blue",size = 2) +
  scale_x_continuous(breaks = seq(0, 100, by = 10)) +
  labs(title = "Grade ≥ 3 Anemia",
       x = "Percentile of eGFR-CR-CYS/CG-CrCl ",
       y = "Grade ≥ 3 Anemia") +
  scale_y_continuous(labels = percent_format(accuracy = 1))+  # Y-axis 
  theme_minimal() +  ## cleantable;classic;minimal
  theme(
    legend.title =element_text() ,
    legend.position = "right",
     axis.title.x = element_text(size = 30),  # X-axis title font size
    axis.title.y = element_text(size = 30),  # Y-axis title font size
    axis.text.x = element_text(size = 30),   # X-axis text font size
    axis.text.y = element_text(size = 30),
    plot.title = element_text(size = 45, face = "bold") # Y-axis text font size
  ) +
  # adding yellow area：assume percentile 1-22  is EGFR-CR-CYS/CG-CrCl < 0.85 area
  annotate("rect", xmin = 1, xmax = 22, ymin = -Inf, ymax = Inf,
           alpha = 0.2, fill = "yellow")
plot_anemia_3
```

```{r}
# plot
plot_throm_3 <- ggplot(final, aes(x = egfr_combined_cg_ratio_percentile, y = Throm_g3_90days)) +
  geom_point(aes(x = egfr_combined_cg_ratio_decile * 10, y = throm_3_rate_decile_egfr),  
             size = 6, color = "black", shape =19) + 
  geom_smooth(method = "loess", se = TRUE, span = 0.75, color = "blue",size = 2) +
  scale_x_continuous(breaks = seq(0, 100, by = 10)) +
  labs(title = "Grade ≥ 3 Thrombocytopenia",
       x = "Percentile of eGFR-CR-CYS/CG-CrCl ",
       y = "Grade ≥ 3 Thrombocytopenia") +
  scale_y_continuous(labels = percent_format(accuracy = 1))+  # Y-axis 
  theme_minimal() +  ## cleantable;classic;minimal
  theme(
    legend.title =element_text() ,
    legend.position = "right",
     axis.title.x = element_text(size = 30),  # X-axis title font size
    axis.title.y = element_text(size = 30),  # Y-axis title font size
    axis.text.x = element_text(size = 30),   # X-axis text font size
    axis.text.y = element_text(size = 30),
    plot.title = element_text(size = 45, face = "bold") # Y-axis text font size
  ) +
  # adding yellow area：assume percentile 1-22  is EGFR-CR-CYS/CG-CrCl < 0.85 area
  annotate("rect", xmin = 1, xmax = 22, ymin = -Inf, ymax = Inf,
           alpha = 0.2, fill = "yellow")
plot_throm_3
```

```{r}
# plot
plot_aki_3 <- ggplot(final, aes(x = egfr_combined_cg_ratio_percentile, y = AKI_g3_90days)) +
 geom_point(aes(x = egfr_combined_cg_ratio_decile * 10, y = aki_3_rate_decile_egfr),  
             size = 6, color = "black", shape =19) + 
  geom_smooth(method = "loess", se = TRUE, span = 0.75, color = "blue",size = 2) +
  scale_x_continuous(breaks = seq(0, 100, by = 10)) +
  labs(title = "Grade ≥ 3 Creatinine Increased",
       x = "Percentile of eGFR-CR-CYS/CG-CrCl ",
       y = "Grade ≥ 3 Creatinine Increased") +
  scale_y_continuous(labels = percent_format(accuracy = 1))+  # Y-axis 
  theme_minimal() +  ## cleantable;classic;minimal
  theme(
    legend.title =element_text() ,
    legend.position = "right",
     axis.title.x = element_text(size = 30),  # X-axis title font size
    axis.title.y = element_text(size = 30),  # Y-axis title font size
    axis.text.x = element_text(size = 30),   # X-axis text font size
    axis.text.y = element_text(size = 30),
    plot.title = element_text(size = 45, face = "bold") # Y-axis text font size
  ) +
  # adding yellow area：assume percentile 1-22  is EGFR-CR-CYS/CG-CrCl < 0.85 area
  annotate("rect", xmin = 1, xmax = 22, ymin = -Inf, ymax = Inf,
           alpha = 0.2, fill = "yellow")
plot_aki_3
```

```{r}

# using plot_grid to create one plot
plot_percentile_combined <- plot_grid(plot_hosp_side_effect,plot_hosp, plot_mortality,plot_anemia_3,plot_throm_3,plot_aki_3,nrow = 2)

print (plot_percentile_combined) #save as 4000 * 2000
```



# Figure 3: first create competing risk model for whole cohort, next performing CIF plots
## generate cmp status and time
```{r}

library(dplyr)
final <- final%>%
  mutate(all_hosp_time = as.numeric(hosp_90_date - Baseline.Sample.Date))%>%
mutate(time_to_hosp = ifelse(is.na(all_hosp_time), 90, all_hosp_time))%>%
  mutate(time_to_hosp = as.numeric(time_to_hosp))



final <- final %>%
  mutate(time_to_side_effect = ifelse(is.na(platinum_related_hop_time_to_event), 90, platinum_related_hop_time_to_event))%>%
  mutate(time_to_side_effect = as.numeric(time_to_side_effect))

final = final %>%
  mutate(cmp_time_side_effect = case_when(
            time_to_death_90 <= time_to_side_effect ~ time_to_death_90,
            TRUE ~ time_to_side_effect),
         cmp_status_side_effect = case_when(
            time_to_death_90 <= time_to_side_effect ~ death_90,
            TRUE ~ platinum_related_hosp))



final = final %>%
  mutate(cmp_time_hosp = case_when(
            time_to_death_90 <= time_to_hosp ~ time_to_death_90,
            TRUE ~ time_to_hosp),
         cmp_status_hosp = case_when(
            time_to_death_90 <= time_to_hosp ~ death_90,
            TRUE ~ as.numeric(hosp_90)
            ))


###mutate variables type

final <- final %>%
  dplyr::mutate(across(c(cmp_status_side_effect
                  ,cmp_status_hosp,cmp_status_neutro_2,cmp_status_neutro_3,cmp_status_anemia_2,cmp_status_anemia_3,cmp_status_neutro_2,cmp_status_neutro_3,cmp_status_throm_2,cmp_status_throm_3,cmp_status_aki_2,cmp_status_aki_3,cmp_status_grade_2_aes,cmp_status_grade_3_aes), as.factor))
 
```

##Patients with SCR/CYS ratio <0.7 had more hospital admissions for platinum-associated AEs and deaths over 90-days (XX% vs YY% and XX% vs. YY%), respectively.
```{r}
library(tableone)
library(gtsummary)


table_one_incidence <- final %>%
  select(platinum_related_hosp, hosp_90,grade_3_aes,death_90, cr_cys_7) %>%
  tbl_summary(
    by = cr_cys_7,
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",  # 
      all_categorical() ~ "{n} ({p}%)"     # 
    ),
    digits = list(
      all_continuous() ~ 1,  # 
      all_categorical() ~ 1  # 
    )
  ) %>%
  add_overall()

# Display the table
table_one_incidence
#Patients with SCR/CYS ratio <0.7 had more hospital admissions for platinum-associated AEs and deaths over 90-days (19.2% vs 8.9% and 11.2% vs. 1.6%), respectively.


```



##for HR of cre/cys,adjusted for 

#Demographics: age, sex
#markers of kidney function: GFR by Cockcroft equation(most oncologist use for creatinine clearance  instead of combined EPI equation)
#non-GFR determinants of cystatin C: BMI, smoking status, corticosteroid use, and thyroid disease.
#Medical comorbidities:Cancer stage?, Charlson comorbidity index, Ecog, high/low platin dose; carbo/cis; platinum partners including paclitaxel, pemetrexed, gemcitabine；ici
#baseline lab result


```{r}
library(gtsummary)
library(tidycmprsk)
final$ecog_values <- as.factor(final$ecog_values)
final$ecog_values
##outcomes should be factors
##ecog_values affect a lot
##change platelet as platelet/100

final$pre_PLT_45days <- final$pre_PLT_45days / 100


final <- final %>%
  mutate(ecog_cat = ifelse(as.numeric(as.character(ecog_values)) < 1, 0, 1))%>%
  mutate(ecog_cat = as.factor(ecog_cat))
table(final$ecog_cat)

```
##calculate cumulative incidence for side effect
```{r}
# Check the distribution of your competing events
table(final$cmp_status_side_effect)


library(cmprsk)

# First verify your event codes
table(final$cmp_status_side_effect)

# Then run cuminc
fit_cuminc <- cmprsk::cuminc(
  ftime = final$cmp_time_side_effect,
  fstatus = final$cmp_status_side_effect,
  cencode = 0  # Make sure this matches your censoring code
)

# Extract numerical results at specific time points
cuminc_results <- timepoints(fit_cuminc, times = c(30, 90))  # Example time points in days

# View results for your event of interest (typically the first element if 1 is your event code)
print(cuminc_results$est[1,])
## we want 90 days incidence, that is 0.118
```


##calculate cumulative incidence for all hosp
```{r}

library(cmprsk)

# First verify your event codes
table(final$cmp_status_hosp)

# Then run cuminc
fit_cuminc <- cmprsk::cuminc(
  ftime = final$cmp_time_hosp,
  fstatus = final$cmp_status_hosp,
  cencode = 0  # Make sure this matches your censoring code
)

# Extract numerical results at specific time points
cuminc_results <- timepoints(fit_cuminc, times = c(30, 90))  # Example time points in days

# View results for your event of interest (typically the first element if 1 is your event code)
print(cuminc_results$est[1,])

```




##calculate cumulative incidence for grade 3 AEs
```{r}

# Then run cuminc
fit_cuminc <- cmprsk::cuminc(
  ftime = final$cmp_time_grade_3_aes,
  fstatus = final$cmp_status_grade_3_aes,
  cencode = 0  # Make sure this matches your censoring code
)

# Extract numerical results at specific time points
cuminc_results <- timepoints(fit_cuminc, times = c(30, 90))  # Example time points in days

# View results for your event of interest (typically the first element if 1 is your event code)
print(cuminc_results$est[1,])

```











```{r}

tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ cr_cys_7 + Age + sex +  bmi + smoking + steroids +  thyroid + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine +egfr_cock +ici+score ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect) ~ cr_cys_7 + Age + sex +  bmi + smoking + steroids +  thyroid + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine +egfr_cock + ici+score,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_anemia_2,cmp_status_anemia_2)  ~ cr_cys_7 + Age + sex +  bmi + smoking + steroids +  thyroid + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine +egfr_cock+ pre_HGB_45days + ici +score,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_anemia_3,cmp_status_anemia_3)  ~ cr_cys_7 + Age + sex +  bmi + smoking + steroids +  thyroid + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine +egfr_cock+ pre_HGB_45days+ ici +score,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_2,cmp_status_throm_2)  ~ cr_cys_7 + Age + sex +  bmi + smoking + steroids +  thyroid + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine +egfr_cock+ pre_PLT_45days+ ici+score,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_3,cmp_status_throm_3)  ~ cr_cys_7 + Age + sex +  bmi + smoking + steroids +  thyroid + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine +egfr_cock+pre_PLT_45days+ ici+score ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


tidycmprsk::crr(Surv(cmp_time_aki_2,cmp_status_aki_2)  ~ cr_cys_7 + Age + sex +  bmi + smoking + steroids +  thyroid + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine +egfr_cock+ ici+score,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


tidycmprsk::crr(Surv(cmp_time_aki_3,cmp_status_aki_3)  ~ cr_cys_7 + Age + sex +  bmi + smoking + steroids +  thyroid + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine +egfr_cock+ ici+score,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_grade_2_aes,cmp_status_grade_2_aes)  ~ cr_cys_7 + Age + sex +  bmi + smoking + steroids +  thyroid + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine +egfr_cock+ pre_HGB_45days + pre_PLT_45days + ici+score,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


tidycmprsk::crr(Surv(cmp_time_grade_3_aes,cmp_status_grade_3_aes)  ~ cr_cys_7 + Age + sex +  bmi + smoking + steroids +  thyroid + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine +egfr_cock+pre_HGB_45days + pre_PLT_45days + ici+score,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

```

##supplemental tables 2-7 univariable analysis of primary and secondary outcomes

###for grade ≥ 3 anemia
```{r}
tidycmprsk::crr(Surv(cmp_time_anemia_3,cmp_status_anemia_3)  ~ Age,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_anemia_3,cmp_status_anemia_3)  ~  sex ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_anemia_3,cmp_status_anemia_3)  ~ cr_cys_7 ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_anemia_3,cmp_status_anemia_3)  ~  bmi ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_anemia_3,cmp_status_anemia_3)  ~  smoking ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_anemia_3,cmp_status_anemia_3)  ~ steroids ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_anemia_3,cmp_status_anemia_3)  ~ thyroid ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_anemia_3,cmp_status_anemia_3)  ~ cancer_stage  ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_anemia_3,cmp_status_anemia_3)  ~ ecog_cat ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_anemia_3,cmp_status_anemia_3)  ~ dose_1 ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_anemia_3,cmp_status_anemia_3)  ~ carbo ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_anemia_3,cmp_status_anemia_3)  ~ Paclitaxel ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_anemia_3,cmp_status_anemia_3)  ~ Pemetrexed ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_anemia_3,cmp_status_anemia_3)  ~ Gemcitabine ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_anemia_3,cmp_status_anemia_3)  ~ egfr_cock ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_anemia_3,cmp_status_anemia_3)  ~ pre_HGB_45days ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


tidycmprsk::crr(Surv(cmp_time_anemia_3,cmp_status_anemia_3)  ~ ici ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


tidycmprsk::crr(Surv(cmp_time_anemia_3,cmp_status_anemia_3)  ~ score ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

```


###for grade ≥ 3 thrombocytopenia
```{r}
tidycmprsk::crr(Surv(cmp_time_throm_3,cmp_status_throm_3)  ~ Age,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_3,cmp_status_throm_3)  ~  sex ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_3,cmp_status_throm_3)  ~ cr_cys_7 ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_3,cmp_status_throm_3)  ~  bmi ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_3,cmp_status_throm_3)  ~  smoking ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_3,cmp_status_throm_3)  ~ steroids ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_3,cmp_status_throm_3)  ~ thyroid ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_3,cmp_status_throm_3)  ~ cancer_stage  ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_3,cmp_status_throm_3)  ~ ecog_cat ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_3,cmp_status_throm_3)  ~ dose_1 ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_3,cmp_status_throm_3)  ~ carbo ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_3,cmp_status_throm_3)  ~ Paclitaxel ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_3,cmp_status_throm_3)  ~ Pemetrexed ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_3,cmp_status_throm_3)  ~ Gemcitabine ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_3,cmp_status_throm_3)  ~ egfr_cock ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_3,cmp_status_throm_3)  ~ pre_PLT_45days ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_3,cmp_status_throm_3)  ~ ici ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_3,cmp_status_throm_3)  ~ score ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))
```

###for grade ≥ 3 AKI
```{r}
tidycmprsk::crr(Surv(cmp_time_aki_3,cmp_status_aki_3)  ~ Age,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_aki_3,cmp_status_aki_3)  ~  sex ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_aki_3,cmp_status_aki_3)  ~ cr_cys_7 ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_aki_3,cmp_status_aki_3)  ~  bmi ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_aki_3,cmp_status_aki_3)  ~  smoking ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_aki_3,cmp_status_aki_3)  ~ steroids ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_aki_3,cmp_status_aki_3)  ~ thyroid ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_aki_3,cmp_status_aki_3)  ~ cancer_stage  ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_aki_3,cmp_status_aki_3)  ~ ecog_cat ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_aki_3,cmp_status_aki_3)  ~ dose_1 ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_aki_3,cmp_status_aki_3)  ~ carbo ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_aki_3,cmp_status_aki_3)  ~ Paclitaxel ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_aki_3,cmp_status_aki_3)  ~ Pemetrexed ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_aki_3,cmp_status_aki_3)  ~ Gemcitabine ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_aki_3,cmp_status_aki_3)  ~ egfr_cock ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_aki_3,cmp_status_aki_3)  ~ ici ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))
tidycmprsk::crr(Surv(cmp_time_aki_3,cmp_status_aki_3)  ~ score ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))
```

###for overall hospitalization
```{r}
tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ Age,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~  sex ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ cr_cys_7 ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~  bmi ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~  smoking ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ steroids ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ thyroid ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ cancer_stage  ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ ecog_cat ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ dose_1 ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ carbo ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ Paclitaxel ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ Pemetrexed ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ Gemcitabine ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ egfr_cock ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ ici ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ score ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

```
##for platinum-asoociated AEs
```{r}
			
tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect)  ~ Age,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect)  ~  sex ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect)  ~ cr_cys_7 ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect)  ~  bmi ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect)  ~  smoking ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect)  ~ steroids ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect)  ~ thyroid ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect)  ~ cancer_stage  ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect)  ~ ecog_cat ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect)  ~ dose_1 ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect)  ~ carbo ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect)  ~ Paclitaxel ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect)  ~ Pemetrexed ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect)  ~ Gemcitabine ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect)  ~ egfr_cock ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect)  ~ ici ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect)  ~ score ,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))
```


##to be continued

## for 90d mortality with cr/cys <0.7 
```{r}
library(survival)
final <- final%>%
  mutate(follow_up_time = last_follow_up_date - Baseline_sample_Date)
final=final%>%mutate(death_follow_up_time_90d=ifelse(death_90==2&follow_up_time<=90,follow_up_time,90))

final <- final%>%
  mutate(mortality_90 = ifelse(death_90==2,1,0))

surv_fit_90d <- survfit(Surv(death_follow_up_time_90d, mortality_90) ~ cr_cys_7, data = final)
# Fit a Cox proportional hazards model
cox_model <- coxph(Surv(death_follow_up_time_90d, mortality_90) ~ cr_cys_7+ Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine + thyroid +ici +score, data = final)

# View the summary of the Cox model
summary(cox_model)
tbl_cox <- tbl_regression(cox_model, exponentiate = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))
tbl_cox


# using survdiff() for Log-Rank test
log_rank_test <- survdiff(Surv(death_follow_up_time_90d, mortality_90) ~ cr_cys_7, data = final)
log_rank_test$pvalue
```
##univariable analysis
```{r}

tbl_regression(coxph(Surv(death_follow_up_time_90d, mortality_90) ~ cr_cys_7 + Age + sex + egfr_cock + bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine + thyroid + ici, data = final), exponentiate = TRUE, pvalue_fun = ~style_pvalue(.x, digits = 3))


tbl_regression(coxph(Surv(death_follow_up_time_90d, mortality_90) ~ Age, data = final), exponentiate = TRUE, pvalue_fun = ~style_pvalue(.x, digits = 3))

tbl_regression(coxph(Surv(death_follow_up_time_90d, mortality_90) ~ sex, data = final), exponentiate = TRUE, pvalue_fun = ~style_pvalue(.x, digits = 3))
tbl_regression(coxph(Surv(death_follow_up_time_90d, mortality_90) ~ cr_cys_7 , data = final), exponentiate = TRUE, pvalue_fun = ~style_pvalue(.x, digits = 3))
tbl_regression(coxph(Surv(death_follow_up_time_90d, mortality_90) ~ bmi, data = final), exponentiate = TRUE, pvalue_fun = ~style_pvalue(.x, digits = 3))
tbl_regression(coxph(Surv(death_follow_up_time_90d, mortality_90) ~  smoking, data = final), exponentiate = TRUE, pvalue_fun = ~style_pvalue(.x, digits = 3))
tbl_regression(coxph(Surv(death_follow_up_time_90d, mortality_90) ~ steroids , data = final), exponentiate = TRUE, pvalue_fun = ~style_pvalue(.x, digits = 3))
tbl_regression(coxph(Surv(death_follow_up_time_90d, mortality_90) ~ thyroid , data = final), exponentiate = TRUE, pvalue_fun = ~style_pvalue(.x, digits = 3))
tbl_regression(coxph(Surv(death_follow_up_time_90d, mortality_90) ~ cancer_stage , data = final), exponentiate = TRUE, pvalue_fun = ~style_pvalue(.x, digits = 3))
tbl_regression(coxph(Surv(death_follow_up_time_90d, mortality_90) ~ ecog_cat, data = final), exponentiate = TRUE, pvalue_fun = ~style_pvalue(.x, digits = 3))
tbl_regression(coxph(Surv(death_follow_up_time_90d, mortality_90) ~ dose_1, data = final), exponentiate = TRUE, pvalue_fun = ~style_pvalue(.x, digits = 3))
tbl_regression(coxph(Surv(death_follow_up_time_90d, mortality_90) ~ carbo, data = final), exponentiate = TRUE, pvalue_fun = ~style_pvalue(.x, digits = 3))

tbl_regression(coxph(Surv(death_follow_up_time_90d, mortality_90) ~ Paclitaxel, data = final), exponentiate = TRUE, pvalue_fun = ~style_pvalue(.x, digits = 3))
tbl_regression(coxph(Surv(death_follow_up_time_90d, mortality_90) ~ Pemetrexed , data = final), exponentiate = TRUE, pvalue_fun = ~style_pvalue(.x, digits = 3))
tbl_regression(coxph(Surv(death_follow_up_time_90d, mortality_90) ~ ici, data = final), exponentiate = TRUE, pvalue_fun = ~style_pvalue(.x, digits = 3))
tbl_regression(coxph(Surv(death_follow_up_time_90d, mortality_90) ~ Gemcitabine, data = final), exponentiate = TRUE, pvalue_fun = ~style_pvalue(.x, digits = 3))
tbl_regression(coxph(Surv(death_follow_up_time_90d, mortality_90) ~ egfr_cock, data = final), exponentiate = TRUE, pvalue_fun = ~style_pvalue(.x, digits = 3))



tbl_regression(coxph(Surv(death_follow_up_time_90d, mortality_90) ~ score, data = final), exponentiate = TRUE, pvalue_fun = ~style_pvalue(.x, digits = 3))







```

#Figure 3 CIF, outcomes are grade 3 AEs, hosplitalization, hos for side effect,mortality
##exposure_cr_cys_7 : reference group is above 0.7cr/cys, exposure group as < 0.7

### for side effect
```{r}
library(survival)
library(ggplot2)
library(pammtools)
library(adjustedCurves)
library(rms)
library(riskRegression)

# using Fine-Gray model
library(prodlim) 
outcome_model <- FGR(
  formula = Hist(cmp_time_side_effect, cmp_status_side_effect) ~ cr_cys_7+ Age + sex + egfr_cock+ bmi + smoking + steroids  + cancer_stage  +  ecog_cat +dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine  +thyroid + ici + score,
  data = final,
  cause = 1  # interested event
)

final$cr_cys_7 <- as.factor(final$cr_cys_7)
final$cmp_status_side_effect <- as.numeric(as.character(final$cmp_status_side_effect))

adjcif <- adjustedcif(data=final,
                      variable="cr_cys_7",
                      ev_time="cmp_time_side_effect",
                      event="cmp_status_side_effect",
                      method="direct",
                      outcome_model=outcome_model,
                      cause=1,
                      conf_int=TRUE)
plot(adjcif, conf_int=TRUE)

library(ggplot2)

plot_side_effect <- plot(adjcif, conf_int = TRUE) +
  geom_step(linewidth = 3) +  # line width
  scale_x_continuous(
    limits = c(0, 90), 
   breaks = seq(0, 90, by = 15)#  
  ) +
  scale_color_manual(
    values = c("#3B4992FF","#BB0021FF"),  # 
    labels = c("≥ 0.7", "< 0.7"),  # 
    name = "SCR/CYS" #
  ) +
  scale_fill_manual(
    values = c("#3B4992FF","#BB0021FF"),  # 
    labels = c("≥ 0.7", "< 0.7")  # 
  ) +
  labs(
    title = "Hospitalization for Platinum-associated AEs",
    x = "Follow up times (Days)",
    y = "Cumulative Incidence"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 40, face = "bold", # ，
                              hjust = 0,  # left alignment (0= left, 0.5= middle, 1= right)
                              vjust = 1,   # upper aligment(Adjust the vertical position)
                              margin = margin(t = 5, b = 10)),  
    axis.title.x = element_text(size = 40, face = "bold"),  # 
    axis.title.y = element_text(size = 40, face = "bold"),  # 
    axis.text.x = element_text(size = 40),  # 
    axis.text.y = element_text(size = 40),  # 
    legend.title = element_text(size = 40),  #element_blank(),  # 
    legend.text = element_text(size = 40),  # 
    legend.position = "",  # “bottom”, “left”, “right”
    legend.background = element_blank(),  # 
    legend.key = element_blank()  # 
  ) +
  scale_y_continuous(
    expand = c(0, 0), 
    limits = c(0, 0.35), 
    labels = scales::percent_format(accuracy = 1)  # 
  ) +
  annotate("text", x = 64, y = 0.28, label = "sHR 2.50; CI 1.19-5.28", size = 20, hjust = 1)

print(plot_side_effect)
```



###for hospitalization
```{r}
library(survival)
library(ggplot2)
library(pammtools)
library(adjustedCurves)
library(rms)
library(riskRegression)

# using fine grey model
library(prodlim) 
outcome_model <- FGR(
  formula = Hist(cmp_time_hosp, cmp_status_hosp) ~ cr_cys_7+ Age + sex + egfr_cock+ bmi + smoking + steroids  + cancer_stage  +  ecog_cat +dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine  +thyroid + ici + score,
  data = final,
  cause = 1  # interested event
)

final$cr_cys_7 <- as.factor(final$cr_cys_7)
final$cmp_status_hosp <- as.numeric(as.character(final$cmp_status_hosp))

adjcif <- adjustedcif(data=final,
                      variable="cr_cys_7",
                      ev_time="cmp_time_hosp",
                      event="cmp_status_hosp",
                      method="direct",
                      outcome_model=outcome_model,
                      cause=1,
                      conf_int= F)

plot(adjcif, conf_int =F )

library(ggplot2)

plot_hosp <- plot(adjcif, conf_int = F) +
  geom_step(linewidth = 3) +  # line width
  scale_x_continuous(
    limits = c(0, 90), 
   breaks = seq(0, 90, by = 15)#  
  ) +
   scale_color_manual(
    values = c("#3B4992FF","#BB0021FF"),  # 
    labels = c(),  # "≥ 0.7", "< 0.7"
    name = "" #设置图例标题SCr/CYS
  ) +
  scale_fill_manual(
    values = c("#3B4992FF","#BB0021FF"),  # 
    labels = c("")  # ≥ 0.7", "< 0.7
  ) +
 
  labs(
    title = "",# "Overall hospitalization" will shown in the middle
    x = "Follow up times (Days)",
    y = "Cumulative Incidence"
  ) +
   ggtitle("Overall hospitalization") +  # another way to set the title, will be shown in left top
  theme_classic() +
  theme(
    plot.title = element_text(size = 40, face = "bold", # ，
                              hjust = 0,  # left alignment (0= left, 0.5= middle, 1= right)
                              vjust = 1,   # upper aligment(Adjust the vertical position)
                              margin = margin(t = 5, b = 10)),  # 
    axis.title.x = element_text(size = 40, face = "bold"),  # 
    axis.title.y = element_text(size = 40, face = "bold"),  # 
    axis.text.x = element_text(size = 40),  # 
    axis.text.y = element_text(size = 40),  # 
    legend.title =element_text(size = 40),  #element_blank(),  # 
    legend.text = element_text(size = 40),  # 
    legend.position = "",  # “bottom”, “left”, “right”
    legend.background = element_blank(),  # 
    legend.key = element_blank()  # 
  ) +
  scale_y_continuous(
    expand = c(0, 0), # 
    limits = c(0, 0.5), 
    labels = scales::percent_format(accuracy = 1)  # 
  ) +
  
  annotate("text", x = 64, y = 0.4, label = "sHR 1.64; CI 1.05-2.56", size = 20, hjust = 1)

print(plot_hosp)
```


### for grade 3 anemia
```{r}
library(survival)
library(ggplot2)
library(pammtools)
library(adjustedCurves)
library(rms)
library(riskRegression)

# using Fine-Gray model
library(prodlim) 
outcome_model <- FGR(
  formula = Hist(cmp_time_anemia_3, cmp_status_anemia_3) ~ cr_cys_7+ Age + sex + egfr_cock+ bmi + smoking + steroids  + cancer_stage  +  ecog_cat +dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine  +thyroid + pre_HGB_45days + ici + score,
  data = final,
  cause = 1  # interested event
)

final$cr_cys_7 <- as.factor(final$cr_cys_7)
final$cmp_status_anemia_3 <- as.numeric(as.character(final$cmp_status_anemia_3))

adjcif <- adjustedcif(data=final,
                      variable="cr_cys_7",
                      ev_time="cmp_time_anemia_3",
                      event="cmp_status_anemia_3",
                      method="direct",
                      outcome_model=outcome_model,
                      cause=1,
                      conf_int=TRUE)
plot(adjcif, conf_int=TRUE)

library(ggplot2)

plot_anemia_3 <- plot(adjcif, conf_int = TRUE) +
  geom_step(linewidth = 3) +  # line width
  scale_x_continuous(
    limits = c(0, 90), 
   breaks = seq(0, 90, by = 15)#  
  ) +
   scale_color_manual(
    values = c("#3B4992FF","#BB0021FF"),  # 
    labels = c("≥ 0.7", "< 0.7"),  # 
    name = "SCR/CYS" #
  ) +
  scale_fill_manual(
    values = c("#3B4992FF","#BB0021FF"),  # 
    labels = c("≥ 0.7", "< 0.7")  # 
  ) +
  labs(
    title = "Grade ≥ 3 Anemia",
    x = "Follow up times (Days)",
    y = "Cumulative Incidence"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 40, face = "bold", #，
                              hjust = 0,  # left alignment (0= left, 0.5= middle, 1= right)
                              vjust = 1,   # upper aligment(Adjust the vertical position)
                              margin = margin(t = 5, b = 10)),  
    axis.title.x = element_text(size = 40, face = "bold"),  # 
    axis.title.y = element_text(size = 40, face = "bold"),  # 
    axis.text.x = element_text(size = 40),  # 
    axis.text.y = element_text(size = 40),  # 
    legend.title = element_text(size = 40),  #element_blank(),  # 
    legend.text = element_text(size = 40),  # 
    legend.position = "",  # “bottom”, “left”, “right”
    legend.background = element_blank(),  # 
    legend.key = element_blank()  # remove background
  ) +
  scale_y_continuous(
    expand = c(0, 0), 
    limits = c(0, 0.35), 
    labels = scales::percent_format(accuracy = 1)  # 
  ) +
  annotate("text", x = 64, y = 0.29, label = "sHR 2.66; CI 1.44-4.89", size = 20, hjust = 1)
print(plot_anemia_3)
```


### for grade 3 thrombocytopenia
```{r}
library(survival)
library(ggplot2)
library(pammtools)
library(adjustedCurves)
library(rms)
library(riskRegression)

# using Fine-Gray model
library(prodlim) 
outcome_model <- FGR(
  formula = Hist(cmp_time_throm_3, cmp_status_throm_3) ~ cr_cys_7+ Age + sex + egfr_cock+ bmi + smoking + steroids  + cancer_stage  +  ecog_cat +dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine  +thyroid + pre_PLT_45days + ici + score,
  data = final,
  cause = 1  # interested event
)

final$cr_cys_7 <- as.factor(final$cr_cys_7)
final$cmp_status_throm_3 <- as.numeric(as.character(final$cmp_status_throm_3))

adjcif <- adjustedcif(data=final,
                      variable="cr_cys_7",
                      ev_time="cmp_time_throm_3",
                      event="cmp_status_throm_3",
                      method="direct",
                      outcome_model=outcome_model,
                      cause=1,
                      conf_int=TRUE)
plot(adjcif, conf_int=TRUE)

library(ggplot2)

plot_throm_3 <- plot(adjcif, conf_int = TRUE) +
  geom_step(linewidth = 3) +  # line width
  scale_x_continuous(
    limits = c(0, 90), 
   breaks = seq(0, 90, by = 15)#  
  ) +
  scale_color_manual(
    values = c("#3B4992FF","#BB0021FF"),  # 
    labels = c("≥ 0.7", "< 0.7"),  # 
    name = "SCR/CYS" #
  ) +
  scale_fill_manual(
    values = c("#3B4992FF","#BB0021FF"),  # 
    labels = c("≥ 0.7", "< 0.7")  # 
  ) +
  labs(
    title = "Grade ≥ 3 Thrombocytopenia",
    x = "Follow up times (Days)",
    y = "Cumulative Incidence"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 40, face = "bold", # ，
                              hjust = 0,  # left alignment (0= left, 0.5= middle, 1= right)
                              vjust = 1,   # upper aligment(Adjust the vertical position)
                              margin = margin(t = 5, b = 10)),  
    axis.title.x = element_text(size = 40, face = "bold"),  # 
    axis.title.y = element_text(size = 40, face = "bold"),  # 
    axis.text.x = element_text(size = 40),  # 
    axis.text.y = element_text(size = 40),  # 
    legend.title = element_text(size = 40),  #element_blank(),  # 
    legend.text = element_text(size = 40),  # 
    legend.position = "",  # “bottom”, “left”, “right”
    legend.background = element_blank(),  # 
    legend.key = element_blank()  # 
  ) +
  scale_y_continuous(
    expand = c(0, 0), 
    limits = c(0, 0.2), 
    labels = scales::percent_format(accuracy = 1)  # 
  ) +
  annotate("text", x = 64, y = 0.165, label = "sHR 6.58; CI 1.90-22.8", size = 20, hjust = 1)
print(plot_throm_3)
```




### for grade 3 aki
```{r}
library(survival)
library(ggplot2)
library(pammtools)
library(adjustedCurves)
library(rms)
library(riskRegression)

# using Fine-Gray model
library(prodlim) 
outcome_model <- FGR(
  formula = Hist(cmp_time_aki_3, cmp_status_aki_3) ~ cr_cys_7+ Age + sex + egfr_cock+ bmi + smoking + steroids  + cancer_stage  +  ecog_cat +dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine  +thyroid + ici + score,
  data = final,
  cause = 1  # interested event
)

final$cr_cys_7 <- as.factor(final$cr_cys_7)
final$cmp_status_aki_3 <- as.numeric(as.character(final$cmp_status_aki_3))

adjcif <- adjustedcif(data=final,
                      variable="cr_cys_7",
                      ev_time="cmp_time_aki_3",
                      event="cmp_status_aki_3",
                      method="direct",
                      outcome_model=outcome_model,
                      cause=1,
                      conf_int=TRUE)
plot(adjcif, conf_int=TRUE)

library(ggplot2)

plot_aki_3 <- plot(adjcif, conf_int = TRUE) +
  geom_step(linewidth = 3) +  # line width
   scale_x_continuous(
    limits = c(0, 90), 
   breaks = seq(0, 90, by = 15)#  
  ) +
  scale_color_manual(
    values = c("#3B4992FF","#BB0021FF"),  # 
    labels = c("≥ 0.7", "< 0.7"),  # 
    name = "SCR/CYS" #
  ) +
  scale_fill_manual(
    values = c("#3B4992FF","#BB0021FF"),  # 
    labels = c("≥ 0.7", "< 0.7")  # 
  ) +
  labs(
    title = "Grade ≥ 3 Creatinine Increased",
    x = "Follow up times (Days)",
    y = "Cumulative Incidence"
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(size = 40, face = "bold", # ，
                              hjust = 0,  # left alignment (0= left, 0.5= middle, 1= right)
                              vjust = 1,   # upper aligment(Adjust the vertical position)
                              margin = margin(t = 5, b = 10)),  
    axis.title.x = element_text(size = 40, face = "bold"),  # 
    axis.title.y = element_text(size = 40, face = "bold"),  # 
    axis.text.x = element_text(size = 40),  # 
    axis.text.y = element_text(size = 40),  # 
    legend.title = element_text(size = 40),  #element_blank(),  # 
    legend.text = element_text(size = 40),  # 
    legend.position = "",  # “bottom”, “left”, “right”
    legend.background = element_blank(),  # 
    legend.key = element_blank()  # 
  ) +
  scale_y_continuous(
    expand = c(0, 0), 
    limits = c(0, 0.06), 
    labels = scales::percent_format(accuracy = 1)  # 
  ) +
  annotate("text", x = 64, y = 0.05, label = "sHR 4.46; CI 0.32-61.7", size = 20, hjust = 1)
print(plot_aki_3)
```



#1-KM curve

```{r}
library(survival)
final <- final%>%
  mutate(follow_up_time = last_follow_up_date - Baseline_sample_Date)
final=final%>%mutate(death_follow_up_time_90d=ifelse(death_90==2&follow_up_time<=90,follow_up_time,90))

final <- final%>%
  mutate(mortality_90 = ifelse(death_90==2,1,0))

surv_fit_90d <- survfit(Surv(death_follow_up_time_90d, mortality_90) ~ cr_cys_7, data = final)
# Fit a Cox proportional hazards model
cox_model <- coxph(Surv(death_follow_up_time_90d, mortality_90) ~ cr_cys_7+ Age + sex + egfr_cock+ bmi + smoking + steroids  + cancer_stage  +  ecog_cat +dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine  +thyroid+ ici+score, data = final)


plot_death <- ggsurvplot(
   surv_fit_90d, # survfit object with calculated statistics.
   fun = "event", # 1-KM curve （1 - survival）
   data = final,                    # data used to fit survival curves. 
   risk.table = F,                # show risk table.
   risk.table.type = "cumevents",  # 
   pval = F,                      # show p-value of log-rank test.
   conf.int = F,                     # hide or show confidence intervals.
   xlim = c(0, 90),                  # narrower X axis.
   break.time.by = 15,               # break X axis in time intervals.
   risk.table.y.text.col = TRUE,     # color risk table text annotations.
   risk.table.y.text = TRUE,         # show bars instead of names in legend of risk table.
   risk.table.height = 0.3,
   risk.table.fontsize = 6,
 #  ylim = c(0, 0.25),                 # Y axis limits
 #  break.y.by = 0.2,                 # break Y axis by 0.2.
   surv.scale = "percent", # Y axis in percent.
   title = "Mortality ", #  
   legend = c(15, 0.15),             # legend position.
   legend.title = "",                # legend title.
   legend.labs = c("SCr/CYS ≥ 0.7","SCr/CYS < 0.7"), # legend labels.
   font.legend = c(16, "plain"),     
   xlab = "Follow up time (days)",   # x-axis label.
   palette = c("#3B4992FF","#BB0021FF"),  # custom color palette.
   size = 3
)

plot_death$plot <- plot_death$plot + 
  scale_y_continuous(labels = percent_format(accuracy = 1),limits = c(0, 0.2) )+
  annotate("text", x = 60, y = 0.08, label = "", size = 10, hjust = 1)+
  annotate("text", x = 65, y = 0.165, label = "aHR 3.76; CI 1.15-12.3", size = 20, hjust = 1)+
  ggtitle("Mortality") +  # 
theme(
    plot.title = element_text(size = 40, face = "bold", color = "black"),        # Title
    plot.subtitle = element_text(size = 40, face = "bold.italic", color = "purple"),  # Subtitle
    plot.caption = element_text(size = 40, face = "plain", color = "orange"),    # Caption
    axis.title.x = element_text(size = 40, face = "bold", color = "black"),      # X-axis label
    axis.title.y = element_text(size = 40, face = "bold", color = "black"),      # Y-axis label
    axis.text.x = element_text(size = 40, face = "plain", color = "black"),      # X-axis tick labels
    axis.text.y = element_text(size = 40, face = "plain")                        # Y-axis tick labels
  )
print(plot_death)
```


```{r}
## for risk table of 1-KM, this is basic code
ggrisktable(
  surv_fit_90d,
  data = final,
  risk.table.type = c("absolute", "percentage", "abs_pct", "nrisk_cumcensor",
    "nrisk_cumevents")
)

ggcumevents(surv_fit_90d, data = final)

ggcumcensor(surv_fit_90d, data = final)

##this is formatted code
library(survminer)
library(ggplot2)
 ggsurvtable(
  surv_fit_90d,
  data = final,
  survtable = c("cumevents"),#"cumcensor" or "risk.table"
  risk.table.type = c("nrisk_cumevents"),# we can choose "absolute", "percentage", "abs_pct", "nrisk_cumcensor"
  title = NULL,
  risk.table.title = NULL,
  cumevents.title = NULL,
  cumcensor.title = NULL,
  color = "strata",
  palette = c("#3B4992FF","#BB0021FF"),
  break.time.by = 20,
  xlim = c(0,90),
  xscale = 1,
  xlab = "Follow up time (days)",
  ylab = "",
  xlog = FALSE,
  legend = "none",# can choose top
  legend.title = "", # can write "Strata" or anything
  legend.labs = c("SCr/CYS ≥ 0.7", "SCr/CYS < 0.7"),
  y.text = TRUE,
  y.text.col = TRUE,
  fontsize = 4.5,
  font.family = "",
  axes.offset = TRUE,
  ggtheme = theme_survminer()
)

```

# using plot_grid to creat one plot
```{r}
# using plot_grid to creat one plot
library(cowplot)
combined_plot_2 <- plot_grid(plot_side_effect,plot_hosp,plot_death$plot, plot_anemia_3,plot_throm_3,plot_aki_3,nrow = 2)

print (combined_plot_2) #save as 4000 * 2000

```


# Figure 5 one year mortality - KM curve(will decide whether use it finally)

```{r}
library(survival)
final <- final%>%
  mutate(follow_up_time = last_follow_up_date - Baseline_sample_Date)
final=final%>%mutate(death_follow_up_time_90d=ifelse(death_90==2&follow_up_time<=90,follow_up_time,90))

final <- final%>%
  mutate(mortality_90 = ifelse(death_90==2,1,0))

```

## for 90d mortality with cr/cys <0.7 
```{r}
library(survival)
final <- final%>%
  mutate(follow_up_time = last_follow_up_date - Baseline_sample_Date)
final=final%>%mutate(death_follow_up_time_90d=ifelse(death_90==2&follow_up_time<=90,follow_up_time,90))

final <- final%>%
  mutate(mortality_90 = ifelse(death_90==2,1,0))

surv_fit_90d <- survfit(Surv(death_follow_up_time_90d, mortality_90) ~ cr_cys_7, data = final)
# Fit a Cox proportional hazards model
cox_model <- coxph(Surv(death_follow_up_time_90d, mortality_90) ~ cr_cys_7+ Age + sex + egfr_cock+ bmi + smoking + steroids  + cancer_stage  +  ecog_cat +dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine  +thyroid+ ici+score, data = final)

# View the summary of the Cox model
summary(cox_model)
tbl_cox <- tbl_regression(cox_model, exponentiate = TRUE,,pvalue_fun = function(x) style_pvalue(x, digits = 3))
tbl_cox


# using survdiff() for Log-Rank test
log_rank_test <- survdiff(Surv(death_follow_up_time_90d, mortality_90) ~ cr_cys_7, data = final)
log_rank_test$pvalue

# Plot survival curves :simple survival analysis without covariants
library(survival)
library(ggplot2)
library(survminer)
library(scales)
# Create the survfit object
```

```{r}
# Generate the ggsurvplot object

ggsurv <- ggsurvplot(
   surv_fit_90d,                     # survfit object with calculated statistics.
   data = final,                    # data used to fit survival curves. 
   risk.table = T,                # show risk table.
   pval = TRUE,                      # show p-value of log-rank test.
   conf.int = FALSE,                 # hide confidence intervals.
   xlim = c(0, 90),                  # narrower X axis.
   break.time.by = 10,               # break X axis in time intervals.
   risk.table.y.text.col = TRUE,     # color risk table text annotations.
   risk.table.y.text = TRUE,         # show bars instead of names in legend of risk table.
   risk.table.height = 0.3,
   risk.table.fontsize = 6,
   ylim = c(0.8, 1),                 # Y axis limits
   break.y.by = 0.2,                 # break Y axis by 0.2.
   surv.scale = "percent", # Y axis in percent.
   title = "", #  
   legend = c(0.2, 0.25),             # legend position.
   legend.title = "",                # legend title.
   legend.labs = c("SCr/CYS ≥ 0.7","SCr/CYS < 0.7"), # legend labels.
   font.legend = c(16, "plain"),     
   xlab = "Follow up time (days)",   # x-axis label.
   palette = c("#3B4992FF","#BB0021FF")  # custom color palette.
)

ggsurv$plot <- ggsurv$plot + 
  scale_y_continuous(labels = percent_format(accuracy = 1), limits = c(0.8, 1))+
  annotate("text", x = 80, y = 0.83, label = "Log-rank p value < 0.001", size = 6, hjust = 1)+
  annotate("text", x = 78, y = 0.85, label = "HR 3.76; CI 1.15-12.30", size = 6, hjust = 1)+
  ggtitle("") +  # 
theme(
    plot.title = element_text(size = 14, face = "bold", color = "black"),        # Title
    plot.subtitle = element_text(size = 20, face = "bold.italic", color = "purple"),  # Subtitle
    plot.caption = element_text(size = 20, face = "plain", color = "orange"),    # Caption
    axis.title.x = element_text(size = 16, face = "bold", color = "black"),      # X-axis label
    axis.title.y = element_text(size = 20, face = "bold", color = "black"),      # Y-axis label
    axis.text.x = element_text(size = 16, face = "plain", color = "black"),      # X-axis tick labels
    axis.text.y = element_text(size = 16, face = "plain")                        # Y-axis tick labels
  )


ggsurv$table <- ggsurv$table + 
  theme(
    axis.text.x = element_text(size = 16),
    axis.title.x = element_text(size = 16, face = "bold", color = "black")# risk table x axis font and size
  )
print(ggsurv$plot) #save as 900* 600
print(ggsurv$table) # save as 950*200
```
## how many patients lost follow up
```{r}

final <- final %>%
  mutate(
    lost_follow_up = as.factor(ifelse(mortality_90 == 0 & follow_up_time < 90, 1, 0))
  )
table(final$lost_follow_up)

```


##KM curve for cr_cys_cat ("< 0.5","0.5-0.7","0.7-0.9","≥ 0.9")


```{r}
library(survival)
final <- final%>%
  mutate(follow_up_time = last_follow_up_date - Baseline_sample_Date)
final=final%>%mutate(death_follow_up_time_90d=ifelse(death_90==2&follow_up_time<=90,follow_up_time,90))

final <- final%>%
  mutate(mortality_90 = ifelse(death_90==2,1,0))

surv_fit_90d_cat <- survfit(Surv(death_follow_up_time_90d, mortality_90) ~ cr_cys_cat, data = final)
# Fit a Cox proportional hazards model
cox_model_cat <- coxph(Surv(death_follow_up_time_90d, mortality_90) ~ cr_cys_7+ Age + sex + egfr_cock+ bmi + smoking + steroids  + cancer_stage  +  ecog_cat +dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine  +thyroid+ ici+score, data = final)

# View the summary of the Cox model
summary(cox_model_cat)
tbl_cox_cat <- tbl_regression(cox_model_cat, exponentiate = TRUE,,pvalue_fun = function(x) style_pvalue(x, digits = 3))
tbl_cox_cat


# 
log_rank_test <- survdiff(Surv(death_follow_up_time_90d, mortality_90) ~ cr_cys_cat, data = final)
log_rank_test$pvalue

```

```{r}
# Generate the ggsurvplot object

ggsurv <- ggsurvplot(
   surv_fit_90d_cat,                     # survfit object with calculated statistics.
   data = final,                    # data used to fit survival curves. 
   risk.table = T,                # show risk table.
   pval = TRUE,                      # show p-value of log-rank test.
   conf.int = FALSE,                 # hide confidence intervals.
   xlim = c(0, 90),                  # narrower X axis.
   break.time.by = 10,               # break X axis in time intervals.
   risk.table.y.text.col = TRUE,     # color risk table text annotations.
   risk.table.y.text = TRUE,         # show bars instead of names in legend of risk table.
   risk.table.height = 0.3,
   risk.table.fontsize = 6,
   ylim = c(0.8, 1),                 # Y axis limits
   break.y.by = 0.2,                 # break Y axis by 0.2.
   surv.scale = "percent", # Y axis in percent.
   title = "Figure", # 2 ways to create plot title
   legend = c(0.2, 0.25),             # legend position.
   legend.title = "SCR/CYS",                # legend title.
   legend.labs = c("< 0.5","0.5-0.7","0.7-0.9","≥ 0.9"), # legend labels."SCr/CYS < 0.5",SCr/CYS ≥ 0.7"
   font.legend = c(16, "plain"),     
   xlab = "Follow up time (days)",   # x-axis label.
   palette = c("#d62728","#ff7f0e","#e377c2","#1f77b4")  # custom color palette.
)

ggsurv$plot <- ggsurv$plot + 
  scale_y_continuous(labels = percent_format(accuracy = 1), limits = c(0.8, 1))+
  annotate("text", x = 70, y = 0.83, label = "Log rank P value < 0.001", size = 6, hjust = 1)+
  #annotate("text", x = 78, y = 0.85, label = "L", size = 6, hjust = 1)+
  ggtitle("Figure") +  # 
theme(
    plot.title = element_text(size = 14, face = "bold", color = "black"),        # Title
    plot.subtitle = element_text(size = 20, face = "bold.italic", color = "purple"),  # Subtitle
    plot.caption = element_text(size = 20, face = "plain", color = "orange"),    # Caption
    axis.title.x = element_text(size = 16, face = "bold", color = "black"),      # X-axis label
    axis.title.y = element_text(size = 20, face = "bold", color = "black"),      # Y-axis label
    axis.text.x = element_text(size = 16, face = "plain", color = "black"),      # X-axis tick labels
    axis.text.y = element_text(size = 16, face = "plain")                        # Y-axis tick labels
  )


ggsurv$table <- ggsurv$table + 
  theme(
    axis.text.x = element_text(size = 16),
    axis.title.x = element_text(size = 16, face = "bold", color = "black")# 设置风险表 x 轴刻度标签字体大小
  )
print(ggsurv)
```


##for 1-KM curve (used in Figure 3 CIF )
```{r}
ggsurv <- ggsurvplot(
   surv_fit_90d, # survfit object with calculated statistics.
   fun = "event", # 1-KM curve shouwing cumulative incidense（1 - survival）
   data = final,                    # data used to fit survival curves. 
   risk.table = F,                # show risk table.
   risk.table.type = "cumevents",  # showing cumulative event,but didn't work
   pval = TRUE,                      # show p-value of log-rank test.
   conf.int = T,                     # hide or show confidence intervals.
   xlim = c(0, 90),                  # narrower X axis.
   break.time.by = 10,               # break X axis in time intervals.
   risk.table.y.text.col = TRUE,     # color risk table text annotations.
   risk.table.y.text = TRUE,         # show bars instead of names in legend of risk table.
   risk.table.height = 0.3,
   risk.table.fontsize = 6,
   ylim = c(0, 0.2),                 # Y axis limits
   break.y.by = 0.2,                 # break Y axis by 0.2.
   surv.scale = "percent", # Y axis in percent.
   title = "Figure ", # 
   legend = c(15, 0.15),             # legend position.
   legend.title = "",                # legend title.
   legend.labs = c("SCr/CYS ≥ 0.7","SCr/CYS < 0.7"), # legend labels.
   font.legend = c(16, "plain"),     
   xlab = "Follow up time (days)",   # x-axis label.
   palette = c("#3B4992FF","#BB0021FF")  # custom color palette.
)

ggsurv$plot <- ggsurv$plot + 
  scale_y_continuous(labels = percent_format(accuracy = 1), limits = c(0, 0.2))+
  annotate("text", x = 15, y = 0.1, label = "Log-rank p value < 0.001", size = 6, hjust = 1)+
  annotate("text", x = 15, y = 0.05, label = "HR 6.61; CI 2.27-19.20", size = 6, hjust = 1)+
  ggtitle("Figure B") +  # 
theme(
    plot.title = element_text(size = 14, face = "bold", color = "black"),        # Title
    plot.subtitle = element_text(size = 20, face = "bold.italic", color = "purple"),  # Subtitle
    plot.caption = element_text(size = 20, face = "plain", color = "orange"),    # Caption
    axis.title.x = element_text(size = 16, face = "bold", color = "black"),      # X-axis label
    axis.title.y = element_text(size = 20, face = "bold", color = "black"),      # Y-axis label
    axis.text.x = element_text(size = 16, face = "plain", color = "black"),      # X-axis tick labels
    axis.text.y = element_text(size = 16, face = "plain")                        # Y-axis tick labels
  )
print(ggsurv)

## for risk table of 1-KM, this is basic code
ggrisktable(
  surv_fit_90d,
  data = final,
  risk.table.type = c("absolute", "percentage", "abs_pct", "nrisk_cumcensor",
    "nrisk_cumevents")
)

ggcumevents(surv_fit_90d, data = final)

ggcumcensor(surv_fit_90d, data = final)

##this is formatted code
library(survminer)
library(ggplot2)
 ggsurvtable(
  surv_fit_90d,
  data = final,
  survtable = c("cumevents"),#"cumcensor" or "risk.table"
  risk.table.type = c("nrisk_cumevents"),# we can choose "absolute", "percentage", "abs_pct", "nrisk_cumcensor"
  title = NULL,
  risk.table.title = NULL,
  cumevents.title = NULL,
  cumcensor.title = NULL,
  color = "strata",
  palette = c("#3B4992FF","#BB0021FF"),
  break.time.by = 10,
  xlim = c(0,90),
  xscale = 1,
  xlab = "Follow up time (days)",
  ylab = "",
  xlog = FALSE,
  legend = "none",# can choose top
  legend.title = "", # can write "Strata" or anything
  legend.labs = c("SCr/CYS ≥ 0.7", "SCr/CYS < 0.7"),
  y.text = TRUE,
  y.text.col = TRUE,
  fontsize = 4.5,
  font.family = "",
  axes.offset = TRUE,
  ggtheme = theme_survminer()
)

```



# Figure 4: competing risk model for subgroup(ecog as 2 groups)
```{r}
final <- final %>%
  mutate(ecog_cat = ifelse(as.numeric(as.character(ecog_values)) < 1, 0, 1))%>%
  mutate(ecog_cat = as.factor(ecog_cat))
table(final$ecog_cat)
```

##for age subgroup

```{r}

final_0_65 <- final%>%
  filter(Age  < 65)

library(gtsummary)
library(tidycmprsk)
##outcomes should be factors


tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ cr_cys_7 + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat +dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine + thyroid + ici+score,failcode=1,cencode=0, data = final_0_65) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect) ~ cr_cys_7 + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final_0_65) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


tidycmprsk::crr(Surv(cmp_time_grade_3_aes,cmp_status_grade_3_aes)  ~ cr_cys_7 + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine + pre_HGB_45days + pre_PLT_45days + thyroid+ ici+score,failcode=1,cencode=0, data = final_0_65) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

cox_model <- coxph(Surv(death_follow_up_time_90d, mortality_90) ~ cr_cys_7+ Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine + thyroid +ici+score, data = final_0_65)

# View the summary of the Cox model
summary(cox_model)
tbl_cox <- tbl_regression(cox_model, exponentiate = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))
tbl_cox

```  


```{r}

final_65_90 <- final%>%
  filter(Age >= 65)

library(gtsummary)
library(tidycmprsk)
##outcomes should be factors

tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ cr_cys_7 + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat +dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final_65_90) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect) ~ cr_cys_7 + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final_65_90) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


tidycmprsk::crr(Surv(cmp_time_grade_3_aes,cmp_status_grade_3_aes)  ~ cr_cys_7 + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine + pre_HGB_45days + pre_PLT_45days+ thyroid+ ici+score,failcode=1,cencode=0, data = final_65_90) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


cox_model <- coxph(Surv(death_follow_up_time_90d, mortality_90) ~ cr_cys_7+ Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine + thyroid +ici+score, data = final_65_90)

# View the summary of the Cox model
summary(cox_model)
tbl_cox <- tbl_regression(cox_model, exponentiate = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))
tbl_cox
```  

##subgroup for males/femates: deleted variable of sex
```{r}
final_male <- final%>%
  filter(sex == 1 )

tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ cr_cys_7 + Age +  egfr_cock+ bmi + smoking + steroids  + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final_male) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect) ~ cr_cys_7 + Age + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final_male) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_grade_3_aes,cmp_status_grade_3_aes)  ~ cr_cys_7 + Age + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine + pre_HGB_45days + pre_PLT_45days+ thyroid+ ici+score,failcode=1,cencode=0, data = final_male) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


cox_model <- coxph(Surv(death_follow_up_time_90d, mortality_90) ~ cr_cys_7 + Age + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score, data = final_male)

# View the summary of the Cox model
summary(cox_model)
tbl_cox <- tbl_regression(cox_model, exponentiate = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))
tbl_cox

```

```{r}
final_female <- final%>%
  filter(sex == 0 )

tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ cr_cys_7 + Age +  egfr_cock+ bmi + smoking + steroids  + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final_female) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect) ~ cr_cys_7 + Age + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final_female) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_grade_3_aes,cmp_status_grade_3_aes)  ~ cr_cys_7 + Age + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine + pre_HGB_45days + pre_PLT_45days+ thyroid+ ici+score,failcode=1,cencode=0, data = final_female) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


cox_model <- coxph(Surv(death_follow_up_time_90d, mortality_90) ~ cr_cys_7+ Age  + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine + thyroid +ici+score, data = final_female)

# View the summary of the Cox model
summary(cox_model)
tbl_cox <- tbl_regression(cox_model, exponentiate = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))
tbl_cox

```

```{r}
final_egfr_above_60 <- final%>%
  filter(egfr_cock >= 60)

library(gtsummary)
library(tidycmprsk)
##outcomes should be factors

tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ cr_cys_7 + Age + sex +  bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final_egfr_above_60) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect) ~ cr_cys_7 + Age + sex +  bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final_egfr_above_60) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_grade_3_aes,cmp_status_grade_3_aes)  ~ cr_cys_7 + Age + sex +  bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine +pre_HGB_45days + pre_PLT_45days+ thyroid+ ici+score,failcode=1,cencode=0, data = final_egfr_above_60) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

cox_model <- coxph(Surv(death_follow_up_time_90d, mortality_90) ~ cr_cys_7+ Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine + thyroid +ici+score, data = final_egfr_above_60)
summary(cox_model)
tbl_cox <- tbl_regression(cox_model, exponentiate = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))
tbl_cox


```  

```{r}
final_egfr_less_60 <- final%>%
  filter(egfr_cock < 60)

library(gtsummary)
library(tidycmprsk)
##outcomes should be factors

tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ cr_cys_7 + Age + sex +  bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final_egfr_less_60) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect) ~ cr_cys_7 + Age + sex +  bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final_egfr_less_60) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_grade_3_aes,cmp_status_grade_3_aes)  ~ cr_cys_7 + Age + sex +  bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine +pre_HGB_45days + pre_PLT_45days+ thyroid+ ici+score,failcode=1,cencode=0, data = final_egfr_less_60) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


cox_model <- coxph(Surv(death_follow_up_time_90d, mortality_90) ~ cr_cys_7+ Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine + thyroid +ici+score, data = final_egfr_less_60)
summary(cox_model)
tbl_cox <- tbl_regression(cox_model, exponentiate = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))
tbl_cox
```  

##subgroup for BMI
```{r}

final_bmi_below_25 <- final %>%
  filter(bmi < 25) 

tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ cr_cys_7 + Age + sex + egfr_cock+ smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final_bmi_below_25) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect) ~ cr_cys_7 + Age + sex + egfr_cock+ smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final_bmi_below_25) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_grade_3_aes,cmp_status_grade_3_aes) ~ cr_cys_7 + Age + sex + egfr_cock+ smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+pre_HGB_45days + pre_PLT_45days+ thyroid+ ici+score,failcode=1,cencode=0, data = final_bmi_below_25) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

cox_model <- coxph(Surv(death_follow_up_time_90d, mortality_90) ~ cr_cys_7+ Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine + thyroid +ici+score, data = final_bmi_below_25)
summary(cox_model)
tbl_cox <- tbl_regression(cox_model, exponentiate = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))
tbl_cox


```
```{r}
final_bmi_above_25 <- final %>%
  filter(bmi >= 25) 

tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ cr_cys_7 + Age + sex + egfr_cock+ smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine + thyroid+ ici+score,failcode=1,cencode=0, data = final_bmi_above_25) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect) ~ cr_cys_7 + Age + sex + egfr_cock+ smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final_bmi_above_25) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_grade_3_aes,cmp_status_grade_3_aes) ~ cr_cys_7 + Age + sex + egfr_cock+ smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+pre_HGB_45days + pre_PLT_45days+ thyroid+ ici+score,failcode=1,cencode=0, data = final_bmi_above_25) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

cox_model <- coxph(Surv(death_follow_up_time_90d, mortality_90) ~ cr_cys_7+ Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine + thyroid +ici+score, data = final_bmi_above_25)
summary(cox_model)
tbl_cox <- tbl_regression(cox_model, exponentiate = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))
tbl_cox
```


##subgroup for cancer type
```{r}
table(final$cancer_retype)

final_thoracic <- final%>%
  filter(cancer_retype == 1)

tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ cr_cys_7 + Age + sex + egfr_cock+ bmi + smoking + steroids  + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final_thoracic) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect) ~ cr_cys_7 + Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final_thoracic) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_grade_3_aes,cmp_status_grade_3_aes)  ~ cr_cys_7 + Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine + pre_HGB_45days + pre_PLT_45days+ thyroid+ ici+score,failcode=1,cencode=0, data = final_thoracic) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


cox_model <- coxph(Surv(death_follow_up_time_90d, mortality_90) ~ cr_cys_7+ Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine + thyroid +ici+score, data = final_thoracic)
summary(cox_model)
tbl_cox <- tbl_regression(cox_model, exponentiate = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))
tbl_cox

```



```{r}
final_breast <- final%>%
  filter(cancer_retype == 2) ## don't have male patients,all use carboplatin and steroids,high dose, no Paclitaxel,   Pemetrexed,Gemcitabine, thyroid

tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ cr_cys_7 + Age + egfr_cock+ bmi + smoking  + cancer_stage + ecog_cat+ ici+score,failcode=1,cencode=0, data = final_breast) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect) ~ cr_cys_7 + Age  + egfr_cock+ bmi + smoking + cancer_stage + ecog_cat+ ici+score,failcode=1,cencode=0, data = final_breast) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_grade_3_aes,cmp_status_grade_3_aes)  ~ cr_cys_7 + Age + egfr_cock+ bmi + smoking + cancer_stage + ecog_cat + pre_HGB_45days + pre_PLT_45days+ ici+score,failcode=1,cencode=0, data = final_breast) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


cox_model <- coxph(Surv(death_follow_up_time_90d, mortality_90) ~ cr_cys_7 + Age + egfr_cock+ bmi + smoking + cancer_stage + ecog_cat + pre_HGB_45days + pre_PLT_45days+ ici+score, data = final_breast)
summary(cox_model)
tbl_cox <- tbl_regression(cox_model, exponentiate = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))
tbl_cox

```

```{r}
final_GI <- final%>%
  filter(cancer_retype == 3)

summary(final_GI[, c("cr_cys_7", "Age", "sex", "egfr_cock", "bmi",  "smoking", "steroids", "cancer_stage", "ecog_cat",  "dose_1", "carbo", "Paclitaxel", "Pemetrexed",  "Gemcitabine", "pre_HGB_45days", "pre_PLT_45days")])  #no Pemetrexed
tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ cr_cys_7 + Age + sex + egfr_cock+ bmi + smoking + steroids  + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel  + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final_GI) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect) ~ cr_cys_7 + Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final_GI) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_grade_3_aes,cmp_status_grade_3_aes)  ~ cr_cys_7 + Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Gemcitabine + pre_HGB_45days + pre_PLT_45days+ thyroid+ ici+score,failcode=1,cencode=0, data = final_GI) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


cox_model <- coxph(Surv(death_follow_up_time_90d, mortality_90) ~ cr_cys_7+ Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine + thyroid +ici+score, data = final_GI)
summary(cox_model)
tbl_cox <- tbl_regression(cox_model, exponentiate = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))
tbl_cox
```

```{r}
final_GU <- final%>%
  filter(cancer_retype == 4)
summary(final_GU[, c("cr_cys_7", "Age", "sex", "egfr_cock", "bmi",  "smoking", "steroids", "cancer_stage", "ecog_cat",  "dose_1", "carbo", "Paclitaxel", "Pemetrexed",  "Gemcitabine", "pre_HGB_45days", "pre_PLT_45days")])  # all cr_cys ≥ 0.7
```

```{r}
final_GYN <- final%>%
  filter(cancer_retype == 5)

tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ cr_cys_7 + Age + sex + egfr_cock+ bmi + smoking + steroids  + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final_GYN) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect) ~ cr_cys_7 + Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final_GYN) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_grade_3_aes,cmp_status_grade_3_aes)  ~ cr_cys_7 + Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine + pre_HGB_45days + pre_PLT_45days+ thyroid+ ici+score,failcode=1,cencode=0, data = final_GYN) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


cox_model <- coxph(Surv(death_follow_up_time_90d, mortality_90) ~ cr_cys_7 + Age + sex + egfr_cock+ bmi + smoking + steroids  + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score, data = final_GYN)
summary(cox_model)
tbl_cox <- tbl_regression(cox_model, exponentiate = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))
tbl_cox

```


```{r}
final_HEENT <- final%>%
  filter(cancer_retype == 6)


tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ cr_cys_7 + Age + sex + egfr_cock+ bmi + smoking + steroids  + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid + ici+score,failcode=1,cencode=0, data = final_HEENT) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect) ~ cr_cys_7 + Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final_HEENT) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_grade_3_aes,cmp_status_grade_3_aes)  ~ cr_cys_7 + Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine + pre_HGB_45days + pre_PLT_45days+ thyroid+ ici+score,failcode=1,cencode=0, data = final_HEENT) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


cox_model <- coxph(Surv(death_follow_up_time_90d, mortality_90) ~ cr_cys_7 + Age + sex + egfr_cock+ bmi + smoking + steroids  + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid + ici+score, data = final_HEENT)
summary(cox_model)
tbl_cox <- tbl_regression(cox_model, exponentiate = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))
tbl_cox

```


##subgroup for cancer stage

```{r}

final_early <- final%>%
  filter(cancer_stage == 1 )

tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ cr_cys_7 + Age + sex + egfr_cock+ bmi + smoking + steroids + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final_early) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect) ~ cr_cys_7 + Age + sex + egfr_cock+ bmi + smoking + steroids + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final_early) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


tidycmprsk::crr(Surv(cmp_time_grade_3_aes,cmp_status_grade_3_aes) ~ cr_cys_7 + Age + sex + egfr_cock+ bmi + smoking + steroids + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ pre_HGB_45days + pre_PLT_45days+ thyroid+ ici+score,failcode=1,cencode=0, data = final_early) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

cox_model <- coxph(Surv(death_follow_up_time_90d, mortality_90) ~ cr_cys_7 + Age + sex + egfr_cock+ bmi + smoking + steroids + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score, data = final_early)
summary(cox_model)
tbl_cox <- tbl_regression(cox_model, exponentiate = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))
tbl_cox


```


```{r}
final_advanced <- final%>%
  filter(cancer_stage == 2 )
tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ cr_cys_7 + Age + sex + egfr_cock+ bmi + smoking + steroids + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final_advanced) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect) ~ cr_cys_7 + Age + sex + egfr_cock+ bmi + smoking + steroids + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final_advanced) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


tidycmprsk::crr(Surv(cmp_time_grade_3_aes,cmp_status_grade_3_aes) ~ cr_cys_7 + Age + sex + egfr_cock+ bmi + smoking + steroids + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ pre_HGB_45days + pre_PLT_45days+ thyroid+ ici+score,failcode=1,cencode=0, data = final_advanced) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

cox_model <- coxph(Surv(death_follow_up_time_90d, mortality_90) ~ cr_cys_7 + Age + sex + egfr_cock+ bmi + smoking + steroids + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score, data = final_advanced)
summary(cox_model)
tbl_cox <- tbl_regression(cox_model, exponentiate = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))
tbl_cox
```


##subgroup for high dose low dose, the defination is carbo-AUC ≥ 5 mg/mL/min, or r cisplatin  ≥ 75 mg/m2

```{r}
final_low_dose_1 <- final%>%
  filter(dose_1 == 0)


tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ cr_cys_7 + Age + sex + egfr_cock+ bmi + smoking + steroids+ cancer_stage + ecog_cat+ carbo + Paclitaxel + Pemetrexed +Gemcitabine + thyroid+ ici+score,failcode=1,cencode=0, data = final_low_dose_1) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect) ~ cr_cys_7 + Age + sex + egfr_cock+ bmi + smoking + steroids  + cancer_stage + ecog_cat + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final_low_dose_1) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


tidycmprsk::crr(Surv(cmp_time_grade_3_aes,cmp_status_grade_3_aes)  ~ cr_cys_7 + Age + sex + egfr_cock+ bmi + smoking + steroids  + cancer_stage + ecog_cat + carbo + Paclitaxel + Pemetrexed + Gemcitabine + pre_HGB_45days+ pre_PLT_45days+ thyroid+ ici+score,failcode=1,cencode=0, data = final_low_dose_1) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

cox_model <- coxph(Surv(death_follow_up_time_90d, mortality_90) ~ cr_cys_7 + Age + sex + egfr_cock+ bmi + smoking + steroids+ cancer_stage + ecog_cat+ carbo + Paclitaxel + Pemetrexed +Gemcitabine + thyroid+ ici+score, data = final_low_dose_1)
summary(cox_model)
tbl_cox <- tbl_regression(cox_model, exponentiate = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))
tbl_cox

```


```{r}
final_high_dose_1 <- final%>%
  filter(dose_1 ==1)


tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ cr_cys_7 + Age + sex + egfr_cock+ bmi + smoking + steroids+ cancer_stage + ecog_cat+ carbo + Paclitaxel + Pemetrexed +Gemcitabine + thyroid+ ici+score,failcode=1,cencode=0, data = final_high_dose_1) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect) ~ cr_cys_7 + Age + sex + egfr_cock+ bmi + smoking + steroids  + cancer_stage + ecog_cat + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final_high_dose_1) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


tidycmprsk::crr(Surv(cmp_time_grade_3_aes,cmp_status_grade_3_aes)  ~ cr_cys_7 + Age + sex + egfr_cock+ bmi + smoking + steroids  + cancer_stage + ecog_cat + carbo + Paclitaxel + Pemetrexed + Gemcitabine + pre_HGB_45days+ pre_PLT_45days+ thyroid+ ici+score,failcode=1,cencode=0, data = final_high_dose_1) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

cox_model <- coxph(Surv(death_follow_up_time_90d, mortality_90) ~ cr_cys_7 + Age + sex + egfr_cock+ bmi + smoking + steroids+ cancer_stage + ecog_cat+ carbo + Paclitaxel + Pemetrexed +Gemcitabine + thyroid+ ici+score, data = final_high_dose_1)
summary(cox_model)
tbl_cox <- tbl_regression(cox_model, exponentiate = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))
tbl_cox



```






#sensitivity analysis: 3 exposures with grade 2\3 AEs,hos,hos for side effect,mortality
#creating forest plot

##for HR of cre/cys,adjusted for 

#Demographics: age, sex
#markers of kidney function: GFR by Cockcroft equation(most oncologist use for creatinine clearance  instead of combined EPI equation)
#non-GFR determinants of cystatin C: BMI, smoking status, corticosteroid use, and thyroid disease.
#Medical comorbidities:Cancer stage?, Charlson comorbidity index, Ecog, high/low platin dose; carbo/cis; platinum partners including paclitaxel, pemetrexed, gemcitabine.
#baseline lab result?


```{r}
library(gtsummary)
library(tidycmprsk)


final$ecog_values <- as.factor(final$ecog_values)
final$ecog_values
##outcomes should be factors
##ecog_values affect a lot



final <- final %>%
  mutate(ecog_cat = ifelse(as.numeric(as.character(ecog_values)) < 1, 0, 1))%>%
  mutate(ecog_cat = as.factor(ecog_cat))
table(final$ecog_cat)


tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ exposure_epi_30+ Age + sex + egfr_cock+ bmi + smoking + steroids  + cancer_stage  +  ecog_cat +dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine + thyroid + ici+score,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect) ~ exposure_epi_30+ Age + sex + egfr_cock+ bmi + smoking + steroids +  cancer_stage +ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_anemia_2,cmp_status_anemia_2)  ~ exposure_epi_30+ Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine + pre_HGB_45days+ thyroid+ ici+score,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_anemia_3,cmp_status_anemia_3)  ~ exposure_epi_30+ Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ pre_HGB_45days+ thyroid + ici+score,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_2,cmp_status_throm_2)  ~ exposure_epi_30+ Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine + pre_PLT_45days+ thyroid+ ici+score,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_3,cmp_status_throm_3)  ~ exposure_epi_30+ Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine +pre_PLT_45days+ thyroid+ ici+score,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))
tidycmprsk::crr(Surv(cmp_time_aki_2,cmp_status_aki_2)  ~ exposure_epi_30+ Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_aki_3,cmp_status_aki_3)  ~ exposure_epi_30+ Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_grade_2_aes,cmp_status_grade_2_aes)  ~ exposure_epi_30+ Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine + pre_HGB_45days + pre_PLT_45days+ thyroid+ ici+score,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


tidycmprsk::crr(Surv(cmp_time_grade_3_aes,cmp_status_grade_3_aes)  ~ exposure_epi_30+ Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine + pre_HGB_45days + pre_PLT_45days+ thyroid+ ici+score,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

```
##unvariable analysis
```{r}
library(gtsummary)
library(tidycmprsk)


final$ecog_values <- as.factor(final$ecog_values)
final$ecog_values
##outcomes should be factors
##ecog_values affect a lot



final <- final %>%
  mutate(ecog_cat = ifelse(as.numeric(as.character(ecog_values)) < 1, 0, 1))%>%
  mutate(ecog_cat = as.factor(ecog_cat))
table(final$ecog_cat)


tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ exposure_epi_30,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect) ~ exposure_epi_30,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_anemia_2,cmp_status_anemia_2)  ~ exposure_epi_30,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_anemia_3,cmp_status_anemia_3)  ~ exposure_epi_30,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_2,cmp_status_throm_2)  ~ exposure_epi_30,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_3,cmp_status_throm_3)  ~ exposure_epi_30,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))
tidycmprsk::crr(Surv(cmp_time_aki_2,cmp_status_aki_2)  ~ exposure_epi_30,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_aki_3,cmp_status_aki_3)  ~ exposure_epi_30,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_grade_2_aes,cmp_status_grade_2_aes)  ~ exposure_epi_30,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


tidycmprsk::crr(Surv(cmp_time_grade_3_aes,cmp_status_grade_3_aes)  ~ exposure_epi_30,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

```


## for 90d mortality with 30 % discrepancy
```{r}
library(survival)
final <- final%>%
  mutate(follow_up_time = last_follow_up_date - Baseline_sample_Date)
final=final%>%mutate(death_follow_up_time_90d=ifelse(death_90==2&follow_up_time<=90,follow_up_time,90))

final <- final%>%
  mutate(mortality_90 = ifelse(death_90==2,1,0))

surv_fit_90d <- survfit(Surv(death_follow_up_time_90d, mortality_90) ~ exposure_epi_30, data = final)
# Fit a Cox proportional hazards model
cox_model <- coxph(Surv(death_follow_up_time_90d, mortality_90) ~ exposure_epi_30 + Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine + thyroid + ici+score, data = final)

# View the summary of the Cox model
summary(cox_model)
tbl_cox <- tbl_regression(cox_model, exponentiate = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))
tbl_cox


# using survdiff() for Log-Rank test
log_rank_test <- survdiff(Surv(death_follow_up_time_90d, mortality_90) ~ exposure_epi_30, data = final)
log_rank_test$pvalue
```

##for HR of 15% discrepancy,adjusted for 

#Demographics: age, sex
#markers of kidney function: GFR by Cockcroft equation(most oncologist use for creatinine clearance  instead of combined EPI equation)
#non-GFR determinants of cystatin C: BMI, smoking status, corticosteroid use, and thyroid disease.
#Medical comorbidities:Cancer stage?, Charlson comorbidity index, Ecog, high/low platin dose; carbo/cis; platinum partners including paclitaxel, pemetrexed, gemcitabine.
#baseline lab result?


```{r}
library(gtsummary)
library(tidycmprsk)


final$ecog_values <- as.factor(final$ecog_values)
final$ecog_values
##outcomes should be factors
##ecog_values affect a lot



final <- final %>%
  mutate(ecog_cat = ifelse(as.numeric(as.character(ecog_values)) < 1, 0, 1))%>%
  mutate(ecog_cat = as.factor(ecog_cat))
table(final$ecog_cat)


tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ exposure_cg_15+ Age + sex + egfr_cock+ bmi + smoking + steroids  + cancer_stage  +  ecog_cat +dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect) ~ exposure_cg_15+ Age + sex + egfr_cock+ bmi + smoking + steroids +  cancer_stage +ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_anemia_2,cmp_status_anemia_2)  ~ exposure_cg_15+ Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine + pre_HGB_45days+ thyroid+ ici+score,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_anemia_3,cmp_status_anemia_3)  ~ exposure_cg_15+ Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ pre_HGB_45days+ thyroid+ ici+score,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_2,cmp_status_throm_2)  ~ exposure_cg_15+ Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine + pre_PLT_45days+ thyroid+ ici+score,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_3,cmp_status_throm_3)  ~ exposure_cg_15+ Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine +pre_PLT_45days+ thyroid+ ici+score,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))
tidycmprsk::crr(Surv(cmp_time_aki_2,cmp_status_aki_2)  ~ exposure_cg_15+ Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_aki_3,cmp_status_aki_3)  ~ exposure_cg_15+ Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_grade_2_aes,cmp_status_grade_2_aes)  ~ exposure_cg_15+ Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine + pre_HGB_45days + pre_PLT_45days+ thyroid+ ici+score,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


tidycmprsk::crr(Surv(cmp_time_grade_3_aes,cmp_status_grade_3_aes)  ~ exposure_cg_15+ Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine + pre_HGB_45days + pre_PLT_45days+ thyroid+ ici+score,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))
```

##univariable analysis
```{r}
library(gtsummary)
library(tidycmprsk)

tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp)  ~ exposure_cg_15,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect) ~ exposure_cg_15,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_anemia_2,cmp_status_anemia_2)  ~ exposure_cg_15,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_anemia_3,cmp_status_anemia_3)  ~ exposure_cg_15,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_2,cmp_status_throm_2)  ~ exposure_cg_15,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_3,cmp_status_throm_3)  ~ exposure_cg_15,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))
tidycmprsk::crr(Surv(cmp_time_aki_2,cmp_status_aki_2)  ~ exposure_cg_15,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_aki_3,cmp_status_aki_3)  ~ exposure_cg_15,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_grade_2_aes,cmp_status_grade_2_aes)  ~ exposure_cg_15,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


tidycmprsk::crr(Surv(cmp_time_grade_3_aes,cmp_status_grade_3_aes)  ~ exposure_cg_15,failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))
```




## for 90d mortality with 15 % discrepancy
```{r}
library(survival)
final <- final%>%
  mutate(follow_up_time = last_follow_up_date - Baseline_sample_Date)
final=final%>%mutate(death_follow_up_time_90d=ifelse(death_90==2&follow_up_time<=90,follow_up_time,90))

final <- final%>%
  mutate(mortality_90 = ifelse(death_90==2,1,0))

surv_fit_90d <- survfit(Surv(death_follow_up_time_90d, mortality_90) ~ exposure_cg_15, data = final)
# Fit a Cox proportional hazards model
cox_model <- coxph(Surv(death_follow_up_time_90d, mortality_90) ~ exposure_cg_15+ Age + sex + egfr_cock+ bmi + smoking + steroids + cancer_stage + ecog_cat + dose_1 + carbo + Paclitaxel + Pemetrexed + Gemcitabine+ thyroid+ ici+score, data = final)

# View the summary of the Cox model
summary(cox_model)
tbl_cox <- tbl_regression(cox_model, exponentiate = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))
tbl_cox


# using survdiff() for Log-Rank test
log_rank_test <- survdiff(Surv(death_follow_up_time_90d, mortality_90) ~ exposure_cg_15, data = final)
log_rank_test$pvalue
```







#Dose difference analysis
#-	dose administered minus the calculated dose for carboplatin (unindexed eGFR CRE-CYS)
#-	Quartiles of dose difference 

#Histogram of dose difference --- one histogram for people who got toxicity, one who didn’t get tox

```{r}
#recalculated carbo dose using unindexed cock-croft equation
#creatinine capped as 0.7,CrCl apped as 125ml/min

Cockcroft_capped <- function(age, weight, male, cre) {
  # when creatinine < 0.7 ，set the creatinine as 0.7
  adjusted_cre <- ifelse(cre < 0.7, 0.7, cre)
  
  # base on gender 
  if (male == 0) {
    value <- (140 - age) * weight * 0.85 / (72 * adjusted_cre)
  } else {
    value <- (140 - age) * weight / (72 * adjusted_cre)
  }
  
  return(value)
}


final$egfr_cock_capped <- mapply(Cockcroft_capped,final$Age,final$weight,final$male,final$baseline_cre) 


final <- final%>%
  mutate(carbo_dose_cal_cock = case_when(
       egfr_cock_capped<= 125 ~ carbo_AUC * (egfr_cock_capped + 25),
       egfr_cock_capped > 125 ~ carbo_AUC * 150
       ))



## reclculated  capped egfr based on creatinine and cystatin function without race, then unindexed it, and calculating cardo dose using capped egfr based on creatinine and cystatin

library(nephro)
final <- final%>%
  mutate(baseline_cre_capped = ifelse(baseline_cre< 0.7,0.7,baseline_cre))
           
final$egfr_cystatin_cre_capped = CKDEpi_RF.creat.cys(final$baseline_cre_capped,final$baseline_cystatin_c,final$sex,final$Age)

# unindexed the egfr
final$egfr_cystatin_cre_capped_unindex = final$egfr_cystatin_cre_capped * final$BSA / 1.73
# calculated carbo dose

final <- final%>%
  mutate(carbo_dose_cal_cre_cys_unindexed = case_when(
       egfr_cystatin_cre_capped_unindex<= 125 ~ carbo_AUC * (egfr_cystatin_cre_capped_unindex + 25),
       egfr_cystatin_cre_capped_unindex > 125 ~ carbo_AUC * 150
       ))

```

```{r}
final$carbo_dose_diff_cock <- final$carbo_dose - final$carbo_dose_cal_cre_cys_unindexed

final <- final %>%
  mutate(carbo_ratio = carbo_dose / carbo_dose_cal_cre_cys_unindexed) %>%
  mutate(carbo_dose_diff_cat = case_when(
    carbo_ratio > 1.2 ~ 1,
    carbo_ratio <= 1.2 & carbo_ratio > 1.1 ~ 2,
    carbo_ratio <= 1.1 & carbo_ratio > 0.9 ~ 3,
    carbo_ratio <= 0.9 & carbo_ratio > 0.8 ~ 4,
    carbo_ratio <= 0.8  ~ 5
  ))

 

table(final$carbo_dose_diff_cat)
table(final$carbo)






ggplot(final, aes(x = carbo_dose_diff_cat)) +
  geom_bar(aes(y = (..count..)/sum(..count..)),
           fill = "#3B4992FF",
           stat = "count") + # 
  geom_text(stat = "count", 
            aes(label = scales::percent(..count../sum(..count..), accuracy = 0.1),
                y = (..count..)/sum(..count..)), 
            vjust = -0.5) + # 
  theme(axis.text.x = element_text(hjust = 1)) + # 
  labs(title = "carbo dose difference distribution", x = "carbo dose difference", y = "Percentage (%)") +
  scale_y_continuous(labels = scales::percent) + # 
  scale_fill_identity() + # 
  theme_classic()


library(ggplot2)
library(dplyr)

# 
final <- final %>%
  mutate(
    carbo_dose_diff_cat_label = case_when(
      carbo_dose_diff_cat == 1 ~ "> 1.2",
      carbo_dose_diff_cat == 2 ~ "1.1-1.2",
      carbo_dose_diff_cat == 3 ~ "0.9-1.1",
      carbo_dose_diff_cat == 4 ~ "0.8-0.9",
      carbo_dose_diff_cat == 5 ~ "≤ 0.8"
    )# 
  )

final$carbo_dose_diff_cat_label = factor(
      final$carbo_dose_diff_cat_label,
      levels = c("≤ 0.8", "0.8-0.9", "0.9-1.1", "1.1-1.2", "> 1.2")
    )
  



final_carbo <- final%>%
  filter(carbo == 1)
# 
ggplot(final_carbo, aes(x = carbo_dose_diff_cat_label)) +
  geom_bar(aes(y = (..count..)/sum(..count..)),  
           fill = ifelse(carbo_dose_diff_cat_label %in% c("> 1.2"),"#BB0021FF", "#3B4992FF"),
           stat = "count") + # 
  geom_text(stat = "count", 
            aes(label = scales::percent(..count../sum(..count..), accuracy = 0.1),
                y = (..count..)/sum(..count..)), 
            vjust = -0.5) + # 
  theme(axis.text.x = element_text(hjust = 1)) + # 
  labs(title = "", x = "carbo dose / carboplatin dose calculated by adjusted eGFR CKD-EPI", y = "Percentage (%)") +
  scale_y_continuous(labels = scales::percent) + # 
  scale_fill_identity() + # 
  theme_classic()

  

  
##generate new cat
final <- final %>%
  mutate(carbo_ratio = carbo_dose / carbo_dose_cal_cre_cys_unindexed) %>%
  mutate(carbo_dose_diff_cat = case_when(
    carbo_ratio > 1.25 ~ 1,
    carbo_ratio <= 1.25 & carbo_ratio > 1.2 ~ 2,
    carbo_ratio <= 1.2 & carbo_ratio > 1.15 ~ 3,
     carbo_ratio <= 1.15 & carbo_ratio > 1.1 ~ 4,
    carbo_ratio <= 1.1 & carbo_ratio > 1.05 ~ 5,
    carbo_ratio <= 1.05 & carbo_ratio > 0.95 ~ 6,
     carbo_ratio <= 0.95 & carbo_ratio > 0.90 ~ 7,
     carbo_ratio <= 0.9 & carbo_ratio > 0.85 ~8,
     carbo_ratio <= 0.85 & carbo_ratio > 0.8 ~ 9,
     carbo_ratio <= 0.8 & carbo_ratio > 0.75 ~ 10,
     carbo_ratio <= 0.75  ~ 11
  ))


final <- final %>%
  mutate(
    carbo_dose_diff_cat_label = case_when(
      carbo_dose_diff_cat == 1 ~ "> 25% overdose",
      carbo_dose_diff_cat == 2 ~ "20-25% overdose",
      carbo_dose_diff_cat == 3 ~ "15-20% overdose",
      carbo_dose_diff_cat == 4 ~ "10-15% overdose",
      carbo_dose_diff_cat == 5 ~ "5-10% overdose",
      carbo_dose_diff_cat == 6 ~ "appropriately dosed",
       carbo_dose_diff_cat == 7 ~ "5-10% underdose",
       carbo_dose_diff_cat == 8 ~ "10-15%  underdose",
       carbo_dose_diff_cat == 9 ~ "15-20% underdose",
       carbo_dose_diff_cat == 10 ~ "20-25% underdose",
       carbo_dose_diff_cat == 11 ~ "> 25% underdose"
    )
  )




table(final$carbo_dose_diff_cat)

final$carbo_dose_diff_cat_label = factor(
      final$carbo_dose_diff_cat_label,
      levels = c( "> 25% underdose","20-25% underdose","15-20% underdose","10-15%  underdose","5-10% underdose","appropriately dosed","5-10% overdose","10-15% overdose","15-20% overdose","20-25% overdose","> 25% overdose")
    )
  

final_carbo <- final%>%
  filter(carbo == 1)
# 
ggplot(final_carbo, aes(x = carbo_dose_diff_cat_label)) +
  geom_bar(aes(y = (..count..)/sum(..count..),  
               fill = ifelse(carbo_dose_diff_cat_label %in% c("> 25% overdose", "20-25% overdose","15-20% overdose"),"#BB0021FF", "#3B4992FF")),
           stat = "count") + # 
  geom_text(stat = "count", 
            aes(label = scales::percent(..count../sum(..count..), accuracy = 0.1),
                y = (..count..)/sum(..count..)), 
            vjust = -0.5) + 
  theme(
    axis.text.x = element_text(face = "bold", size = 14, hjust = 1), 
    axis.text.y = element_text(face = "bold", size = 14), # 
    axis.title.x = element_text(face = "bold", size = 16), # 
    axis.title.y = element_text(face = "bold", size = 16), # 
    axis.text = element_text(face = "bold",size = 20) # 
  ) + 
  labs(title = "Figure A", x = "", y = "Percentage (%)") +
  scale_y_continuous(labels = scales::percent) + # 
  scale_fill_identity() + # 
  theme_classic()


# 
ggplot(final, aes(x = carbo_ratio)) +
  geom_histogram(
    binwidth = 0.05, 
    color = "black", 
    fill = "darkblue", 
    aes(y = ..count.. / sum(..count..) * 100)  # 
  ) +
  scale_y_continuous(name = "Percentage (%)", labels = scales::percent_format(scale = 1)) +  # 
  scale_x_continuous(
    breaks = c(0.55, 0.7, 0.85, 1, 1.15, 1.3, 1.45))+
  labs(title = "Distribution of Carbo Ratio", 
       x = "Carbo Ratio") +  # 
  theme_classic() +  # 
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),  # 
    axis.title = element_text(size = 12),  # 
    axis.text = element_text(size = 10)  # 
  )




```

##AEs:setting carbo _dose_diff as 5 groups

```{r}
final <- final %>%
  dplyr::mutate(across(c(cmp_status_anemia_2,cmp_status_anemia_3,cmp_status_throm_2,cmp_status_throm_3,cmp_status_neutro_2,cmp_status_neutro_3,cmp_status_aki_2,cmp_status_aki_3), as.factor))

```
```{r}
final <- final %>%
  dplyr::mutate(
    carbo_dose_diff_cat = relevel(as.factor(carbo_dose_diff_cat), ref = "3")
  ) # setting group 3 as reference group
levels(final$carbo_dose_diff_cat)


tidycmprsk::crr(Surv(cmp_time_anemia_2,cmp_status_anemia_2) ~ carbo_dose_diff_cat+ Age + male, failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_anemia_3,cmp_status_anemia_3) ~ carbo_dose_diff_cat, failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_2,cmp_status_throm_2) ~ carbo_dose_diff_cat + Age + male, failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_3,cmp_status_throm_3) ~ carbo_dose_diff_cat, failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_neutro_2,cmp_status_neutro_2) ~ carbo_dose_diff_cat + Age + male, failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_aki_2,cmp_status_aki_2) ~ carbo_dose_diff_cat + Age + male, failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_aki_3,cmp_status_aki_3) ~ carbo_dose_diff_cat, failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp) ~ carbo_dose_diff_cat, failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect) ~ carbo_dose_diff_cat + Age + male, failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

final <- final%>%
  mutate(follow_up_time = last_follow_up_date - Baseline_sample_Date)
final=final%>%mutate(death_follow_up_time_90d=ifelse(death_90==2&follow_up_time<=90,follow_up_time,90))

final <- final%>%
  mutate(mortality_90 = ifelse(death_90==2,1,0))


cox <- coxph(Surv(death_follow_up_time_90d, mortality_90) ~ carbo_dose_diff_cat, data = final)


```


#combing cat as 2 groups: > 15% and ≤ 15%
```{r}

final <- final %>%
  mutate(carbo_dose_diff_cat_2_15 = ifelse(carbo_ratio > 1.15 , 1, 0))
  
table(final$carbo_dose_diff_cat_2_15)

final <- final %>%
  dplyr::mutate(
    carbo_dose_diff_cat_2_15 = relevel(as.factor(carbo_dose_diff_cat_2_15), ref = "0")
  ) # setting group 3 as reference group
levels(final$carbo_dose_diff_cat_2_15)


final <- final %>%
  dplyr::mutate(across(c(cmp_status_anemia_2,cmp_status_anemia_3,cmp_status_throm_2,cmp_status_throm_3,cmp_status_neutro_2,cmp_status_neutro_3,cmp_status_aki_2,cmp_status_aki_3), as.factor))



tidycmprsk::crr(Surv(cmp_time_anemia_2,cmp_status_anemia_2) ~ carbo_dose_diff_cat_2_15+ Age + male+ cancer_stage + score, failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_anemia_3,cmp_status_anemia_3) ~ carbo_dose_diff_cat_2_15+ Age + male+ cancer_stage + score, failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_2,cmp_status_throm_2) ~ carbo_dose_diff_cat_2_15 + Age + male+ cancer_stage + score, failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_throm_3,cmp_status_throm_3) ~ carbo_dose_diff_cat_2_15+ Age + male+ cancer_stage + score, failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_neutro_2,cmp_status_neutro_2) ~ carbo_dose_diff_cat_2_15 + Age + male+ cancer_stage + score, failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))
tidycmprsk::crr(Surv(cmp_time_neutro_2,cmp_status_neutro_3) ~ carbo_dose_diff_cat_2_15 + Age + male+ cancer_stage + score, failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_aki_2,cmp_status_aki_2) ~ carbo_dose_diff_cat_2_15 + Age + male+ cancer_stage + score, failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_aki_3,cmp_status_aki_3) ~ carbo_dose_diff_cat_2_15+ Age + male+ cancer_stage + score, failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

tidycmprsk::crr(Surv(cmp_time_hosp,cmp_status_hosp) ~ carbo_dose_diff_cat_2_15+ Age + male+ cancer_stage + score, failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))


tidycmprsk::crr(Surv(cmp_time_side_effect,cmp_status_side_effect) ~ carbo_dose_diff_cat_2_15 + Age + male, failcode=1,cencode=0, data = final) %>% tbl_regression(exp = TRUE,pvalue_fun = function(x) style_pvalue(x, digits = 3))

cox <- coxph(Surv(death_follow_up_time_90d, mortality_90) ~ carbo_dose_diff_cat_2_15 + Age + male+ cancer_stage + score, data = final)
tbl_cox <- tbl_regression(cox, exponentiate = TRUE,,pvalue_fun = function(x) style_pvalue(x, digits = 3))
tbl_cox
```

